### 2016-06-29 2016_Proceedings_ISMIR/keynotes.tex
initial checkin, made some changes from 2015 already

%-------------------------------------------
\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Keynote Talks}
\includepdf[pages=1,pagecommand=\thispagestyle{empty}]{external/10_Keynotes.pdf}
\thispagestyle{empty}\cleardoublepage
 %-------------------------------------------
% Keynote talk 1
\addcontentsline{toc}{subsection}{Integrating Music Information Sources for Music Production and Consumption\\\textit{Mark Sandler}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-1_Keynotes-1.pdf}%

\thispagestyle{empty}\cleardoublepage
% Keynote talk 2
\addcontentsline{toc}{subsection}{The Promise of Music Information Retrieval: Are we there yet?\\\textit{J.\ Stephen Downie}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-2_Keynotes-2.pdf}%

### 2016-06-29 2016_Proceedings_ISMIR/tutorials.tex
initial checkin, made some changes from 2015 already

%-------------------------------------------
\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Tutorials}
\includepdf[pages=1,pagecommand=\thispagestyle{empty}]{external/11_Tutorials.pdf}%
\thispagestyle{empty}\cleardoublepage
 %-------------------------------------------
% Tutorial 1
\addcontentsline{toc}{subsection}{Why Singing is Interesting\\\textit{Simon Dixon, Masataka Goto, Matthias Mauch}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-1_Tutorial-1.pdf}%

% Tutorial 2
\addcontentsline{toc}{subsection}{Addressing the Music Information Needs of Musicologists\\\textit{Richard J.\ Lewis, Ben Fields, Tim Crawford}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-2_Tutorial-2.pdf}%

% Tutorial 3
\addcontentsline{toc}{subsection}{Markov Logic Networks for Music Analysis\\\textit{Helene Papadopoulos}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-3_Tutorial-3.pdf}%

% Tutorial 4
\addcontentsline{toc}{subsection}{COmputation and FLAmenco: Why Flamenco is Interesting for
MIR Research\\\textit{Emilia G{\'o}mez, Nadine Kroher, Jose Miguel D{\'i}az-B{\'a}{\~n}ez, Sergio Oramas, 
Joaqu{\'i}n Mora, Francisco G{\'o}mez-Mart{\'i}n}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-4_Tutorial-4.pdf}%

% Tutorial 5
\addcontentsline{toc}{subsection}{Using Correlation Analysis and Big Data to Identify and Predict Musical Behaviors\\\textit{Jeff C.\ Smith}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-5_Tutorial-5.pdf}%

% Tutorial 6
\addcontentsline{toc}{subsection}{Automatic Music Transcription\\\textit{Zhiyao Duan, Emmanouil Benetos}}
\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-6_Tutorial-6.pdf}%

### 2016-06-29 2016_Proceedings_ISMIR/00-run.sh

@@ -1,0 +1,13 @@
+#!/bin/bash -xuev
+
+rm -f 2016_Proceedings_ISMIR.aux
+rm -f 2016_Proceedings_ISMIR.ain
+pdflatex 2016_Proceedings_ISMIR.tex
+
+#ReplaceText.vbs 2016_Proceedings_ISMIR.aux "\IeC " ""
+sed -e 's/\IeC //g' 2016_Proceedings_ISMIR.aux > 2016_Proceedings_ISMIR_2.aux
+
+authorindex -d 2016_Proceedings_ISMIR_2.aux
+
+pdflatex 2016_Proceedings_ISMIR.tex
+pdflatex 2016_Proceedings_ISMIR.tex

### 2016-06-29 2016_Proceedings_ISMIR/keynotes.tex
added macro for including abstracts

@@
 % Keynote talk 1
-\addcontentsline{toc}{subsection}{Integrating Music Information Sources for Music Production and Consumption\\\textit{Mark Sandler}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-1_Keynotes-1.pdf}%
+\includeabstract{Integrating Music Information Sources for Music Production and Consumption}{Mark Sandler}{external/10-1_Keynotes-1.pdf}
 
@@
 % Keynote talk 2
-\addcontentsline{toc}{subsection}{The Promise of Music Information Retrieval: Are we there yet?\\\textit{J.\ Stephen Downie}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/10-2_Keynotes-2.pdf}%
+\includeabstract{The Promise of Music Information Retrieval: Are we there yet?}{J.\ Stephen Downie}{external/10-2_Keynotes-2.pdf}

### 2016-06-29 2016_Proceedings_ISMIR/tutorials.tex
added macro for including abstracts

@@
 % Tutorial 1
-\addcontentsline{toc}{subsection}{Why Singing is Interesting\\\textit{Simon Dixon, Masataka Goto, Matthias Mauch}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-1_Tutorial-1.pdf}%
+\includeabstract{Why Singing is Interesting}{Simon Dixon, Masataka Goto, Matthias Mauch}{external/11-1_Tutorial-1.pdf}
 
 % Tutorial 2
-\addcontentsline{toc}{subsection}{Addressing the Music Information Needs of Musicologists\\\textit{Richard J.\ Lewis, Ben Fields, Tim Crawford}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-2_Tutorial-2.pdf}%
+\includeabstract{Addressing the Music Information Needs of Musicologists}{Richard J.\ Lewis, Ben Fields, Tim Crawford}{external/11-2_Tutorial-2.pdf}
 
 % Tutorial 3
-\addcontentsline{toc}{subsection}{Markov Logic Networks for Music Analysis\\\textit{Helene Papadopoulos}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-3_Tutorial-3.pdf}%
+\includeabstract{Markov Logic Networks for Music Analysis}{Helene Papadopoulos}{external/11-3_Tutorial-3.pdf}
 
 % Tutorial 4
-\addcontentsline{toc}{subsection}{COmputation and FLAmenco: Why Flamenco is Interesting for
-MIR Research\\\textit{Emilia G{\'o}mez, Nadine Kroher, Jose Miguel D{\'i}az-B{\'a}{\~n}ez, Sergio Oramas, 
-Joaqu{\'i}n Mora, Francisco G{\'o}mez-Mart{\'i}n}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-4_Tutorial-4.pdf}%
+\includeabstract{COmputation and FLAmenco: Why Flamenco is Interesting for
+MIR Research}{Emilia G{\'o}mez, Nadine Kroher, Jose Miguel D{\'i}az-B{\'a}{\~n}ez, Sergio Oramas, Joaqu{\'i}n Mora, Francisco G{\'o}mez-Mart{\'i}n}{external/11-4_Tutorial-4.pdf}
 
 % Tutorial 5
-\addcontentsline{toc}{subsection}{Using Correlation Analysis and Big Data to Identify and Predict Musical Behaviors\\\textit{Jeff C.\ Smith}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-5_Tutorial-5.pdf}%
+\includeabstract{Using Correlation Analysis and Big Data to Identify and Predict Musical Behaviors}{Jeff C.\ Smith}{external/11-5_Tutorial-5.pdf}
 
 % Tutorial 6
-\addcontentsline{toc}{subsection}{Automatic Music Transcription\\\textit{Zhiyao Duan, Emmanouil Benetos}}
-\includepdf[pagecommand=\thispagestyle{fancy}]{external/11-6_Tutorial-6.pdf}%
+\includeabstract{Automatic Music Transcription}{Zhiyao Duan, Emmanouil Benetos}{external/11-6_Tutorial-6.pdf}

### 2016-06-29 2016_Proceedings_ISMIR/tutorials.tex
updated TOC info for keynotes and tutorials

@@
 % Tutorial 1
-\includeabstract{Why Singing is Interesting}{Simon Dixon, Masataka Goto, Matthias Mauch}{external/11-1_Tutorial-1.pdf}
+\includeabstract{Jazz solo analysis between music information
+  retrieval, music psychology, and jazz research}{Jakob Abe{\ss}er,
+  Klaus Frieler, Wolf-Georg Zaddach}{external/11-1_Tutorial-1.pdf}
 
 % Tutorial 2
-\includeabstract{Addressing the Music Information Needs of Musicologists}{Richard J.\ Lewis, Ben Fields, Tim Crawford}{external/11-2_Tutorial-2.pdf}
+\includeabstract{Music Information Retrieval: Overview, Recent
+  Developments and Future Challenges}{Emilia G\'omez, Markus Schedl,
+  Xavier Serra, Xiao Hu}{external/11-2_Tutorial-2.pdf}
 
 % Tutorial 3
-\includeabstract{Markov Logic Networks for Music Analysis}{Helene Papadopoulos}{external/11-3_Tutorial-3.pdf}
+\includeabstract{Why is studio production interesting?}{Emmanuel
+  Deruty, Fran\c{c}ois Pachet}{external/11-3_Tutorial-3.pdf}
 
 % Tutorial 4
-\includeabstract{COmputation and FLAmenco: Why Flamenco is Interesting for
-MIR Research}{Emilia G{\'o}mez, Nadine Kroher, Jose Miguel D{\'i}az-B{\'a}{\~n}ez, Sergio Oramas, Joaqu{\'i}n Mora, Francisco G{\'o}mez-Mart{\'i}n}{external/11-4_Tutorial-4.pdf}
+\includeabstract{Introduction to EEG Decoding for Music Information Retrieval
+Research}{Sebastian Stober, Blair Kaneshiro}{external/11-4_Tutorial-4.pdf}
 
 % Tutorial 5
-\includeabstract{Using Correlation Analysis and Big Data to Identify and Predict Musical Behaviors}{Jeff C.\ Smith}{external/11-5_Tutorial-5.pdf}
+\includeabstract{Natural Language Processing for MIR}{Sergio Oramas,
+  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{external/11-5_Tutorial-5.pdf}
 
 % Tutorial 6
-\includeabstract{Automatic Music Transcription}{Zhiyao Duan, Emmanouil Benetos}{external/11-6_Tutorial-6.pdf}
+\includeabstract{Why Hip-Hop is interesting}{Jan Van Balen, Ethan
+  Hein, Dan Brown}{external/11-6_Tutorial-6.pdf}

### 2016-06-30 2016_Proceedings_ISMIR/papers.tex
wrote script to generate papers.tex, might not have gotten unicode right yet

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 1}
\includepdf[pages=2,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Learning to Pinpoint Singing Voice from Weakly Labeled Examples}{Jan Schlüter}{articles/315_Paper}
\includepaper{SiMPle: Assessing Music Similarity Using Subsequences Joins}{"Diego Silva, Chin-Chia Michael Yeh, Gustavo Batista and Eamonn Keogh"}{articles/099_Paper}
\includepaper{Feature Learning for Chord Recognition: The Deep Chroma Extractor}{Filip Korzeniowski and Gerhard Widmer}{articles/178_Paper}
\includepaper{Brain Beats: Tempo Extraction from EEG Data}{"Sebastian Stober, Thomas Praetzlich and Meinard Mueller"}{articles/022_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 2}
\includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{AUTOMATIC TAGGING USING DEEP CONVOLUTIONAL NEURAL NETWORKS}{"Keunwoo Choi, George Fazekas and Mark Sandler"}{articles/009_Paper}
\includepaper{Analyzing Measure Annotations for Western Classical Music Recordings}{"Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz and Meinard Müller"}{articles/079_Paper}
\includepaper{Score-Informed Identification of Missing and Extra Notes in Piano Recordings}{"Sebastian Ewert, Siying Wang, Meinard Mueller and Mark Sandler"}{articles/123_Paper}
\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{"Sebastian Böck, Florian Krebs and Gerhard Widmer"}{articles/186_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 3}
\includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font and Xavier Serra}{articles/195_Paper}
\includepaper{Using Priors To Improve Estimates of Music Structure}{Jordan Smith and Masataka Goto}{articles/135_Paper}
\includepaper{A Neural Greedy Model for Voice Separation in Symbolic Music}{Patrick Gray and Razvan Bunescu}{articles/296_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 4}
\includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Towards Reading Sheet Music}{"Matthias Dorfer, Andreas Arzt and Gerhard Widmer"}{articles/027_Paper}
\includepaper{A plan for sustainable MIR evaluation}{"Brian McFee, Eric Humphrey and Julián Urbano"}{articles/257_Paper}
\includepaper{Go With the Flow: When Listeners Use Music as Technology}{"Andrew Demetriou, Martha Larson and Cynthia C. S. Liem"}{articles/068_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 5}
\includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Automatic Melodic Reduction using a Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
\includepaper{Singing Melody Extraction using Multi-Column Deep Neural Networks}{"Sangeun Kum, Changheun Oh and Juhan Nam"}{articles/119_Paper}
\includepaper{Instrumental idiom in the 16th century: patterns in arrangements of vocal music}{"David Lewis, Tim Crawford and Daniel Müllensiefen"}{articles/165_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 6}
\includepdf[pages=9,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Learning a feature space for world music style similarity}{"Maria Panteli, Emmanouil Benetos and Simon Dixon"}{articles/166_Paper}
\includepaper{Bayesian meter tracking on learned signal representations}{Andre Holzapfel and Thomas Grill}{articles/132_Paper}
\includepaper{The Sousta corpus: Beat-informed automatic transcription of traditional dance tunes}{Andre Holzapfel and Emmanouil Benetos}{articles/156_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Oral session 7}
\includepdf[pages=10,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{A LOOK AT THE CLOUD FROM BOTH SIDES NOW: AN ANALYSIS OF CLOUD MUSIC SERVICE USAGE}{"Jin Ha Lee, Yea-Seul Kim and Chris Hubbles"}{articles/087_Paper}
\includepaper{A Hybrid Gaussian-HMM-Deep Learning Approach For Automatic Chord Estimation With Very Large Vocabulary}{Junqi Deng and Yu-Kwong Kwok}{articles/058_Paper}
\includepaper{SYSTEMATIC EXPLORATION OF COMPUTATIONAL MUSIC STRUCTURE RESEARCH}{Oriol Nieto and Juan Pablo Bello}{articles/043_Paper}
\includepaper{Extracting Ground-Truth Information from MIDI Files: A MIDIfesto}{Colin Raffel and Daniel Ellis}{articles/105_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Poster session 1}
\includepdf[pages=1,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{TIME-DELAYED MELODY SURFACES FOR R_GA RECOGNITION}{"Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan _entürk and Xavier Serra"}{articles/030_Paper}
\includepaper{ON PRACTICAL STRATEGIES OF MELODY INDEXING FOR QUERY BY HUMMING}{Bartlomiej Stasiak}{articles/089_Paper}
\includepaper{Recurrent Neural Networks for Drum Transcription}{"Richard Vogl, Matthias Dorfer and Peter Knees"}{articles/269_Paper}
\includepaper{Integer Programming Formulation of the Problem of Generating Milton Babbitt's All-partition Arrays}{"Tsubasa Tanaka, Brian Bemman and David Meredith"}{articles/034_Paper}
\includepaper{Mining Musical Traits of Social Functions in Native American Music}{"Daniel Shanahan, Kerstin Neubarth and Darrell Conklin"}{articles/167_Paper}
\includepaper{Exploring The Latent Structure of Collaborations in Music Production}{Nazareno Andrade and Flavio Figueiredo}{articles/251_Paper}
\includepaper{Musical Note Estimation for F0 Trajectories of Singing Voices based on a Bayesian Semi-beat-synchronous HMM}{"Ryo Nishikimi, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii"}{articles/004_Paper}
\includepaper{NOISE ROBUST MUSIC ARTIST RECOGNITION USING I-VECTOR FEATURES}{Hamid Eghbal-zadeh and Gerhard Widmer}{articles/037_Paper}
\includepaper{Piano Transcription using an Exponential Decay Model}{"Tian Cheng, Matthias Mauch, Emmanouil Benetos and Simon Dixon"}{articles/085_Paper}
\includepaper{Live Song ID: A Hashprint Approach}{"TJ Tsai, Thomas Praetzlich and Meinard Mueller"}{articles/098_Paper}
\includepaper{Nonnegative tensor factorization with frequency modulation cues for blind audio source separation}{"Elliot Creager, Noah Stein and Roland Badeau"}{articles/103_Paper}
\includepaper{On the evaluation of rhythmic and melodic descriptors}{Maria Panteli and Simon Dixon}{articles/161_Paper}
\includepaper{Analysis and classification of phonation modes in singing}{Daniel Stoller and Simon Dixon}{articles/233_Paper}
\includepaper{Beat Tracking with a Cepstroid Invariant Neural Network}{Anders Elowsson}{articles/252_Paper}
\includepaper{On drum playing technique detection in polyphonic mixtures}{Chih-Wei Wu and Alexander Lerch}{articles/268_Paper}
\includepaper{MusicDB: A Platform for Longitudinal Music Analytics}{Jeremy Hyrkas and Bill Howe}{articles/284_Paper}
\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{"Jan Haji_, jr., Ji_í Novotn_, Pavel Pecina and Jaroslav Pokorn_"}{articles/289_Paper}
\includepaper{Two (note) heads are better than one: pen-based multimodal interaction with music notation}{"Jorge Calvo-Zaragoza, David Rizo and Jose M. Iñesta"}{articles/006_Paper}
\includepaper{Music Structural Segmentation Across Genres with Gammatone Features}{Mi Tian and Mark B. Sandler}{articles/032_Paper}
\includepaper{Enhancing cover song identification with hierarchical rank aggregation}{"Julien Osmalskyj, Marc Van Droogenbroeck and Jean-Jacques Embrechts"}{articles/064_Paper}
\includepaper{GENRE ONTOLOGY LEARNING: COMPARING CURATED WITH CROWD-SOURCED ONTOLOGIES}{Hendrik Schreiber}{articles/074_Paper}
\includepaper{Improving voice separation by better connecting contigs}{"Nicolas Guiomard-Kagan, Mathieu Giraud, Richard Groult and Florence Levé"}{articles/129_Paper}
\includepaper{Querying XML Score Databases: XQuery is not Enough!}{"Raphael Fournier-S'niehotta, Philippe Rigaux and Nicolas Travers"}{articles/136_Paper}
\includepaper{Analysing Scattering-Based Music Content Analysis Systems: Where's the Music?}{"Francisco Rodríguez-Algarra, Bob L. Sturm and Hugo Maruri-Aguilar"}{articles/146_Paper}
\includepaper{ELUCIDATING USER BEHAVIOR IN MUSIC SERVICES THROUGH PERSONA AND GENDER}{"John Fuller, Lauren Hubener, Yea-Seul Kim and Jin Ha Lee"}{articles/205_Paper}
\includepaper{Improving Predictions of Derived Viewpoints in Multiple Viewpoints Systems}{Thomas Hedges and Geraint Wiggins}{articles/208_Paper}
\includepaper{Phrase-level Audio Segmentation of Jazz Improvisations Informed by Symbolic Data}{Jeff Gregorio and Youngmoo Kim}{articles/245_Paper}
\includepaper{Conversations with Expert Users in Music Retrieval and Research Challenges for Creative MIR}{Kristina Andersen and Peter Knees}{articles/246_Paper}
\includepaper{A comparison of melody extraction methods based on source-filter modelling}{"Juan J. Bosch, Rachel M. Bittner, Justin Salamon and Emilia Gómez"}{articles/256_Paper}
\includepaper{Large-Scale Organization of Hierarchical Music Analyses}{Phillip Kirlin}{articles/259_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Poster session 2}
\includepdf[pages=4,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Towards Template-Based Vibrato Analysis in Complex Music Signals}{"Jonathan Driedger, Stefan Balke, Sebastian Ewert and Meinard Mueller"}{articles/005_Paper}
\includepaper{"Automatic music recommendation systems: do demographic, profiling, and contextual features improve their performance?"}{Gabriel Vigliensoni and Ichiro Fujinaga}{articles/044_Paper}
\includepaper{Ensemble: A Hybrid Human-Machine System for Generating Melody Scores from Audio}{"Tim Tse, Justin Salamon, Alex Williams, Helga Jiang and Edith Law"}{articles/072_Paper}
\includepaper{An ontology for audio features}{"Alo Allik, György Fazekas and Mark Sandler"}{articles/077_Paper}
\includepaper{Predicting Missing Music Components with Bidirectional Long Short-Term Memory Neural Networks}{I-Ting Liu and Richard Randall}{articles/097_Paper}
\includepaper{Analysis of Vocal Imitations of Pitch Trajectories}{Jiajie Dai and Simon Dixon}{articles/127_Paper}
\includepaper{Whither the Design of Experiments in MIR?}{Bob L. Sturm}{articles/128_Paper}
\includepaper{Singing Voice Melody Transcription using Deep Neural Networks}{François Rigaud and Mathieu Radenen}{articles/163_Paper}
\includepaper{Musical Typicality: How Many Similar Songs Exist?}{"Tomoyasu Nakano, Daichi Mochihashi, Kazuyoshi Yoshii and Masataka Goto"}{articles/191_Paper}
\includepaper{Automatic Drum Transcription using Bi-directional Recurrent Neural Networks}{"Carl Southall, Ryan Stables and Jason Hockman"}{articles/217_Paper}
\includepaper{On the use of note onsets for improved lyrics-to-audio alignment}{"Georgi Dzhambazov, Ajay Srinivasamurthy, Sertan Sentürk and Xavier Serra"}{articles/243_Paper}
\includepaper{A higher-dimensional expansion of affective norms for English terms for music tagging}{"Michele Buccoli, Massimiliano Zanoni, György Fazekas, Augusto Sarti, Mark Sandler and Stefano Tubaro"}{articles/253_Paper}
\includepaper{Impact of Music on Decision Making in Quantitative Tasks}{"Elad Liebman, Peter Stone and Corey White"}{articles/272_Paper}
\includepaper{WiMIR: An Informetric Study on Women Authors in ISMIR}{"Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham and J. Stephen Downie"}{articles/283_Paper}
\includepaper{Aligned Hierarchies: A Multi-Scale Structure-Based Representation for Music-Based Data Streams}{Katherine M. Kinnaird}{articles/020_Paper}
\includepaper{Genre specific dictionaries for harmonic/percussive source separation}{"Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski and Gaël Richard"}{articles/042_Paper}
\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO_TEMPORAL MODULATIONS}{"Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi"}{articles/046_Paper}
\includepaper{TOWARDS EVALUATING MULTIPLE PREDOMINANT MELODY ANNOTATIONS IN JAZZ RECORDINGS}{"Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar and Meinard Mueller"}{articles/049_Paper}
\includepaper{Simultaneous Separation and Segmentation in Layered Music}{Prem Seetharaman and Bryan Pardo}{articles/057_Paper}
\includepaper{Composer Recognition based on 2D-Filtered Piano-Rolls}{"Gissel Velarde, Carlos Cancino Chacón, David Meredith, Weyde Tillman and Maaten Grachten"}{articles/063_Paper}
\includepaper{Bootstrapping a system for phoneme recognition and keyword spotting in unaccompanied singing}{Anna Kruspe}{articles/070_Paper}
\includepaper{A Methodology for Quality Assessment in Collaborative Score Libraries}{"Vincent Besson, Marco Gurrieri, Philippe Rigaux, Alice Tacaille and Virginie Thion"}{articles/076_Paper}
\includepaper{Transcribing Human Piano Performances Into Music Notation}{"Andrea Cogliati, David Temperley and Zhiyao Duan"}{articles/088_Paper}
\includepaper{Learning Invariants for Instrument Recognition}{Vincent Lostanlen and Carmine Emanuele Cella}{articles/093_Paper}
\includepaper{"Exploiting frequency, periodicity and harmonicity using advanced time-frequency concentration techniques for multipitch estimation of choir and symphony"}{"Li Su, Tsung-Ying Chuang and Yi-Hsuan Yang"}{articles/104_Paper}
\includepaper{A LATENT SPACE APPROACH TO LISTENING BEHAVIOR ANALYSIS}{"Chia-Hao Chung, Jing-Kai Lou and Homer Chen"}{articles/110_Paper}
\includepaper{Data-driven exploration of melodic structure in Hindustani music}{"Kaustuv Kanti Ganguli, Sankalp Gulati, Xavier Serra and Preeti Rao"}{articles/121_Paper}
\includepaper{learning temporal feature using deep neural network and its application to music genre classification}{Il-Young Jeong and Kyogu Lee}{articles/159_Paper}
\includepaper{Listen to Me – Don't Listen to Me: What Communities of Critics Tell Us About Music}{Ben Fields and Christophe Rhodes}{articles/173_Paper}
\includepaper{On the Potential of Simple Framewise Approaches to Piano Transcription}{"Rainer Kelz, Matthias Dorfer, Filip Korzeniowski, Sebastian Böck, Andreas Arzt and Gerhard Widmer"}{articles/179_Paper}
\includepaper{A Dataset for Automatic Practice Logging}{"R. Michael Winters, Siddharth Gururani and Alexander Lerch"}{articles/181_Paper}
\includepaper{Long-term reverberation modeling in under-determined audio source separation}{Romain Hennequin and François Rigaud}{articles/196_Paper}
\includepaper{Downbeat Detection with Conditional Random Fields and Deep Learned Features}{Simon Durand and Slim Essid}{articles/213_Paper}
\includepaper{Automatic Outlier Detection in Music Datasets}{"Yen-Cheng Lu, Chih-Wei Wu, Alexander Lerch and Chang-Tien Lu"}{articles/215_Paper}

\thispagestyle{empty}\cleardoublepage
\addcontentsline{toc}{section}{Poster session 3}
\includepdf[pages=8,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
\thispagestyle{empty}\cleardoublepage

\includepaper{Cross-collection evaluation for music classification tasks}{"Dmitry Bogdanov, Alastair Porter, Perfecto Herrera and Xavier Serra"}{articles/220_Paper}
\includepaper{I Said it First: Topological Analysis of Lyrical Influence Networks}{Jack Atherton and Blair Kaneshiro}{articles/221_Paper}
\includepaper{Exploring Customer Reviews for Music Genre Classification and Evolutionary Studies}{"Sergio Oramas, Luis Espinosa-Anke, Aonghus Lawlor, Horacio Saggion and Xavier Serra"}{articles/240_Paper}
\includepaper{DOWNBEAT TRACKING USING BEAT SYNCHRONOUS FEATURES WITH RECURRENT NEURAL NETWORKS}{"Florian Krebs, Sebastian Böck, Matthias Dorfer and Gerhard Widmer"}{articles/249_Paper}
\includepaper{Learning and Visualizing Music Specifications Using Pattern Graphs}{"Rafael Valle, Alexandre Donzé, Daniel J. Fremont, Ilge Akkaya, Sanjit A. Seshia and Adrian Freed"}{articles/280_Paper}
\includepaper{AVA: An Interactive System for Visual and Quantitative Analyses of Vibrato and Portamento Performance Styles}{"Luwei Yang, Elaine Chew and Khalid Z. Rajab"}{articles/314_Paper}
\includepaper{"A Hierarchical Bayesian Model of Chords, Pitches, and Spectrograms for Multipitch Analysis"}{"Yuta Ojima, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii"}{articles/003_Paper}
\includepaper{Symbolic Meter Detection using Inner Metric Analysis}{W. Bas de Haas and Anja Volk}{articles/033_Paper}
\includepaper{CROSS TASK STUDY ON MIREX RECENT RESULTS: AN INDEX FOR EVOLUTION MEASUREMENT AND SOME STAGNATION HYPOTHESES}{"Ricardo Scholz, Geber Ramalho and Giordano Cabral"}{articles/054_Paper}
\includepaper{Towards Modeling and Decomposing Loop-Based Electronic Music}{"Patricio López-Serrano, Christian Dittmar, Jonathan Driedger and Meinard Mueller"}{articles/065_Paper}
\includepaper{Human-Interactive Optical Music Recognition}{"Liang Chen, Erik Stolterman and Christopher Raphael"}{articles/106_Paper}
\includepaper{A corpus of annotated Irish traditional dance music recordings: design and benchmark evaluations}{"Pierre Beauguitte, Bryan Duggan and John Kelleher"}{articles/148_Paper}
\includepaper{Jazz Expressive Performance Modeling}{"Helena Bantulà, Sergio Giraldo and Rafael Ramírez"}{articles/162_Paper}
\includepaper{Landmark-based Audio Fingerprinting for DJ Mix Monitoring}{"Reinhard Sonnleitner, Andreas Arzt and Gerhard Widmer"}{articles/187_Paper}
\includepaper{Mining Online Music Listening Trajectories}{"Flavio Figueiredo, Bruno Ribeiro, Jussara M. Almeida, Nazareno Andrade and Christos Faloutsos"}{articles/193_Paper}
\includepaper{Good-sounds.org: a framework to explore goodness in instrumental sounds}{"Giuseppe Bandiera, Oriol Romani Picas and Xavier Serra"}{articles/199_Paper}
\includepaper{Adaptive Frequency Neural Networks for Dynamic Pulse and Metre Perception}{"Andrew Lambert, Tillman Weyde and Newton Armstrong"}{articles/228_Paper}
\includepaper{Integration and Quality Assessment of Heterogeneous Chord Sequences using Data Fusion}{"Hendrik Vincent Koops, W. Bas de Haas, Dimitrios Bountouridis and Anja Volk"}{articles/019_Paper}
\includepaper{Can Microblogs Predict Music Charts? An Analysis of the Relationship between #Nowplaying Tweets and Music Charts}{"Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht"}{articles/039_Paper}
\includepaper{Mixtape: Direction-based navigation in large music collections}{"Joao Paulo V. Cardoso, Luciana Fujii Pontello, Pedro H. F. Holanda, Bruno Guilherme, Olga Goussevskaia and Ana Paula Couto da SIlva"}{articles/155_Paper}
\includepaper{An Evaluation Framework and Case Study for Rhythmic Concatenative Synthesis}{"Cárthach Ó Nuanáin, Perfecto Herrera and Sergi Jordà"}{articles/180_Paper}
\includepaper{Interactive Scores in Classical Music Production}{"Simon Waloschek, Axel Berndt, Benjamin W. Bohl and Aristotelis Hadjakos"}{articles/192_Paper}
\includepaper{An Analysis of Agreement in Classical Music Perception and Its Relationship to Listener Characteristics}{"Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez and Marko Tkalcic"}{articles/260_Paper}
\includepaper{STRUCTURAL SEGMENTATION AND VISUALIZATION OF SITAR AND SAROD CONCERT AUDIO}{"Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli and Preeti Rao"}{articles/151_Paper}
\includepaper{Minimax Viterbi algorithm for HMM-based Guitar fingering decision}{Gen Hori and Shigeki Sagayama}{articles/285_Paper}

### 2016-06-30 deriveFiles.py

@@ -1,0 +1,74 @@
+#!/usr/bin/python
+
+"""Split up master list of paper titles, authors, and sessions
+(completePaperList.csv) into the various files needed by Meinard's
+scripts for generating the pdf proceedings (papers.tex) and the
+electronic proceedings.
+
+"""
+
+import csv
+import codecs
+import io
+
+def unicode_csv_reader(utf8_data, dialect="excel", **kwargs):
+    """This function will read a csv file and will interpret the
+    contained data as utf-8.
+
+    """
+    #csv_reader = csv.reader(utf8_data, dialect=dialect, **kwargs)
+    csv_reader = csv.reader(utf8_data, **kwargs)
+    for row in csv_reader:
+        yield [unicode(cell, 'utf-8') for cell in row]
+
+def unicode_tsv_reader(utf8file):
+    "Generator for reading a tab-delimited file"
+    for line in utf8file.readlines():
+        #yield [cell for cell in unicode(line, 'utf-8').rstrip('\n\r').split('\t')]
+        yield [cell for cell in line.rstrip('\n\r').split('\t')]
+        
+def generatePapersDotTex(csvFile):
+    lastSession = ""
+    sessionInfo = loadSessionInfo()
+    # with io.open('2016_Proceedings_ISMIR/papers.tex', 'w', encoding='utf-8') as papersDotTex:
+    # with codecs.open('2016_Proceedings_ISMIR/papers.tex', 'w', 'utf-8') as papersDotTex:
+    with open('2016_Proceedings_ISMIR/papers.tex', 'w') as papersDotTex:
+        for title, authors, number, session in unicode_tsv_reader(csvFile):
+            if session != lastSession:
+                name, page = sessionInfo[session]
+                papersDotTex.write(papersSectionHeader(name, page))
+            lastSession = session
+            
+            papersDotTex.write('\includepaper{%s}{%s}{articles/%03d_Paper}\n'
+                               % (title, authors, int(number)))
+
+
+def papersSectionHeader(name, page):
+    chunk = """
+
+\\thispagestyle{empty}\\cleardoublepage
+\\addcontentsline{toc}{section}{%s}
+\\includepdf[pages=%s,pagecommand=\\thispagestyle{empty}]{external/12_Sessions.pdf}%%
+\\thispagestyle{empty}\\cleardoublepage
+
+""" % (name, page)
+    return chunk
+
+def loadSessionInfo():
[…]

### 2016-06-30 2016_Proceedings_ISMIR/papers.tex
fixed unicode issue by fixing csv file

@@
 \includepaper{Learning to Pinpoint Singing Voice from Weakly Labeled Examples}{Jan Schlüter}{articles/315_Paper}
-\includepaper{SiMPle: Assessing Music Similarity Using Subsequences Joins}{"Diego Silva, Chin-Chia Michael Yeh, Gustavo Batista and Eamonn Keogh"}{articles/099_Paper}
+\includepaper{SiMPle: Assessing Music Similarity Using Subsequences Joins}{Diego Silva, Chin-Chia Michael Yeh, Gustavo Batista and Eamonn Keogh}{articles/099_Paper}
 \includepaper{Feature Learning for Chord Recognition: The Deep Chroma Extractor}{Filip Korzeniowski and Gerhard Widmer}{articles/178_Paper}
-\includepaper{Brain Beats: Tempo Extraction from EEG Data}{"Sebastian Stober, Thomas Praetzlich and Meinard Mueller"}{articles/022_Paper}
+\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Praetzlich and Meinard Mueller}{articles/022_Paper}
 
@@
 
-\includepaper{AUTOMATIC TAGGING USING DEEP CONVOLUTIONAL NEURAL NETWORKS}{"Keunwoo Choi, George Fazekas and Mark Sandler"}{articles/009_Paper}
-\includepaper{Analyzing Measure Annotations for Western Classical Music Recordings}{"Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz and Meinard Müller"}{articles/079_Paper}
-\includepaper{Score-Informed Identification of Missing and Extra Notes in Piano Recordings}{"Sebastian Ewert, Siying Wang, Meinard Mueller and Mark Sandler"}{articles/123_Paper}
-\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{"Sebastian Böck, Florian Krebs and Gerhard Widmer"}{articles/186_Paper}
+\includepaper{AUTOMATIC TAGGING USING DEEP CONVOLUTIONAL NEURAL NETWORKS}{Keunwoo Choi, George Fazekas and Mark Sandler}{articles/009_Paper}
+\includepaper{Analyzing Measure Annotations for Western Classical Music Recordings}{Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz and Meinard Müller}{articles/079_Paper}
+\includepaper{Score-Informed Identification of Missing and Extra Notes in Piano Recordings}{Sebastian Ewert, Siying Wang, Meinard Mueller and Mark Sandler}{articles/123_Paper}
+\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs and Gerhard Widmer}{articles/186_Paper}
 
@@
 
-\includepaper{Towards Reading Sheet Music}{"Matthias Dorfer, Andreas Arzt and Gerhard Widmer"}{articles/027_Paper}
-\includepaper{A plan for sustainable MIR evaluation}{"Brian McFee, Eric Humphrey and Julián Urbano"}{articles/257_Paper}
-\includepaper{Go With the Flow: When Listeners Use Music as Technology}{"Andrew Demetriou, Martha Larson and Cynthia C. S. Liem"}{articles/068_Paper}
+\includepaper{Towards Reading Sheet Music}{Matthias Dorfer, Andreas Arzt and Gerhard Widmer}{articles/027_Paper}
+\includepaper{A plan for sustainable MIR evaluation}{Brian McFee, Eric Humphrey and Julián Urbano}{articles/257_Paper}
+\includepaper{Go With the Flow: When Listeners Use Music as Technology}{Andrew Demetriou, Martha Larson and Cynthia C. S. Liem}{articles/068_Paper}
 
@@
 \includepaper{Automatic Melodic Reduction using a Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
-\includepaper{Singing Melody Extraction using Multi-Column Deep Neural Networks}{"Sangeun Kum, Changheun Oh and Juhan Nam"}{articles/119_Paper}
-\includepaper{Instrumental idiom in the 16th century: patterns in arrangements of vocal music}{"David Lewis, Tim Crawford and Daniel Müllensiefen"}{articles/165_Paper}
+\includepaper{Singing Melody Extraction using Multi-Column Deep Neural Networks}{Sangeun Kum, Changheun Oh and Juhan Nam}{articles/119_Paper}
+\includepaper{Instrumental idiom in the 16th century: patterns in arrangements of vocal music}{David Lewis, Tim Crawford and Daniel Müllensiefen}{articles/165_Paper}
 
@@
 
-\includepaper{Learning a feature space for world music style similarity}{"Maria Panteli, Emmanouil Benetos and Simon Dixon"}{articles/166_Paper}
+\includepaper{Learning a feature space for world music style similarity}{Maria Panteli, Emmanouil Benetos and Simon Dixon}{articles/166_Paper}
 \includepaper{Bayesian meter tracking on learned signal representations}{Andre Holzapfel and Thomas Grill}{articles/132_Paper}
@@
 
-\includepaper{A LOOK AT THE CLOUD FROM BOTH SIDES NOW: AN ANALYSIS OF CLOUD MUSIC SERVICE USAGE}{"Jin Ha Lee, Yea-Seul Kim and Chris Hubbles"}{articles/087_Paper}
+\includepaper{A LOOK AT THE CLOUD FROM BOTH SIDES NOW: AN ANALYSIS OF CLOUD MUSIC SERVICE USAGE}{Jin Ha Lee, Yea-Seul Kim and Chris Hubbles}{articles/087_Paper}
 \includepaper{A Hybrid Gaussian-HMM-Deep Learning Approach For Automatic Chord Estimation With Very Large Vocabulary}{Junqi Deng and Yu-Kwong Kwok}{articles/058_Paper}
@@
 
-\includepaper{TIME-DELAYED MELODY SURFACES FOR R_GA RECOGNITION}{"Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan _entürk and Xavier Serra"}{articles/030_Paper}
+\includepaper{TIME-DELAYED MELODY SURFACES FOR R_GA RECOGNITION}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan _entürk and Xavier Serra}{articles/030_Paper}
 \includepaper{ON PRACTICAL STRATEGIES OF MELODY INDEXING FOR QUERY BY HUMMING}{Bartlomiej Stasiak}{articles/089_Paper}
-\includepaper{Recurrent Neural Networks for Drum Transcription}{"Richard Vogl, Matthias Dorfer and Peter Knees"}{articles/269_Paper}
-\includepaper{Integer Programming Formulation of the Problem of Generating Milton Babbitt's All-partition Arrays}{"Tsubasa Tanaka, Brian Bemman and David Meredith"}{articles/034_Paper}
-\includepaper{Mining Musical Traits of Social Functions in Native American Music}{"Daniel Shanahan, Kerstin Neubarth and Darrell Conklin"}{articles/167_Paper}
+\includepaper{Recurrent Neural Networks for Drum Transcription}{Richard Vogl, Matthias Dorfer and Peter Knees}{articles/269_Paper}
+\includepaper{Integer Programming Formulation of the Problem of Generating Milton Babbitt's All-partition Arrays}{Tsubasa Tanaka, Brian Bemman and David Meredith}{articles/034_Paper}
+\includepaper{Mining Musical Traits of Social Functions in Native American Music}{Daniel Shanahan, Kerstin Neubarth and Darrell Conklin}{articles/167_Paper}
 \includepaper{Exploring The Latent Structure of Collaborations in Music Production}{Nazareno Andrade and Flavio Figueiredo}{articles/251_Paper}
-\includepaper{Musical Note Estimation for F0 Trajectories of Singing Voices based on a Bayesian Semi-beat-synchronous HMM}{"Ryo Nishikimi, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii"}{articles/004_Paper}
+\includepaper{Musical Note Estimation for F0 Trajectories of Singing Voices based on a Bayesian Semi-beat-synchronous HMM}{Ryo Nishikimi, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii}{articles/004_Paper}
 \includepaper{NOISE ROBUST MUSIC ARTIST RECOGNITION USING I-VECTOR FEATURES}{Hamid Eghbal-zadeh and Gerhard Widmer}{articles/037_Paper}
-\includepaper{Piano Transcription using an Exponential Decay Model}{"Tian Cheng, Matthias Mauch, Emmanouil Benetos and Simon Dixon"}{articles/085_Paper}
-\includepaper{Live Song ID: A Hashprint Approach}{"TJ Tsai, Thomas Praetzlich and Meinard Mueller"}{articles/098_Paper}
-\includepaper{Nonnegative tensor factorization with frequency modulation cues for blind audio source separation}{"Elliot Creager, Noah Stein and Roland Badeau"}{articles/103_Paper}
+\includepaper{Piano Transcription using an Exponential Decay Model}{Tian Cheng, Matthias Mauch, Emmanouil Benetos and Simon Dixon}{articles/085_Paper}
+\includepaper{Live Song ID: A Hashprint Approach}{TJ Tsai, Thomas Praetzlich and Meinard Mueller}{articles/098_Paper}
+\includepaper{Nonnegative tensor factorization with frequency modulation cues for blind audio source separation}{Elliot Creager, Noah Stein and Roland Badeau}{articles/103_Paper}
 \includepaper{On the evaluation of rhythmic and melodic descriptors}{Maria Panteli and Simon Dixon}{articles/161_Paper}
@@
 \includepaper{MusicDB: A Platform for Longitudinal Music Analytics}{Jeremy Hyrkas and Bill Howe}{articles/284_Paper}
-\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{"Jan Haji_, jr., Ji_í Novotn_, Pavel Pecina and Jaroslav Pokorn_"}{articles/289_Paper}
-\includepaper{Two (note) heads are better than one: pen-based multimodal interaction with music notation}{"Jorge Calvo-Zaragoza, David Rizo and Jose M. Iñesta"}{articles/006_Paper}
+\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{Jan Haji_, jr., Ji_í Novotn_, Pavel Pecina and Jaroslav Pokorn_}{articles/289_Paper}
+\includepaper{Two (note) heads are better than one: pen-based multimodal interaction with music notation}{Jorge Calvo-Zaragoza, David Rizo and Jose M. Iñesta}{articles/006_Paper}
 \includepaper{Music Structural Segmentation Across Genres with Gammatone Features}{Mi Tian and Mark B. Sandler}{articles/032_Paper}
-\includepaper{Enhancing cover song identification with hierarchical rank aggregation}{"Julien Osmalskyj, Marc Van Droogenbroeck and Jean-Jacques Embrechts"}{articles/064_Paper}
+\includepaper{Enhancing cover song identification with hierarchical rank aggregation}{Julien Osmalskyj, Marc Van Droogenbroeck and Jean-Jacques Embrechts}{articles/064_Paper}
 \includepaper{GENRE ONTOLOGY LEARNING: COMPARING CURATED WITH CROWD-SOURCED ONTOLOGIES}{Hendrik Schreiber}{articles/074_Paper}
-\includepaper{Improving voice separation by better connecting contigs}{"Nicolas Guiomard-Kagan, Mathieu Giraud, Richard Groult and Florence Levé"}{articles/129_Paper}
-\includepaper{Querying XML Score Databases: XQuery is not Enough!}{"Raphael Fournier-S'niehotta, Philippe Rigaux and Nicolas Travers"}{articles/136_Paper}
-\includepaper{Analysing Scattering-Based Music Content Analysis Systems: Where's the Music?}{"Francisco Rodríguez-Algarra, Bob L. Sturm and Hugo Maruri-Aguilar"}{articles/146_Paper}
-\includepaper{ELUCIDATING USER BEHAVIOR IN MUSIC SERVICES THROUGH PERSONA AND GENDER}{"John Fuller, Lauren Hubener, Yea-Seul Kim and Jin Ha Lee"}{articles/205_Paper}
+\includepaper{Improving voice separation by better connecting contigs}{Nicolas Guiomard-Kagan, Mathieu Giraud, Richard Groult and Florence Levé}{articles/129_Paper}
+\includepaper{Querying XML Score Databases: XQuery is not Enough!}{Raphael Fournier-S'niehotta, Philippe Rigaux and Nicolas Travers}{articles/136_Paper}
+\includepaper{Analysing Scattering-Based Music Content Analysis Systems: Where's the Music?}{Francisco Rodríguez-Algarra, Bob L. Sturm and Hugo Maruri-Aguilar}{articles/146_Paper}
+\includepaper{ELUCIDATING USER BEHAVIOR IN MUSIC SERVICES THROUGH PERSONA AND GENDER}{John Fuller, Lauren Hubener, Yea-Seul Kim and Jin Ha Lee}{articles/205_Paper}
 \includepaper{Improving Predictions of Derived Viewpoints in Multiple Viewpoints Systems}{Thomas Hedges and Geraint Wiggins}{articles/208_Paper}
@@
 \includepaper{Conversations with Expert Users in Music Retrieval and Research Challenges for Creative MIR}{Kristina Andersen and Peter Knees}{articles/246_Paper}
-\includepaper{A comparison of melody extraction methods based on source-filter modelling}{"Juan J. Bosch, Rachel M. Bittner, Justin Salamon and Emilia Gómez"}{articles/256_Paper}
+\includepaper{A comparison of melody extraction methods based on source-filter modelling}{Juan J. Bosch, Rachel M. Bittner, Justin Salamon and Emilia Gómez}{articles/256_Paper}
 \includepaper{Large-Scale Organization of Hierarchical Music Analyses}{Phillip Kirlin}{articles/259_Paper}
@@
 
-\includepaper{Towards Template-Based Vibrato Analysis in Complex Music Signals}{"Jonathan Driedger, Stefan Balke, Sebastian Ewert and Meinard Mueller"}{articles/005_Paper}
-\includepaper{"Automatic music recommendation systems: do demographic, profiling, and contextual features improve their performance?"}{Gabriel Vigliensoni and Ichiro Fujinaga}{articles/044_Paper}
-\includepaper{Ensemble: A Hybrid Human-Machine System for Generating Melody Scores from Audio}{"Tim Tse, Justin Salamon, Alex Williams, Helga Jiang and Edith Law"}{articles/072_Paper}
-\includepaper{An ontology for audio features}{"Alo Allik, György Fazekas and Mark Sandler"}{articles/077_Paper}
+\includepaper{Towards Template-Based Vibrato Analysis in Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert and Meinard Mueller}{articles/005_Paper}
+\includepaper{Automatic music recommendation systems: do demographic, profiling, and contextual features improve their performance?}{Gabriel Vigliensoni and Ichiro Fujinaga}{articles/044_Paper}
+\includepaper{Ensemble: A Hybrid Human-Machine System for Generating Melody Scores from Audio}{Tim Tse, Justin Salamon, Alex Williams, Helga Jiang and Edith Law}{articles/072_Paper}
+\includepaper{An ontology for audio features}{Alo Allik, György Fazekas and Mark Sandler}{articles/077_Paper}
 \includepaper{Predicting Missing Music Components with Bidirectional Long Short-Term Memory Neural Networks}{I-Ting Liu and Richard Randall}{articles/097_Paper}
@@
 \includepaper{Singing Voice Melody Transcription using Deep Neural Networks}{François Rigaud and Mathieu Radenen}{articles/163_Paper}
-\includepaper{Musical Typicality: How Many Similar Songs Exist?}{"Tomoyasu Nakano, Daichi Mochihashi, Kazuyoshi Yoshii and Masataka Goto"}{articles/191_Paper}
-\includepaper{Automatic Drum Transcription using Bi-directional Recurrent Neural Networks}{"Carl Southall, Ryan Stables and Jason Hockman"}{articles/217_Paper}
-\includepaper{On the use of note onsets for improved lyrics-to-audio alignment}{"Georgi Dzhambazov, Ajay Srinivasamurthy, Sertan Sentürk and Xavier Serra"}{articles/243_Paper}
-\includepaper{A higher-dimensional expansion of affective norms for English terms for music tagging}{"Michele Buccoli, Massimiliano Zanoni, György Fazekas, Augusto Sarti, Mark Sandler and Stefano Tubaro"}{articles/253_Paper}
-\includepaper{Impact of Music on Decision Making in Quantitative Tasks}{"Elad Liebman, Peter Stone and Corey White"}{articles/272_Paper}
-\includepaper{WiMIR: An Informetric Study on Women Authors in ISMIR}{"Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham and J. Stephen Downie"}{articles/283_Paper}
+\includepaper{Musical Typicality: How Many Similar Songs Exist?}{Tomoyasu Nakano, Daichi Mochihashi, Kazuyoshi Yoshii and Masataka Goto}{articles/191_Paper}
+\includepaper{Automatic Drum Transcription using Bi-directional Recurrent Neural Networks}{Carl Southall, Ryan Stables and Jason Hockman}{articles/217_Paper}
+\includepaper{On the use of note onsets for improved lyrics-to-audio alignment}{Georgi Dzhambazov, Ajay Srinivasamurthy, Sertan Sentürk and Xavier Serra}{articles/243_Paper}
+\includepaper{A higher-dimensional expansion of affective norms for English terms for music tagging}{Michele Buccoli, Massimiliano Zanoni, György Fazekas, Augusto Sarti, Mark Sandler and Stefano Tubaro}{articles/253_Paper}
+\includepaper{Impact of Music on Decision Making in Quantitative Tasks}{Elad Liebman, Peter Stone and Corey White}{articles/272_Paper}
+\includepaper{WiMIR: An Informetric Study on Women Authors in ISMIR}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham and J. Stephen Downie}{articles/283_Paper}
 \includepaper{Aligned Hierarchies: A Multi-Scale Structure-Based Representation for Music-Based Data Streams}{Katherine M. Kinnaird}{articles/020_Paper}
-\includepaper{Genre specific dictionaries for harmonic/percussive source separation}{"Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski and Gaël Richard"}{articles/042_Paper}
-\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO_TEMPORAL MODULATIONS}{"Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi"}{articles/046_Paper}
-\includepaper{TOWARDS EVALUATING MULTIPLE PREDOMINANT MELODY ANNOTATIONS IN JAZZ RECORDINGS}{"Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar and Meinard Mueller"}{articles/049_Paper}
+\includepaper{Genre specific dictionaries for harmonic/percussive source separation}{Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski and Gaël Richard}{articles/042_Paper}
+\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO_TEMPORAL MODULATIONS}{Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi}{articles/046_Paper}
+\includepaper{TOWARDS EVALUATING MULTIPLE PREDOMINANT MELODY ANNOTATIONS IN JAZZ RECORDINGS}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar and Meinard Mueller}{articles/049_Paper}
 \includepaper{Simultaneous Separation and Segmentation in Layered Music}{Prem Seetharaman and Bryan Pardo}{articles/057_Paper}
-\includepaper{Composer Recognition based on 2D-Filtered Piano-Rolls}{"Gissel Velarde, Carlos Cancino Chacón, David Meredith, Weyde Tillman and Maaten Grachten"}{articles/063_Paper}
+\includepaper{Composer Recognition based on 2D-Filtered Piano-Rolls}{Gissel Velarde, Carlos Cancino Chacón, David Meredith, Weyde Tillman and Maaten Grachten}{articles/063_Paper}
 \includepaper{Bootstrapping a system for phoneme recognition and keyword spotting in unaccompanied singing}{Anna Kruspe}{articles/070_Paper}
-\includepaper{A Methodology for Quality Assessment in Collaborative Score Libraries}{"Vincent Besson, Marco Gurrieri, Philippe Rigaux, Alice Tacaille and Virginie Thion"}{articles/076_Paper}
-\includepaper{Transcribing Human Piano Performances Into Music Notation}{"Andrea Cogliati, David Temperley and Zhiyao Duan"}{articles/088_Paper}
+\includepaper{A Methodology for Quality Assessment in Collaborative Score Libraries}{Vincent Besson, Marco Gurrieri, Philippe Rigaux, Alice Tacaille and Virginie Thion}{articles/076_Paper}
+\includepaper{Transcribing Human Piano Performances Into Music Notation}{Andrea Cogliati, David Temperley and Zhiyao Duan}{articles/088_Paper}
 \includepaper{Learning Invariants for Instrument Recognition}{Vincent Lostanlen and Carmine Emanuele Cella}{articles/093_Paper}
-\includepaper{"Exploiting frequency, periodicity and harmonicity using advanced time-frequency concentration techniques for multipitch estimation of choir and symphony"}{"Li Su, Tsung-Ying Chuang and Yi-Hsuan Yang"}{articles/104_Paper}
-\includepaper{A LATENT SPACE APPROACH TO LISTENING BEHAVIOR ANALYSIS}{"Chia-Hao Chung, Jing-Kai Lou and Homer Chen"}{articles/110_Paper}
-\includepaper{Data-driven exploration of melodic structure in Hindustani music}{"Kaustuv Kanti Ganguli, Sankalp Gulati, Xavier Serra and Preeti Rao"}{articles/121_Paper}
+\includepaper{Exploiting frequency, periodicity and harmonicity using advanced time-frequency concentration techniques for multipitch estimation of choir and symphony}{Li Su, Tsung-Ying Chuang and Yi-Hsuan Yang}{articles/104_Paper}
+\includepaper{A LATENT SPACE APPROACH TO LISTENING BEHAVIOR ANALYSIS}{Chia-Hao Chung, Jing-Kai Lou and Homer Chen}{articles/110_Paper}
+\includepaper{Data-driven exploration of melodic structure in Hindustani music}{Kaustuv Kanti Ganguli, Sankalp Gulati, Xavier Serra and Preeti Rao}{articles/121_Paper}
 \includepaper{learning temporal feature using deep neural network and its application to music genre classification}{Il-Young Jeong and Kyogu Lee}{articles/159_Paper}
 \includepaper{Listen to Me – Don't Listen to Me: What Communities of Critics Tell Us About Music}{Ben Fields and Christophe Rhodes}{articles/173_Paper}
-\includepaper{On the Potential of Simple Framewise Approaches to Piano Transcription}{"Rainer Kelz, Matthias Dorfer, Filip Korzeniowski, Sebastian Böck, Andreas Arzt and Gerhard Widmer"}{articles/179_Paper}
-\includepaper{A Dataset for Automatic Practice Logging}{"R. Michael Winters, Siddharth Gururani and Alexander Lerch"}{articles/181_Paper}
+\includepaper{On the Potential of Simple Framewise Approaches to Piano Transcription}{Rainer Kelz, Matthias Dorfer, Filip Korzeniowski, Sebastian Böck, Andreas Arzt and Gerhard Widmer}{articles/179_Paper}
+\includepaper{A Dataset for Automatic Practice Logging}{R. Michael Winters, Siddharth Gururani and Alexander Lerch}{articles/181_Paper}
 \includepaper{Long-term reverberation modeling in under-determined audio source separation}{Romain Hennequin and François Rigaud}{articles/196_Paper}
 \includepaper{Downbeat Detection with Conditional Random Fields and Deep Learned Features}{Simon Durand and Slim Essid}{articles/213_Paper}
-\includepaper{Automatic Outlier Detection in Music Datasets}{"Yen-Cheng Lu, Chih-Wei Wu, Alexander Lerch and Chang-Tien Lu"}{articles/215_Paper}
+\includepaper{Automatic Outlier Detection in Music Datasets}{Yen-Cheng Lu, Chih-Wei Wu, Alexander Lerch and Chang-Tien Lu}{articles/215_Paper}
 
@@
 
-\includepaper{Cross-collection evaluation for music classification tasks}{"Dmitry Bogdanov, Alastair Porter, Perfecto Herrera and Xavier Serra"}{articles/220_Paper}
+\includepaper{Cross-collection evaluation for music classification tasks}{Dmitry Bogdanov, Alastair Porter, Perfecto Herrera and Xavier Serra}{articles/220_Paper}
 \includepaper{I Said it First: Topological Analysis of Lyrical Influence Networks}{Jack Atherton and Blair Kaneshiro}{articles/221_Paper}
-\includepaper{Exploring Customer Reviews for Music Genre Classification and Evolutionary Studies}{"Sergio Oramas, Luis Espinosa-Anke, Aonghus Lawlor, Horacio Saggion and Xavier Serra"}{articles/240_Paper}
-\includepaper{DOWNBEAT TRACKING USING BEAT SYNCHRONOUS FEATURES WITH RECURRENT NEURAL NETWORKS}{"Florian Krebs, Sebastian Böck, Matthias Dorfer and Gerhard Widmer"}{articles/249_Paper}
-\includepaper{Learning and Visualizing Music Specifications Using Pattern Graphs}{"Rafael Valle, Alexandre Donzé, Daniel J.
-Fremont, Ilge Akkaya, Sanjit A.
-Seshia and Adrian Freed"}{articles/280_Paper}
-\includepaper{AVA: An Interactive System for Visual and Quantitative Analyses of Vibrato and Portamento Performance Styles}{"Luwei Yang, Elaine Chew and Khalid Z. Rajab"}{articles/314_Paper}
-\includepaper{"A Hierarchical Bayesian Model of Chords, Pitches, and Spectrograms for Multipitch Analysis"}{"Yuta Ojima, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii"}{articles/003_Paper}
+\includepaper{Exploring Customer Reviews for Music Genre Classification and Evolutionary Studies}{Sergio Oramas, Luis Espinosa-Anke, Aonghus Lawlor, Horacio Saggion and Xavier Serra}{articles/240_Paper}
+\includepaper{DOWNBEAT TRACKING USING BEAT SYNCHRONOUS FEATURES WITH RECURRENT NEURAL NETWORKS}{Florian Krebs, Sebastian Böck, Matthias Dorfer and Gerhard Widmer}{articles/249_Paper}
+\includepaper{Learning and Visualizing Music Specifications Using Pattern Graphs}{Rafael Valle, Alexandre Donzé, Daniel J. Fremont, Ilge Akkaya, Sanjit A. Seshia and Adrian Freed}{articles/280_Paper}
+\includepaper{AVA: An Interactive System for Visual and Quantitative Analyses of Vibrato and Portamento Performance Styles}{Luwei Yang, Elaine Chew and Khalid Z. Rajab}{articles/314_Paper}
+\includepaper{A Hierarchical Bayesian Model of Chords, Pitches, and Spectrograms for Multipitch Analysis}{Yuta Ojima, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii}{articles/003_Paper}
 \includepaper{Symbolic Meter Detection using Inner Metric Analysis}{W. Bas de Haas and Anja Volk}{articles/033_Paper}
-\includepaper{CROSS TASK STUDY ON MIREX RECENT RESULTS: AN INDEX FOR EVOLUTION MEASUREMENT AND SOME STAGNATION HYPOTHESES}{"Ricardo Scholz, Geber Ramalho and Giordano Cabral"}{articles/054_Paper}
-\includepaper{Towards Modeling and Decomposing Loop-Based Electronic Music}{"Patricio López-Serrano, Christian Dittmar, Jonathan Driedger and Meinard Mueller"}{articles/065_Paper}
-\includepaper{Human-Interactive Optical Music Recognition}{"Liang Chen, Erik Stolterman and Christopher Raphael"}{articles/106_Paper}
-\includepaper{A corpus of annotated Irish traditional dance music recordings: design and benchmark evaluations}{"Pierre Beauguitte, Bryan Duggan and John Kelleher"}{articles/148_Paper}
-\includepaper{Jazz Expressive Performance Modeling}{"Helena Bantulà, Sergio Giraldo and Rafael Ramírez"}{articles/162_Paper}
-\includepaper{Landmark-based Audio Fingerprinting for DJ Mix Monitoring}{"Reinhard Sonnleitner, Andreas Arzt and Gerhard Widmer"}{articles/187_Paper}
-\includepaper{Mining Online Music Listening Trajectories}{"Flavio Figueiredo, Bruno Ribeiro, Jussara M. Almeida, Nazareno Andrade and Christos Faloutsos"}{articles/193_Paper}
-\includepaper{Good-sounds.org: a framework to explore goodness in instrumental sounds}{"Giuseppe Bandiera, Oriol Romani Picas and Xavier Serra"}{articles/199_Paper}
-\includepaper{Adaptive Frequency Neural Networks for Dynamic Pulse and Metre Perception}{"Andrew Lambert, Tillman Weyde and Newton Armstrong"}{articles/228_Paper}
-\includepaper{Integration and Quality Assessment of Heterogeneous Chord Sequences using Data Fusion}{"Hendrik Vincent Koops, W. Bas de Haas, Dimitrios Bountouridis and Anja Volk"}{articles/019_Paper}
+\includepaper{CROSS TASK STUDY ON MIREX RECENT RESULTS: AN INDEX FOR EVOLUTION MEASUREMENT AND SOME STAGNATION HYPOTHESES}{Ricardo Scholz, Geber Ramalho and Giordano Cabral}{articles/054_Paper}
+\includepaper{Towards Modeling and Decomposing Loop-Based Electronic Music}{Patricio López-Serrano, Christian Dittmar, Jonathan Driedger and Meinard Mueller}{articles/065_Paper}
+\includepaper{Human-Interactive Optical Music Recognition}{Liang Chen, Erik Stolterman and Christopher Raphael}{articles/106_Paper}
+\includepaper{A corpus of annotated Irish traditional dance music recordings: design and benchmark evaluations}{Pierre Beauguitte, Bryan Duggan and John Kelleher}{articles/148_Paper}
+\includepaper{Jazz Expressive Performance Modeling}{Helena Bantulà, Sergio Giraldo and Rafael Ramírez}{articles/162_Paper}
+\includepaper{Landmark-based Audio Fingerprinting for DJ Mix Monitoring}{Reinhard Sonnleitner, Andreas Arzt and Gerhard Widmer}{articles/187_Paper}
+\includepaper{Mining Online Music Listening Trajectories}{Flavio Figueiredo, Bruno Ribeiro, Jussara M. Almeida, Nazareno Andrade and Christos Faloutsos}{articles/193_Paper}
+\includepaper{Good-sounds.org: a framework to explore goodness in instrumental sounds}{Giuseppe Bandiera, Oriol Romani Picas and Xavier Serra}{articles/199_Paper}
+\includepaper{Adaptive Frequency Neural Networks for Dynamic Pulse and Metre Perception}{Andrew Lambert, Tillman Weyde and Newton Armstrong}{articles/228_Paper}
+\includepaper{Integration and Quality Assessment of Heterogeneous Chord Sequences using Data Fusion}{Hendrik Vincent Koops, W. Bas de Haas, Dimitrios Bountouridis and Anja Volk}{articles/019_Paper}
 \includepaper{Can Microblogs Predict Music Charts?
-An Analysis of the Relationship between #Nowplaying Tweets and Music Charts}{"Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht"}{articles/039_Paper}
-\includepaper{Mixtape: Direction-based navigation in large music collections}{"Joao Paulo V.
+An Analysis of the Relationship between #Nowplaying Tweets and Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht}{articles/039_Paper}
+\includepaper{Mixtape: Direction-based navigation in large music collections}{Joao Paulo V.
 Cardoso, Luciana Fujii Pontello, Pedro H.
 F.
-Holanda, Bruno Guilherme, Olga Goussevskaia and Ana Paula Couto da SIlva"}{articles/155_Paper}
-\includepaper{An Evaluation Framework and Case Study for Rhythmic Concatenative Synthesis}{"Cárthach Ó Nuanáin, Perfecto Herrera and Sergi Jordà"}{articles/180_Paper}
-\includepaper{Interactive Scores in Classical Music Production}{"Simon Waloschek, Axel Berndt, Benjamin W. Bohl and Aristotelis Hadjakos"}{articles/192_Paper}
-\includepaper{An Analysis of Agreement in Classical Music Perception and Its Relationship to Listener Characteristics}{"Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez and Marko Tkalcic"}{articles/260_Paper}
-\includepaper{STRUCTURAL SEGMENTATION AND VISUALIZATION OF SITAR AND SAROD CONCERT AUDIO}{"Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli and Preeti Rao"}{articles/151_Paper}
+Holanda, Bruno Guilherme, Olga Goussevskaia and Ana Paula Couto da SIlva}{articles/155_Paper}
+\includepaper{An Evaluation Framework and Case Study for Rhythmic Concatenative Synthesis}{Cárthach Ó Nuanáin, Perfecto Herrera and Sergi Jordà}{articles/180_Paper}
+\includepaper{Interactive Scores in Classical Music Production}{Simon Waloschek, Axel Berndt, Benjamin W. Bohl and Aristotelis Hadjakos}{articles/192_Paper}
+\includepaper{An Analysis of Agreement in Classical Music Perception and Its Relationship to Listener Characteristics}{Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez and Marko Tkalcic}{articles/260_Paper}
+\includepaper{STRUCTURAL SEGMENTATION AND VISUALIZATION OF SITAR AND SAROD CONCERT AUDIO}{Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli and Preeti Rao}{articles/151_Paper}
 \includepaper{Minimax Viterbi algorithm for HMM-based Guitar fingering decision}{Gen Hori and Shigeki Sagayama}{articles/285_Paper}

### 2016-07-01 deriveFiles.py
write electronic tools data files based on main input file

@@ -8,8 +8,8 @@ electronic proceedings.
 """
 
 import csv
-import codecs
-import io
+import collections
+import os
 
 def unicode_csv_reader(utf8_data, dialect="excel", **kwargs):
     """This function will read a csv file and will interpret the
@@ -21,11 +21,12 @@ def unicode_csv_reader(utf8_data, dialect="excel", **kwargs):
     for row in csv_reader:
         yield [unicode(cell, 'utf-8') for cell in row]
 
-def unicode_tsv_reader(utf8file):
+def unicode_tsv_reader(utf8FileName):
     "Generator for reading a tab-delimited file"
-    for line in utf8file.readlines():
-        #yield [cell for cell in unicode(line, 'utf-8').rstrip('\n\r').split('\t')]
-        yield [cell for cell in line.rstrip('\n\r').split('\t')]
+    with open(utf8FileName) as utf8file:
+        for line in utf8file.readlines():
+            #yield [cell for cell in unicode(line, 'utf-8').rstrip('\n\r').split('\t')]
+            yield [cell for cell in line.rstrip('\n\r').split('\t')]
         
 def generatePapersDotTex(csvFile):
     lastSession = ""
@@ -55,17 +56,50 @@ def papersSectionHeader(name, page):
     return chunk
 
 def loadSessionInfo():
-    with open('data/sessionInfo.csv') as csvFile:
-        return {k: (name, int(num)) for k, name, num in unicode_tsv_reader(csvFile)}
+    return {k: (name, int(num)) for k, name, num
+            in unicode_tsv_reader('data/sessionInfo.csv')}
 
+    
 def generateElectronicCsvFiles(csvFile):
-    pass
+    generateSessionIndex(csvFile)
+    generateSessionFiles(csvFile)
+    
+def generateSessionIndex(csvFile):
+    sessionInfo = loadSessionInfo()
+    fileName = '2016_Proceedings_ISMIR_Electronic_Tools/data/session_index.csv'
+    makeDirs(os.path.dirname(fileName))
+    with open(fileName, 'w') as sessionFile:
+        for session, (name, number) in sorted(sessionInfo.iteritems()):
+            sessionFile.write('%s;%s;%s\n' % (session, number, name))
+        
+def generateSessionFiles(csvFile):
+    sessionInfo = loadSessionInfo()
+    sessions = collections.defaultdict(list)
+    for title, authors, number, session in unicode_tsv_reader(csvFile):
+        sessions[session].append((title, authors, int(number)))
[…]

### 2016-07-02 2016_Proceedings_ISMIR/papers.tex
fixed compilation issues, switched to smaller times font for headers, footers, TOC, removed underscores from csv

@@
 
-\includepaper{TIME-DELAYED MELODY SURFACES FOR R_GA RECOGNITION}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan _entürk and Xavier Serra}{articles/030_Paper}
+\includepaper{TIME-DELAYED MELODY SURFACES FOR RAGA RECOGNITION}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan entürk and Xavier Serra}{articles/030_Paper}
 \includepaper{ON PRACTICAL STRATEGIES OF MELODY INDEXING FOR QUERY BY HUMMING}{Bartlomiej Stasiak}{articles/089_Paper}
@@
 \includepaper{MusicDB: A Platform for Longitudinal Music Analytics}{Jeremy Hyrkas and Bill Howe}{articles/284_Paper}
-\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{Jan Haji_, jr., Ji_í Novotn_, Pavel Pecina and Jaroslav Pokorn_}{articles/289_Paper}
+\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{Jan Haji, jr., Jií Novotn, Pavel Pecina and Jaroslav Pokorn}{articles/289_Paper}
 \includepaper{Two (note) heads are better than one: pen-based multimodal interaction with music notation}{Jorge Calvo-Zaragoza, David Rizo and Jose M. Iñesta}{articles/006_Paper}
@@
 \includepaper{Genre specific dictionaries for harmonic/percussive source separation}{Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski and Gaël Richard}{articles/042_Paper}
-\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO_TEMPORAL MODULATIONS}{Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi}{articles/046_Paper}
+\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO-TEMPORAL MODULATIONS}{Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi}{articles/046_Paper}
 \includepaper{TOWARDS EVALUATING MULTIPLE PREDOMINANT MELODY ANNOTATIONS IN JAZZ RECORDINGS}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar and Meinard Mueller}{articles/049_Paper}
@@
 \includepaper{Can Microblogs Predict Music Charts?
-An Analysis of the Relationship between #Nowplaying Tweets and Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht}{articles/039_Paper}
+An Analysis of the Relationship between \#Nowplaying Tweets and Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht}{articles/039_Paper}
 \includepaper{Mixtape: Direction-based navigation in large music collections}{Joao Paulo V.

### 2016-07-02 2016_Proceedings_ISMIR/00-run.sh

@@ -1,11 +1,10 @@
-#!/bin/bash -xuev
+#!/bin/bash
 
-rm -f 2016_Proceedings_ISMIR.aux
-rm -f 2016_Proceedings_ISMIR.ain
+rm -f 2016_Proceedings_ISMIR.{aux,ain,log,toc}
 pdflatex 2016_Proceedings_ISMIR.tex
 
 #ReplaceText.vbs 2016_Proceedings_ISMIR.aux "\IeC " ""
-sed -e 's/\IeC //g' 2016_Proceedings_ISMIR.aux > 2016_Proceedings_ISMIR_2.aux
+sed -e 's/\\IeC //g' 2016_Proceedings_ISMIR.aux > 2016_Proceedings_ISMIR_2.aux
 
 authorindex -d 2016_Proceedings_ISMIR_2.aux
 

### 2016-07-10 2016_Proceedings_ISMIR/tutorials.tex
updated list of paper info

--- 2016-06-29 2016_Proceedings_ISMIR/tutorials.tex
@@
 % Tutorial 1
-\includeabstract{Why Singing is Interesting}{Simon Dixon, Masataka Goto, Matthias Mauch}{external/11-1_Tutorial-1.pdf}
+\includeabstract{Jazz solo analysis between music information
+  retrieval, music psychology, and jazz research}{Jakob Abe{\ss}er,
+  Klaus Frieler, Wolf-Georg Zaddach}{The tutorial will consist of four parts.
+The first part sets the scene with a short run through jazz history and its main styles and an overview of the central musical elements in jazz.
+Out of this introduction, the main research questions will be derived, which cover jazz research and jazz historiography, analysis of musical style, performance research, and psychology of creative processes.
+Particularly, research issues as addressed in the Jazzomat Research Project will be discussed and results will be presented.
+
+The second part of the tutorial will deal with the details of the Weimar Jazz Database.
+Each solo encompasses pitch, onset, and offset time of the played tones as well as several additional annotations, e.g., manually tapped beat grids, chords, enumerations of sections and choruses as well as phrase segmentations.
+The process of creating the monophonic transcriptions will be explained (solo selection, transcription procedure, and quality management) and examples will be shown.
+Moreover, the underlying data-model of the Weimar Jazz Database, which includes symbolic data as well as data automatically extracted from the audio-files (e.g., intensity curves and beat-wise bass chroma) will be discussed in detail.
+
+In the third part, we will introduce our analysis tools MeloSpySuite and MeloSpyGUI, which allow the computation of a large set of currently over 500 symbolic features from monophonic melodies.
+These features quantify various tonal, harmonic, rhythmic, metrical, and structural properties of the solo melodies.
+In addition, pattern retrieval modules, based on n-gram representations and a two-stage search option using regular expressions, play an integral part for the extraction of motivic cells and formulas from jazz solos.
+All tools can be readily applied to other melodic datasets besides the Weimar Jazz Database.
+Several use cases will be demonstrated and research results will be discussed.
+
+The final part of the tutorial will focus on audio-based analysis of recorded jazz solo performances.
+We follow a score-informed analysis approach by using the solo transcriptions from the Weimar Jazz Database as prior information.
+This allows us to mitigate common problems in transcribing and analyzing polyphonic and multi-timbral audio such as overlapping instrument partials.
+A score-informed source separation algorithm is used to split the original recordings into a solo and an accompaniment track, which allows the tracking of f0-curves and intensity contours of the solo instrument.
+We will present the results of different analyses of the stylistic idiosyncrasies across well-known saxophone and trumpet players.
+Finally, we will briefly outline further potentials and challenges of score-informed MIR techniques.}{\paragraph{Jakob Abeßer} holds a degree in computer engineering (Dipl.-Ing.) from Ilmenau University of Technology.
+He is a postdoctoral researcher in the Semantic Music Technologies group at Fraunhofer IDMT and obtained a PhD degree (Dr.-Ing.) in Media Technology from Ilmenau University of Technology in 2014.
+During his PhD, he was a visiting researcher at the Finnish Centre of Excellence in Interdisciplinary Music Research, University of Jyväskylä, Finland in 2010.
+As a research scientist at Fraunhofer, he has experience with algorithm development in the fields of automatic music transcription, symbolic music analysis, machine learning, and music instrument recognition.
+Also, he works as a postdoctoral researcher at the University of Music in Weimar in the Jazzomat Research Project, focusing on analyzing jazz solo recordings using Music Information Retrieval technologies.
+
+\paragraph{Klaus Frieler} graduated in theoretical physics (diploma) and received a PhD in systematic musicology in 2008.
+In between, he worked several years as a freelance software developer before taking up a post as lecturer in systematic musicology at the University of Hamburg in 2008.
+In 2012, he had a short stint at the C4DM, Queen Mary University of London.
+Since the end of 2012, he is a post-doctoral researcher with the Jazzomat Research Project at the University of Music “Franz Liszt” Weimar.
+His main research interests are computational and statistical music psychology with a focus on creativity, melody perception, singing intonation, and jazz research.
+Since 2006, he also works as an independent music expert specializing in copyright cases.
+
+\paragraph{Wolf-Georg Zaddach} studied musicology, arts administration, and history in Weimar and Jena, music management and jazz guitar in Prague, Czech Republic.
+After finishing his Magister Artium with a thesis about jazz in Czechoslovakia in the 50s and 60s, he worked as assistant professor at the department of musicology in Weimar.
+Since 10/2012 he works at the jazz research project of Prof.
+Dr.
+Martin Pfleiderer.
+Since 02/2014, he holds a scholarship by the German National Academic Foundation (Studienstiftung des deutschen Volkes) for his Ph.D.
+about heavy and extreme metal in the 1980s GDR/East Germany.
+He frequently performs live and on records as a guitarist.}
 
 % Tutorial 2
-\includeabstract{Addressing the Music Information Needs of Musicologists}{Richard J.\ Lewis, Ben Fields, Tim Crawford}{external/11-2_Tutorial-2.pdf}
+\includeabstract{Music Information Retrieval: Overview, Recent
+  Developments and Future Challenges}{Emilia G\'omez, Markus Schedl,
+  Xavier Serra, Xiao Hu}{This tutorial provides a survey of the field of Music Information Retrieval (MIR), that aims, among other things, at automatically extracting semantically meaningful information from various representations of music entities, such as audio, scores, lyrics, web pages or microblogs.
+The tutorial is designed for students, engineers, researchers, and data scientists who are new to MIR and want to get introduced to the field.
+
+The tutorial will cover some of the main tasks in MIR, such as music identification, transcription, search by similarity, genre/mood/artist classification, query by humming, music recommendation, and playlist generation.
+We will review approaches based on content-based and context-based music description and show how MIR tasks are addressed from a user-centered and multicultural perspective.
+The tutorial will focus on latest developments and current challenges in the field.}{\paragraph{Emilia Gómez} is an Associate Professor (Serra-Hunter Fellow) at the Music Technology Group, Department of Information and Communication Technologies, Universitat Pompeu Fabra in Barcelona, Spain.
+She graduated as a Telecommunication Engineer at Universidad de Sevilla (Spain) and she studied classical piano performance at Seville Conservatoire of Music.
+She then received a DEA in Acoustics, Signal Processing and Computer Science applied to Music (ATIAM) at IRCAM, Paris (France) and a Ph.D.
+in Computer Science and Digital Communication at the UPF (awarded by EPSON foundation).
+Her research is within the Music Information Retrieval (MIR) field.
+She tries to understand and enhance music listening experiences by automatically extracting descriptors from music signals.
+She has designed algorithms able to describe music signals in terms of melody, tonality, and, by incorporating machine learning techniques, she has been able to model high-level concepts such as similarity, style or emotion.
+Emilia Gómez has co-authored more than a 100 publications in peer-reviewed scientific journals and conferences.
+She has contributed to more than 15 research projects, most of them funded by the European Commission and Spanish Government.
+She is elected member-at-large of the International Society for Music Information Retrieval (ISMIR).
+At the moment, she contributes to the COFLA project on computational analysis of flamenco music and she is the principal investigator for the European research project PHENICX, trying to innovate the way we experience classical music concerts.
+
+\paragraph{Markus Schedl} is an Associate Professor at the Johannes Kepler University Linz / Department of Computational Perception.
+He graduated in Computer Science from the Vienna University of Technology and earned his Ph.D.
+in Technical Sciences from the Johannes Kepler University Linz.
+Markus further studied International Business Administration at the Vienna University of Economics and Business Administration as well as at the Handelshogskolan of the University of Gothenburg, which led to a Master’s degree.
+Markus (co-)authored more than 120 refereed conference papers and journal articles (among others, published in ACM Multimedia, SIGIR, ECIR, IEEE Visualization; Journal of Machine Learning Research, ACM Transactions on Information Systems, Springer Information Retrieval, IEEE Multimedia).
+Furthermore, he is associate editor of the Springer International Journal of Multimedia Information Retrieval and serves on various program committees and reviewed submissions to several conferences and journals (among others, ACM Multimedia, ECIR, IJCAI, ICASSP, IEEE Visualization; IEEE Transactions of Multimedia, Elsevier Data \& Knowledge Engineering, ACM Transactions on Intelligent Systems and Technology, Springer Multimedia Systems).
+His main research interests include web and social media mining, information retrieval, multimedia, and music information research.
+Since 2007, Markus has been giving several lectures, among others, ”Music Information Retrieval”, ”Exploratory Data Analysis”, ”Multimedia Search and Retrieval”, ”Learning from User-generated Data”, ”Multimedia Data Mining”, and ”Intelligent Systems”.
+He further spent several guest lecturing stays at the Universitat Pompeu Fabra, Barcelona, Spain, the Utrecht University, the Netherlands, the Queen Mary, University of London, UK, and the Kungliga Tekniska Hgskolan, Stockholm, Sweden.
+
+\paragraph{Xavier Serra} is Associate Professor of the Department of Information and Communication Technologies and Director of the Music Technology Group at the Universitat Pompeu Fabra in Barcelona.
+After a multidisciplinary academic education he obtained a PhD in Computer Music from Stanford University in 1989 with a dissertation on the spectral processing of musical sounds that is considered a key reference in the field.
+His research interests cover the analysis, description and synthesis of sound and music signals, with a balance between basic and applied research and approaches from both scientific/technological and humanistic/artistic disciplines.
+Dr.
+Serra is very active in promoting initiatives in the field of Sound and Music Computing at the local and international levels, being involved in the editorial board of a number of journals and conferences and giving lectures on current and future challenges of the field.
+He has recently been awarded an Advanced Grant of the European Research Council to carry out the project CompMusic aimed at promoting multicultural approaches in music computing research.
+
+\paragraph{Xiao Hu} is an Assistant Professor in the Division of Information and Technology Studies in the Faculty of Ed- ucation of the University of Hong Kong.
+She received her Ph.D degree in Library and Information Science from the University of Illinois, with an award winning dissertation on multimodal music mood classification.
+Dr.
+Hu’s research interests include music mood recognition, MIR evaluation, user-centered MIR studies and cross-cultural MIR.
+Dr.
+Hu has won the Best Student Paper award in the ACM Joint Conference on Digital Libraries (2010) and Best Student Paper award in the iConference (2010).
+Dr.
+Hu has been a visiting scholar at the National Institute of Informatics, Japan.
+She was a tutorial speaker on music affect recognition (2012) and a Conference Co-chair (2014) in the International Society for Music Information Retrieval Conference.}
+%  Xavier Serra, Xiao Hu}{external/11-2_Tutorial-2.pdf}{}
 
 % Tutorial 3
-\includeabstract{Markov Logic Networks for Music Analysis}{Helene Papadopoulos}{external/11-3_Tutorial-3.pdf}
+\includeabstract{Why is studio production interesting?}{Emmanuel
+  Deruty, Fran\c{c}ois Pachet}{The tutorial follows the “Why X is interesting” series that aims at bridging the gap between technology-oriented and music-related research.
+It will suggest a number of reasons why production is important for MIR, seen from the eyes of an expert (the first author) and a MIR researcher (the second one).
+
+In music, the use of studio techniques has become commonplace with the advent of cheap personal computers and powerful DAWs.
+The MIR community has long been confronted to studio production.
+Since ISMIR’s first installment in 2000, about 35 papers involving more than 70 authors have addressed studio production.
+However, more than 44% of these identify studio production as a source of problems: the so-called album or producer effect gets in the way of artist or genre identification, audio processing techniques prevent proper onset detections, or effects are responsible for false positive in singing voice detection.
+A few of these papers even characterize production as not being part of the music.
+On the other hand, another 35% of these papers either outline the knowledge of studio production as useful or indispensable to MIR tasks, or try to provide a formal characterization for this set of techniques.
+
+A difficulty met by MIR researchers interested in studio production techniques is that production specialists are reluctant to formalize their knowledge.
+Like old-fashioned guild artisans, engineers and producers reputedly learn “tricks of the trade” from the “Greatest Teachers” or “mentors”.
+As a result, knowledge of studio production techniques is not widespread in the scientific community.
+Even in the upcoming field of automatic mixing, a domain intrinsically related to studio production, we have found that only 15% of scientific papers take these techniques into account.
+A similar issue can be observed at DAFx, where papers dealing with studio production as actually performed in the music community are rare.
+
+The tutorial aims at explaining studio production techniques to MIR researchers in a simple and practical way, in order to highlight the main production tricks and usages to a MIR audience.
+
+We will review standard aspects of studio music production, including recording, processing, mixing, and mastering.
+We will then focus on the basic methods of audio processing: EQs, compression, reverbs, and such.
+We will illustrate how these basic techniques can be combined creatively.
+
+Production techniques may be implemented in a variety of ways, depending on trends and available hardware.
+We’ll go through a brief retrospective of how these techniques have been used since the mid 60’s in different ways.
+As different variations of the same basic processes can influence, sometimes drastically, the finished product, we believe such knowledge may be useful in relation to classification and similarity.
+
+MIR researchers often conceptualize lead vocals as a solo line, possibly ornamented with backing vocals and audio effects.
+In practice, we’ll show that vocal track production in mainstream pop music results in complex architectures.
+We will analyze the vocals tracks in some mainstream hits.
+It will demonstrate that studio production is an integral part of the music, not an extraneous layer of effects.
+Consequences are obvious for the nature of the information MIR scholars look for, e.g.
+in information extraction, retrieval, similarity or recommendation.
+
+We will complete the tutorial with a short demo of automatic mixing techniques developed in our lab that use auto-adaptive audio effects.
+It will demonstrate that consideration of production is a definite advantage in music generation.}{\paragraph{Emmanuel Deruty} studied studio production for music at the Conservatoire de Paris (CNSMDP), where he graduated as Tonmeister in 2000.
+He has worked in many fields related to audio and music production in Europe and in the US: sound designer in a research context (IRCAM), sound designer in a commercial context (Soundwalk collective), film music producer and composer (Autour de Minuit \& Everybody on Deck, Paris), lecturer at Alchemea College of sound engineering (London), writer for the Sound on Sound magazine (Cambridge, UK).
+He’s worked as a M.I.R.
+researcher at IRCAM, INRIA and Akoustic-Arts, France.
+He’s currently working on automatic mixing at Sony CSL, and is a specialist of the “loudness war”.
+
+\paragraph{François Pachet} received his Ph.D.
+and Habilitation degrees from Paris 6 University (UPMC).
+He is a Civil Engineer and was Assistant Professor in Artificial Intelligence and Computer Science, at Paris 6 University, until 1997.
+He is now director of the Sony Computer Science Laboratory in Paris, where he conducts research in interactive music listening and performance and musical metadata and developed several innovative technologies and award winning systems.
+François Pachet has published intensively in artificial intelligence and computer music.
+He was co-chair of the IJCAI 2015 special track on Artificial Intelligence and the Arts, and has been elected ECCAI Fellow in 2014.
+His current goal, funded by an ERC Advanced Grant, is to build computational representations of style from text and music corpora,that can be exploited for personalized content generation.
+He is also an accomplished musician (guitar, composition) and has published two music albums (in jazz and pop) as composer and performer.}
+%  Deruty, Fran\c{c}ois Pachet}{external/11-3_Tutorial-3.pdf}{}
 
 % Tutorial 4
-\includeabstract{COmputation and FLAmenco: Why Flamenco is Interesting for
-MIR Research}{Emilia G{\'o}mez, Nadine Kroher, Jose Miguel D{\'i}az-B{\'a}{\~n}ez, Sergio Oramas, Joaqu{\'i}n Mora, Francisco G{\'o}mez-Mart{\'i}n}{external/11-4_Tutorial-4.pdf}
+\includeabstract{Introduction to EEG Decoding for Music Information Retrieval
+Research}{Sebastian Stober, Blair Kaneshiro}{Perceptual and cognitive approaches to MIR research have very recently expanded to the realm of neuroscience, with MIR groups beginning to conduct neuroscience research and vice versa.
+First publications have already reached ISMIR and for the very first time, there will be a dedicated satellite event on cognitively based music informatics research (CogMIR) at this year’s ISMIR conference.
+Within the context of this growing potential for cross-disciplinary collaborations, this tutorial will provide fundamental knowledge of neuroscientific approaches and findings with the goal of sparking the interest of MIR researchers and leading to future intersections between these two exciting fields.
+Specifically, our focus for this tutorial is on electroencephalography (EEG), a widely used and relatively inexpensive recording modality which offers high temporal resolution, portability, and mobility – characteristics that may prove especially attractive for applications in MIR.
+Attendees of this tutorial will gain a fundamental understanding of EEG responses, including how the data are recorded as well as standard procedures for preprocessing and cleaning the data.
+Keeping in mind the interests and objectives of the MIR community, we will highlight EEG analysis approaches, including single-trial analyses, that lend themselves to retrieval scenarios.
+Finally, we will review relevant open-source software, tools, and datasets for facilitating future research.
+The tutorial will be structured as a combination of informational slides and live-coding analysis demonstrations, with ample time for Q\&A with the audience.}{\paragraph{Sebastian Stober} is head of the recently established junior research group on “Machine Learning in Cognitive Science” within the inter-disciplinary setting of the Research Focus Cognitive Science at the University of Potsdam.
+Before, he was a post-doctoral fellow at the Brain and Mind Institute of the University of Western Ontario where he investigated ways to identify perceived and imagined music pieces from electroencephalography (EEG) recordings.
+He studied computer science with focus on intelligent systems and music information retrieval at the Otto-von-Guericke University Magdeburg where he received his diploma degree in 2005 and his Ph.D.
+in 2011 for his thesis on adaptive methods for user-centered organization of music collections.
+He has also been co-organizer for the International Workshops on Learning Semantics of Audio Signals (LSAS) and Adaptive Multimedia Retrieval (AMR).
+With his current research on music imagery information retrieval, he combines music information retrieval with cognitive neuroscience.
+
+\paragraph{Blair Kaneshiro} is a Ph.D.
+candidate (ABD) at the Center for Computer Research in Music and Acoustics at Stanford University.
+She earned her B.A.
+in Music, M.A.
+in Music, Science, and Technology, and M.S.
+in Electrical Engineering, all from Stanford.
+Her research explores musical engagement and expectation through brain responses, with an emphasis on multivariate and single-trial approaches to EEG analysis.
+Other research interests include the study of musical engagement using behavioral and large-scale social-media data, and promotion of reproducible and cross-disciplinary research through open-source tools and datasets.
+She is affiliated with CCRMA’s Music Engagement Research Initiative (MERI) led by professor Jonathan Berger; music tech company Shazam; and the Brain Research group (formerly Suppes Brain Lab) at Stanford’s Center for the Study of Language and Information.}
+%Research}{Sebastian Stober, Blair Kaneshiro}{external/11-4_Tutorial-4.pdf}{}
 
 % Tutorial 5
-\includeabstract{Using Correlation Analysis and Big Data to Identify and Predict Musical Behaviors}{Jeff C.\ Smith}{external/11-5_Tutorial-5.pdf}
+\includeabstract{Natural Language Processing for MIR}{Sergio Oramas,
+  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{An increasing amount of musical information is being published daily in media like Social Networks, Digital Libraries or Web Pages.
+All this data has the potential to impact in musicological studies, as well as tasks within MIR such as music recommendation.
+Making sense of it is a very challenging task, and so this tutorial aims to provide the audience with potential applications of Natural Language Processing (NLP) to MIR and Computational Musicology.
+
+In this tutorial, we will focus on linguistic, semantic and statistical­based approaches to extract and formalize knowledge about music from naturally occurring text.
+We propose to provide the audience with a preliminary introduction to NLP, covering its main tasks along with the state­of­the­art and most recent developments.
+In addition, we will showcase the main challenges that the music domain poses to the different NLP tasks, and the already developed methodologies for leveraging them in MIR and musicological applications.
+We will cover the following NLP tasks:
+
+\begin{itemize}
+\item Basic text preprocessing and normalization
+\item Linguistic enrichment in the form of part­of­speech tagging, as well as shallow and dependency parsing.
+\item Information Extraction, with special focus on Entity Linking and Relation Extraction.
+\item Text Mining
+\item Topic Modeling
+\item Sentiment Analysis
+\item Word Vector Embeddings
+\end{itemize}
+
+We will also introduce some of the most popular python libraries for NLP (e.g.
+Gensim, Spacy) and useful lexical resources (e.g.
+WordNet, BabelNet).
+At the same time, the tutorial analyzes the challenges and opportunities that the application of these techniques to large amounts of texts presents to MIR researchers and musicologists, presents some research contributions and provides a forum to discuss about how address those challenges in future research.
+We envisage this tutorial as a highly interactive session, with a sizable amount of hands­-on activities and live demos of actual systems.}{\paragraph{Sergio Oramas} received a degree in Computer Engineering by the Technical University of Madrid in 2004, and a B.A.
+in Musicology by the University of La Rioja in 2011.
+He is a PhD candidate at the Music Technology Group (Pompeu Fabra University) since 2013, holding a “La Caixa” PhD Fellowship.
+His research interests are focused on the extraction of structured knowledge from text and its application in Music Information Retrieval and Computational Musicology.
+
+\paragraph{Luis Espinosa-Anke} is a PhD candidate at the Natural Language Processing group in at Pompeu Fabra University.
+His research focuses in learning knowledge representations of language, including automatic construction of glossaries; knowledge base generation, population and unification; and automatic taxonomy learning.
+He is Fulbright alumni, “laCaixa” scholar, and member of the Erasmus Mundus Association as well as the European Network of eLexicography.
+
+\paragraph{Shuo Zhang} is a PhD candidate in Computational Linguistics at Georgetown University, USA, and a collaborator/researcher at the Music Technology Group, Universitat Pompeu Fabra.
+He has worked in both text (NLP­information extraction) and sound (speech processing­time­series data mining in speech prosody) aspects of computational linguistics and their applications in MIR.
+His past and current projects include areas such as coreference resolution, search and visualization of multilayered linguistic corpora, text mining \& topic modeling in MIR, temporal semantics, time­series mining in speech and music, etc.
+Shuo holds B.Sci.
+from the Peking University, M.A.
+from the Department of Music, University of Pittsburgh, and M.Sci.
+in Computational Linguistics from Georgetown University.
+
+\paragraph{Horacio Saggion} is Profesor Agregado at the Department of Technologies, Universitat Pompeu Fabra.
+He holds a PhD in Computer Science from Université de Montréal (Canada).
+He is associated to the Natural Language Processing group where he works on automatic text summarization, text simplification, information extraction, text processing in social media, sentiment analysis and related topics.
+His research is empirical combining symbolic, pattern­based approaches and statistical and machine learning techniques.
+Before joining Universitat Pompeu Fabra, he worked at the University of Sheffield for a number of UK and European research projects developing competitive human language technology.
+He was also an invited researcher at Johns Hopkins University in 2011.
+Horacio has published over 100 works in leading scientific journals, conferences, and books in the field of human language technology.}
+%  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{external/11-5_Tutorial-5.pdf}{}
 
 % Tutorial 6
-\includeabstract{Automatic Music Transcription}{Zhiyao Duan, Emmanouil Benetos}{external/11-6_Tutorial-6.pdf}
+\includeabstract{Why Hip-Hop is interesting}{Jan Van Balen, Ethan
+  Hein, Dan Brown}{Hip-hop, as a musical culture, is extremely popular around the world.
+Its influence on popular music is unprecedented: the hip-hop creative process has become the dominant practice of the pop mainstream, and spawned a range of electronic styles.
+Strangely, Hip-hop hasn’t been the subject of much research in Music Information Retrieval.
+Music research rooted in the European music traditions tends to look at music in terms harmony, melody and form.
+Even compared to other popular music, these are facets of music that don’t quite work the same way in Hip-Hop as they do in the music of Beethoven and the Beatles.
+
+In this tutorial, we will argue that a different perspective may be needed to approach the analysis of Hip-hop and popular music computationally—an analysis with a stronger focus on timbre, rhythm and lyrics and attention to groove, texture, rhyme, metadata and semiotics.
+
+Hip-hop is often said to integrate four modes of artistic expression: Rap, turntablism, breakdance and graffiti culture.
+In the first part of this tutorial, we will discuss the emergence and evolution of Hip-Hop as a musical genre, and its particularities, focusing our discussion on beat-making (turntablism and sampling), and Rap.
+A second part of the talk will highlight the most important reasons why MIR practitioners and other music technologists should care about Hip-Hop, talking about Hip-hop’s relevance today, and the role Hip-hop in popular music.
+We highlight its relative absence in music theory, music education, and MIR.
+The latter will be illustrated with examples of MIR and digital musicology studies in which Hip-hop music is explicitly ignored or found to ‘break’ the methodology.
+
+Next, we review some of the work done on the intersection of Hip-hop and music technology.
+Because the amount of computational research on Hip-hop music is rather modest, we discuss, in depth, three clusters of research on the intersection of Hip-hop and music technology.
+The first two are related of MIR, focusing on ‘beats’ and sampling, and Rap lyrics and rhyme.
+For the third topic, situating Hip-hop in the broader topic of music technology, we look at how an important role for both music technology and Hip-hop is emerging in music education.
+Finally, the last part of the talk will give an overview of resources and research opportunities for Hip-hop research.
+
+This tutorial is aimed at anyone interested in Music Information Retrieval and popular music, whether familiar with Hip-hop music or not.
+We also aim to make it relevant to a broader audience interested in music technology, touching on topics like sampling and samplers, and Hip-hop in technology and music education, and to anyone interested in text processing, with an additional focus on the analysis of lyrics.
+
+Throughout the tutorial, we intend to include a lot of listening examples.
+Participants will access to an extended playlist of selected listening examples, along with a short guide to the significance of the selected recordings.}{\paragraph{Jan Van Balen} researches the use of audio MIR methods to learn new things about music and music memory.
+Living in London, he is finishing his PhD with Utrecht University (NL), on audio corpus analysis and popular music.
+As part of his PhD project and with colleagues at Utrecht University and University of Amsterdam, he worked on Hooked, a game to collect data on popular music memory and ‘hooks’.
+Other work has focused on the analysis of the game’s audio and participant data, and on content ID techniques for the analysis of samples, cover songs and folk tunes.
+
+\paragraph{Ethan Hein} is a doctoral student in music education at New York University.
+He teaches music technology, production and education at NYU and Montclair State University.
+As the Experience Designer In Residence with the NYU Music Experience Design Lab, Ethan has taken a leadership role in a range of technologies for learning and expression.
+In collaboration with Soundfly, he recently launched an online course called Theory For Producers.
+He maintains a widely-followed and influential blog at http://www.ethanhein.com, and has written for various publications, including Slate, Quartz, and NewMusicBox.
+
+\paragraph{Dan Brown} is Associate Professor of Computer Science at the University of Waterloo, where he has been a faculty member since 2000.
+Dan earned his Bachelor’s degree in Math with Computer Science from MIT, and his PhD in Computer Science from Cornell.
+Before coming to Waterloo, he spent a year working on the Human and Mouse Genome Projects as a post-doc at the MIT Center for Genome Research.
+Dan’s primary research interests are designing algorithms for understanding biological evolution, and applying bioinformatics ideas to problems in music information retrieval.}
+%  Hein, Dan Brown}{external/11-6_Tutorial-6.pdf}{}

### 2016-07-11 2016_Proceedings_ISMIR/papers.tex
derived files now compile without any issues, escape latex special characters in python and convert and to comma

@@
 \thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 1}
+\addcontentsline{toc}{section}{Oral session 1: Mixed}
 \includepdf[pages=2,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
@@
 
+\includepaper{SiMPle: Assessing Music Similarity Using Subsequences Joins}{Diego Silva, Chin-Chia Michael Yeh, Gustavo Batista, Eamonn Keogh}{articles/099_Paper}
+\includepaper{Score-Informed Identification of Missing and Extra Notes in Piano Recordings}{Sebastian Ewert, Siying Wang, Meinard Mueller, Mark Sandler}{articles/123_Paper}
+\includepaper{Feature Learning for Chord Recognition: The Deep Chroma Extractor}{Filip Korzeniowski, Gerhard Widmer}{articles/178_Paper}
 \includepaper{Learning to Pinpoint Singing Voice from Weakly Labeled Examples}{Jan Schlüter}{articles/315_Paper}
-\includepaper{SiMPle: Assessing Music Similarity Using Subsequences Joins}{Diego Silva, Chin-Chia Michael Yeh, Gustavo Batista and Eamonn Keogh}{articles/099_Paper}
-\includepaper{Feature Learning for Chord Recognition: The Deep Chroma Extractor}{Filip Korzeniowski and Gerhard Widmer}{articles/178_Paper}
-\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Praetzlich and Meinard Mueller}{articles/022_Paper}
 
 \thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 2}
+\addcontentsline{toc}{section}{Oral session 2: Rhythm}
 \includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
@@
 
-\includepaper{AUTOMATIC TAGGING USING DEEP CONVOLUTIONAL NEURAL NETWORKS}{Keunwoo Choi, George Fazekas and Mark Sandler}{articles/009_Paper}
-\includepaper{Analyzing Measure Annotations for Western Classical Music Recordings}{Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz and Meinard Müller}{articles/079_Paper}
-\includepaper{Score-Informed Identification of Missing and Extra Notes in Piano Recordings}{Sebastian Ewert, Siying Wang, Meinard Mueller and Mark Sandler}{articles/123_Paper}
-\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs and Gerhard Widmer}{articles/186_Paper}
+\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs, Gerhard Widmer}{articles/186_Paper}
+\includepaper{Bayesian meter tracking on learned signal representations}{Andre Holzapfel, Thomas Grill}{articles/132_Paper}
+\includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font, Xavier Serra}{articles/195_Paper}
+\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Praetzlich, Meinard Mueller}{articles/022_Paper}
 
 \thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 3}
+\addcontentsline{toc}{section}{Oral session 3: Users}
 \includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
@@
 
-\includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font and Xavier Serra}{articles/195_Paper}
-\includepaper{Using Priors To Improve Estimates of Music Structure}{Jordan Smith and Masataka Goto}{articles/135_Paper}
-\includepaper{A Neural Greedy Model for Voice Separation in Symbolic Music}{Patrick Gray and Razvan Bunescu}{articles/296_Paper}
+\includepaper{A Plan For Sustainable Mir Evaluation}{Brian McFee, Eric Humphrey, Julián Urbano}{articles/257_Paper}
+\includepaper{Go With The Flow: When Listeners Use Music As Technology}{Andrew Demetriou, Martha Larson, Cynthia C. S. Liem}{articles/068_Paper}
+\includepaper{A Look At The Cloud From Both Sides Now: An Analysis Of Cloud Music Service Usage}{Jin Ha Lee, Yea-Seul Kim, Chris Hubbles}{articles/087_Paper}
 
 \thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 4}
+\addcontentsline{toc}{section}{Oral session 4: Musicologies}
 \includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
@@
 
-\includepaper{Towards Reading Sheet Music}{Matthias Dorfer, Andreas Arzt and Gerhard Widmer}{articles/027_Paper}
-\includepaper{A plan for sustainable MIR evaluation}{Brian McFee, Eric Humphrey and Julián Urbano}{articles/257_Paper}
-\includepaper{Go With the Flow: When Listeners Use Music as Technology}{Andrew Demetriou, Martha Larson and Cynthia C. S. Liem}{articles/068_Paper}
+\includepaper{Analyzing Measure Annotations For Western Classical Music Recordings}{Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz, Meinard Müller}{articles/079_Paper}
+\includepaper{Instrumental Idiom In The 16Th Century: Patterns In Arrangements Of Vocal Music}{David Lewis, Tim Crawford, Daniel Müllensiefen}{articles/165_Paper}
+\includepaper{The Sousta Corpus: Beat-Informed Automatic Transcription Of Traditional Dance Tunes}{Andre Holzapfel, Emmanouil Benetos}{articles/156_Paper}
+\includepaper{Learning A Feature Space For World Music Style Similarity}{Maria Panteli, Emmanouil Benetos, Simon Dixon}{articles/166_Paper}
 
 \thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 5}
+\addcontentsline{toc}{section}{Oral session 5: Structure}
 \includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
@@
 
-\includepaper{Automatic Melodic Reduction using a Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
-\includepaper{Singing Melody Extraction using Multi-Column Deep Neural Networks}{Sangeun Kum, Changheun Oh and Juhan Nam}{articles/119_Paper}
-\includepaper{Instrumental idiom in the 16th century: patterns in arrangements of vocal music}{David Lewis, Tim Crawford and Daniel Müllensiefen}{articles/165_Paper}
+\includepaper{Systematic Exploration Of Computational Music Structure Research}{Oriol Nieto, Juan Pablo Bello}{articles/043_Paper}
+\includepaper{Using Priors To Improve Estimates Of Music Structure}{Jordan Smith, Masataka Goto}{articles/135_Paper}
 
 \thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 6}
+\addcontentsline{toc}{section}{Oral session 6: Symbolic}
 \includepdf[pages=9,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
@@
 
-\includepaper{Learning a feature space for world music style similarity}{Maria Panteli, Emmanouil Benetos and Simon Dixon}{articles/166_Paper}
-\includepaper{Bayesian meter tracking on learned signal representations}{Andre Holzapfel and Thomas Grill}{articles/132_Paper}
-\includepaper{The Sousta corpus: Beat-informed automatic transcription of traditional dance tunes}{Andre Holzapfel and Emmanouil Benetos}{articles/156_Paper}
+\includepaper{Music Structural Segmentation Across Genres With Gammatone Features}{Mi Tian, Mark B. Sandler}{articles/032_Paper}
+\includepaper{Automatic Melodic Reduction Using A Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
+\includepaper{A Neural Greedy Model For Voice Separation In Symbolic Music}{Patrick Gray, Razvan Bunescu}{articles/296_Paper}
 
 \thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 7}
+\addcontentsline{toc}{section}{Oral session 7: Deep-learning}
 \includepdf[pages=10,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
@@
 
-\includepaper{A LOOK AT THE CLOUD FROM BOTH SIDES NOW: AN ANALYSIS OF CLOUD MUSIC SERVICE USAGE}{Jin Ha Lee, Yea-Seul Kim and Chris Hubbles}{articles/087_Paper}
-\includepaper{A Hybrid Gaussian-HMM-Deep Learning Approach For Automatic Chord Estimation With Very Large Vocabulary}{Junqi Deng and Yu-Kwong Kwok}{articles/058_Paper}
-\includepaper{SYSTEMATIC EXPLORATION OF COMPUTATIONAL MUSIC STRUCTURE RESEARCH}{Oriol Nieto and Juan Pablo Bello}{articles/043_Paper}
-\includepaper{Extracting Ground-Truth Information from MIDI Files: A MIDIfesto}{Colin Raffel and Daniel Ellis}{articles/105_Paper}
+\includepaper{Towards Reading Sheet Music}{Matthias Dorfer, Andreas Arzt, Gerhard Widmer}{articles/027_Paper}
+\includepaper{Extracting Ground-Truth Information From Midi Files: A Midifesto}{Colin Raffel, Daniel Ellis}{articles/105_Paper}
+\includepaper{Automatic Tagging Using Deep Convolutional Neural Networks}{Keunwoo Choi, George Fazekas, Mark Sandler}{articles/009_Paper}
+\includepaper{A Hybrid Gaussian-Hmm-Deep Learning Approach For Automatic Chord Estimation With Very Large Vocabulary}{Junqi Deng, Yu-Kwong Kwok}{articles/058_Paper}
+\includepaper{Singing Melody Extraction Using Multi-Column Deep Neural Networks}{Sangeun Kum, Changheun Oh, Juhan Nam}{articles/119_Paper}
 
@@
 
-\includepaper{TIME-DELAYED MELODY SURFACES FOR RAGA RECOGNITION}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan entürk and Xavier Serra}{articles/030_Paper}
-\includepaper{ON PRACTICAL STRATEGIES OF MELODY INDEXING FOR QUERY BY HUMMING}{Bartlomiej Stasiak}{articles/089_Paper}
-\includepaper{Recurrent Neural Networks for Drum Transcription}{Richard Vogl, Matthias Dorfer and Peter Knees}{articles/269_Paper}
-\includepaper{Integer Programming Formulation of the Problem of Generating Milton Babbitt's All-partition Arrays}{Tsubasa Tanaka, Brian Bemman and David Meredith}{articles/034_Paper}
-\includepaper{Mining Musical Traits of Social Functions in Native American Music}{Daniel Shanahan, Kerstin Neubarth and Darrell Conklin}{articles/167_Paper}
-\includepaper{Exploring The Latent Structure of Collaborations in Music Production}{Nazareno Andrade and Flavio Figueiredo}{articles/251_Paper}
-\includepaper{Musical Note Estimation for F0 Trajectories of Singing Voices based on a Bayesian Semi-beat-synchronous HMM}{Ryo Nishikimi, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii}{articles/004_Paper}
-\includepaper{NOISE ROBUST MUSIC ARTIST RECOGNITION USING I-VECTOR FEATURES}{Hamid Eghbal-zadeh and Gerhard Widmer}{articles/037_Paper}
-\includepaper{Piano Transcription using an Exponential Decay Model}{Tian Cheng, Matthias Mauch, Emmanouil Benetos and Simon Dixon}{articles/085_Paper}
-\includepaper{Live Song ID: A Hashprint Approach}{TJ Tsai, Thomas Praetzlich and Meinard Mueller}{articles/098_Paper}
-\includepaper{Nonnegative tensor factorization with frequency modulation cues for blind audio source separation}{Elliot Creager, Noah Stein and Roland Badeau}{articles/103_Paper}
-\includepaper{On the evaluation of rhythmic and melodic descriptors}{Maria Panteli and Simon Dixon}{articles/161_Paper}
-\includepaper{Analysis and classification of phonation modes in singing}{Daniel Stoller and Simon Dixon}{articles/233_Paper}
-\includepaper{Beat Tracking with a Cepstroid Invariant Neural Network}{Anders Elowsson}{articles/252_Paper}
-\includepaper{On drum playing technique detection in polyphonic mixtures}{Chih-Wei Wu and Alexander Lerch}{articles/268_Paper}
-\includepaper{MusicDB: A Platform for Longitudinal Music Analytics}{Jeremy Hyrkas and Bill Howe}{articles/284_Paper}
-\includepaper{Further Steps towards a Standard Testbed for Optical Music Recognition}{Jan Haji, jr., Jií Novotn, Pavel Pecina and Jaroslav Pokorn}{articles/289_Paper}
-\includepaper{Two (note) heads are better than one: pen-based multimodal interaction with music notation}{Jorge Calvo-Zaragoza, David Rizo and Jose M. Iñesta}{articles/006_Paper}
-\includepaper{Music Structural Segmentation Across Genres with Gammatone Features}{Mi Tian and Mark B. Sandler}{articles/032_Paper}
-\includepaper{Enhancing cover song identification with hierarchical rank aggregation}{Julien Osmalskyj, Marc Van Droogenbroeck and Jean-Jacques Embrechts}{articles/064_Paper}
-\includepaper{GENRE ONTOLOGY LEARNING: COMPARING CURATED WITH CROWD-SOURCED ONTOLOGIES}{Hendrik Schreiber}{articles/074_Paper}
-\includepaper{Improving voice separation by better connecting contigs}{Nicolas Guiomard-Kagan, Mathieu Giraud, Richard Groult and Florence Levé}{articles/129_Paper}
-\includepaper{Querying XML Score Databases: XQuery is not Enough!}{Raphael Fournier-S'niehotta, Philippe Rigaux and Nicolas Travers}{articles/136_Paper}
-\includepaper{Analysing Scattering-Based Music Content Analysis Systems: Where's the Music?}{Francisco Rodríguez-Algarra, Bob L. Sturm and Hugo Maruri-Aguilar}{articles/146_Paper}
-\includepaper{ELUCIDATING USER BEHAVIOR IN MUSIC SERVICES THROUGH PERSONA AND GENDER}{John Fuller, Lauren Hubener, Yea-Seul Kim and Jin Ha Lee}{articles/205_Paper}
-\includepaper{Improving Predictions of Derived Viewpoints in Multiple Viewpoints Systems}{Thomas Hedges and Geraint Wiggins}{articles/208_Paper}
-\includepaper{Phrase-level Audio Segmentation of Jazz Improvisations Informed by Symbolic Data}{Jeff Gregorio and Youngmoo Kim}{articles/245_Paper}
-\includepaper{Conversations with Expert Users in Music Retrieval and Research Challenges for Creative MIR}{Kristina Andersen and Peter Knees}{articles/246_Paper}
-\includepaper{A comparison of melody extraction methods based on source-filter modelling}{Juan J. Bosch, Rachel M. Bittner, Justin Salamon and Emilia Gómez}{articles/256_Paper}
-\includepaper{Large-Scale Organization of Hierarchical Music Analyses}{Phillip Kirlin}{articles/259_Paper}
+\includepaper{An Ontology For Audio Features}{Alo Allik, György Fazekas, Mark Sandler}{articles/077_Paper}
+\includepaper{Adaptive Frequency Neural Networks For Dynamic Pulse And Metre Perception}{Andrew Lambert, Tillman Weyde, Newton Armstrong}{articles/228_Paper}
+\includepaper{Listen To Me – Don'T Listen To Me: What Communities Of Critics Tell Us About Music}{Ben Fields, Christophe Rhodes}{articles/173_Paper}
+\includepaper{An Evaluation Framework And Case Study For Rhythmic Concatenative Synthesis}{Cárthach Ó Nuanáin, Perfecto Herrera, Sergi Jordà}{articles/180_Paper}
+\includepaper{On Drum Playing Technique Detection In Polyphonic Mixtures}{Chih-Wei Wu, Alexander Lerch}{articles/268_Paper}
+\includepaper{Analysis And Classification Of Phonation Modes In Singing}{Daniel Stoller, Simon Dixon}{articles/233_Paper}
+\includepaper{Nonnegative Tensor Factorization With Frequency Modulation Cues For Blind Audio Source Separation}{Elliot Creager, Noah Stein, Roland Badeau}{articles/103_Paper}
+\includepaper{Downbeat Tracking Using Beat Synchronous Features With Recurrent Neural Networks}{Florian Krebs, Sebastian Böck, Matthias Dorfer, Gerhard Widmer}{articles/249_Paper}
+\includepaper{Automatic Music Recommendation Systems: Do Demographic, Profiling, And Contextual Features Improve Their Performance?}{Gabriel Vigliensoni, Ichiro Fujinaga}{articles/044_Paper}
+\includepaper{Composer Recognition Based On 2D-Filtered Piano-Rolls}{Gissel Velarde, Carlos Cancino Chacón, David Meredith, Weyde Tillman, Maaten Grachten}{articles/063_Paper}
+\includepaper{Integration And Quality Assessment Of Heterogeneous Chord Sequences Using Data Fusion}{Hendrik Vincent Koops, W. Bas de Haas, Dimitrios Bountouridis, Anja Volk}{articles/019_Paper}
+\includepaper{Predicting Missing Music Components With Bidirectional Long Short-Term Memory Neural Networks}{I-Ting Liu, Richard Randall}{articles/097_Paper}
+\includepaper{Further Steps Towards A Standard Testbed For Optical Music Recognition}{Jan Hajič, jr., Jiří Novotný, Pavel Pecina, Jaroslav Pokorný}{articles/289_Paper}
+\includepaper{Analysis Of Vocal Imitations Of Pitch Trajectories}{Jiajie Dai, Simon Dixon}{articles/127_Paper}
+\includepaper{Towards Template-Based Vibrato Analysis In Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}
+\includepaper{Enhancing Cover Song Identification With Hierarchical Rank Aggregation}{Julien Osmalskyj, Marc Van Droogenbroeck, Jean-Jacques Embrechts}{articles/064_Paper}
+\includepaper{Conversations With Expert Users In Music Retrieval And Research Challenges For Creative Mir}{Kristina Andersen, Peter Knees}{articles/246_Paper}
+\includepaper{Ava: An Interactive System For Visual And Quantitative Analyses Of Vibrato And Portamento Performance Styles}{Luwei Yang, Elaine Chew, Khalid Z. Rajab}{articles/314_Paper}
+\includepaper{Improving Voice Separation By Better Connecting Contigs}{Nicolas Guiomard-Kagan, Mathieu Giraud, Richard Groult, Florence Levé}{articles/129_Paper}
+\includepaper{A Corpus Of Annotated Irish Traditional Dance Music Recordings: Design And Benchmark Evaluations}{Pierre Beauguitte, Bryan Duggan, John Kelleher}{articles/148_Paper}
+\includepaper{Learning And Visualizing Music Specifications Using Pattern Graphs}{Rafael Valle, Alexandre Donzé, Daniel J. Fremont, Ilge Akkaya, Sanjit A. Seshia, Adrian Freed}{articles/280_Paper}
+\includepaper{Landmark-Based Audio Fingerprinting For Dj Mix Monitoring}{Reinhard Sonnleitner, Andreas Arzt, Gerhard Widmer}{articles/187_Paper}
+\includepaper{Long-Term Reverberation Modeling In Under-Determined Audio Source Separation}{Romain Hennequin, François Rigaud}{articles/196_Paper}
+\includepaper{Exploring Customer Reviews For Music Genre Classification And Evolutionary Studies}{Sergio Oramas, Luis Espinosa-Anke, Aonghus Lawlor, Horacio Saggion, Xavier Serra}{articles/240_Paper}
+\includepaper{Towards Evaluating Multiple Predominant Melody Annotations In Jazz Recordings}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar, Meinard Mueller}{articles/049_Paper}
+\includepaper{Ensemble: A Hybrid Human-Machine System For Generating Melody Scores From Audio}{Tim Tse, Justin Salamon, Alex Williams, Helga Jiang, Edith Law}{articles/072_Paper}
+\includepaper{Integer Programming Formulation Of The Problem Of Generating Milton Babbitt'S All-Partition Arrays}{Tsubasa Tanaka, Brian Bemman, David Meredith}{articles/034_Paper}
+\includepaper{Structural Segmentation And Visualization Of Sitar And Sarod Concert Audio}{Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}
+\includepaper{Automatic Outlier Detection In Music Datasets}{Yen-Cheng Lu, Chih-Wei Wu, Alexander Lerch, Chang-Tien Lu}{articles/215_Paper}
 
@@
 
-\includepaper{Towards Template-Based Vibrato Analysis in Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert and Meinard Mueller}{articles/005_Paper}
-\includepaper{Automatic music recommendation systems: do demographic, profiling, and contextual features improve their performance?}{Gabriel Vigliensoni and Ichiro Fujinaga}{articles/044_Paper}
-\includepaper{Ensemble: A Hybrid Human-Machine System for Generating Melody Scores from Audio}{Tim Tse, Justin Salamon, Alex Williams, Helga Jiang and Edith Law}{articles/072_Paper}
-\includepaper{An ontology for audio features}{Alo Allik, György Fazekas and Mark Sandler}{articles/077_Paper}
-\includepaper{Predicting Missing Music Components with Bidirectional Long Short-Term Memory Neural Networks}{I-Ting Liu and Richard Randall}{articles/097_Paper}
-\includepaper{Analysis of Vocal Imitations of Pitch Trajectories}{Jiajie Dai and Simon Dixon}{articles/127_Paper}
-\includepaper{Whither the Design of Experiments in MIR?}{Bob L. Sturm}{articles/128_Paper}
-\includepaper{Singing Voice Melody Transcription using Deep Neural Networks}{François Rigaud and Mathieu Radenen}{articles/163_Paper}
-\includepaper{Musical Typicality: How Many Similar Songs Exist?}{Tomoyasu Nakano, Daichi Mochihashi, Kazuyoshi Yoshii and Masataka Goto}{articles/191_Paper}
-\includepaper{Automatic Drum Transcription using Bi-directional Recurrent Neural Networks}{Carl Southall, Ryan Stables and Jason Hockman}{articles/217_Paper}
-\includepaper{On the use of note onsets for improved lyrics-to-audio alignment}{Georgi Dzhambazov, Ajay Srinivasamurthy, Sertan Sentürk and Xavier Serra}{articles/243_Paper}
-\includepaper{A higher-dimensional expansion of affective norms for English terms for music tagging}{Michele Buccoli, Massimiliano Zanoni, György Fazekas, Augusto Sarti, Mark Sandler and Stefano Tubaro}{articles/253_Paper}
-\includepaper{Impact of Music on Decision Making in Quantitative Tasks}{Elad Liebman, Peter Stone and Corey White}{articles/272_Paper}
-\includepaper{WiMIR: An Informetric Study on Women Authors in ISMIR}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham and J. Stephen Downie}{articles/283_Paper}
-\includepaper{Aligned Hierarchies: A Multi-Scale Structure-Based Representation for Music-Based Data Streams}{Katherine M. Kinnaird}{articles/020_Paper}
-\includepaper{Genre specific dictionaries for harmonic/percussive source separation}{Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski and Gaël Richard}{articles/042_Paper}
-\includepaper{SPARSE CODING BASED MUSIC GENRE CLASSIFICATION USING SPECTRO-TEMPORAL MODULATIONS}{Chih-Shan Lin, Kai-Chun Hsu and Tai-Shih Chi}{articles/046_Paper}
-\includepaper{TOWARDS EVALUATING MULTIPLE PREDOMINANT MELODY ANNOTATIONS IN JAZZ RECORDINGS}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar and Meinard Mueller}{articles/049_Paper}
-\includepaper{Simultaneous Separation and Segmentation in Layered Music}{Prem Seetharaman and Bryan Pardo}{articles/057_Paper}
-\includepaper{Composer Recognition based on 2D-Filtered Piano-Rolls}{Gissel Velarde, Carlos Cancino Chacón, David Meredith, Weyde Tillman and Maaten Grachten}{articles/063_Paper}
-\includepaper{Bootstrapping a system for phoneme recognition and keyword spotting in unaccompanied singing}{Anna Kruspe}{articles/070_Paper}
-\includepaper{A Methodology for Quality Assessment in Collaborative Score Libraries}{Vincent Besson, Marco Gurrieri, Philippe Rigaux, Alice Tacaille and Virginie Thion}{articles/076_Paper}
-\includepaper{Transcribing Human Piano Performances Into Music Notation}{Andrea Cogliati, David Temperley and Zhiyao Duan}{articles/088_Paper}
-\includepaper{Learning Invariants for Instrument Recognition}{Vincent Lostanlen and Carmine Emanuele Cella}{articles/093_Paper}
-\includepaper{Exploiting frequency, periodicity and harmonicity using advanced time-frequency concentration techniques for multipitch estimation of choir and symphony}{Li Su, Tsung-Ying Chuang and Yi-Hsuan Yang}{articles/104_Paper}
-\includepaper{A LATENT SPACE APPROACH TO LISTENING BEHAVIOR ANALYSIS}{Chia-Hao Chung, Jing-Kai Lou and Homer Chen}{articles/110_Paper}
-\includepaper{Data-driven exploration of melodic structure in Hindustani music}{Kaustuv Kanti Ganguli, Sankalp Gulati, Xavier Serra and Preeti Rao}{articles/121_Paper}
-\includepaper{learning temporal feature using deep neural network and its application to music genre classification}{Il-Young Jeong and Kyogu Lee}{articles/159_Paper}
-\includepaper{Listen to Me – Don't Listen to Me: What Communities of Critics Tell Us About Music}{Ben Fields and Christophe Rhodes}{articles/173_Paper}
-\includepaper{On the Potential of Simple Framewise Approaches to Piano Transcription}{Rainer Kelz, Matthias Dorfer, Filip Korzeniowski, Sebastian Böck, Andreas Arzt and Gerhard Widmer}{articles/179_Paper}
-\includepaper{A Dataset for Automatic Practice Logging}{R. Michael Winters, Siddharth Gururani and Alexander Lerch}{articles/181_Paper}
-\includepaper{Long-term reverberation modeling in under-determined audio source separation}{Romain Hennequin and François Rigaud}{articles/196_Paper}
-\includepaper{Downbeat Detection with Conditional Random Fields and Deep Learned Features}{Simon Durand and Slim Essid}{articles/213_Paper}
-\includepaper{Automatic Outlier Detection in Music Datasets}{Yen-Cheng Lu, Chih-Wei Wu, Alexander Lerch and Chang-Tien Lu}{articles/215_Paper}
+\includepaper{A Hierarchical Bayesian Model Of Chords, Pitches, And Spectrograms For Multipitch Analysis}{Yuta Ojima, Eita Nakamura, Katsutoshi Itoyama, Kazuyoshi Yoshii}{articles/003_Paper}
+\includepaper{A Higher-Dimensional Expansion Of Affective Norms For English Terms For Music Tagging}{Michele Buccoli, Massimiliano Zanoni, György Fazekas, Augusto Sarti, Mark Sandler, Stefano Tubaro}{articles/253_Paper}
+\includepaper{A Latent Space Approach To Listening Behavior Analysis}{Chia-Hao Chung, Jing-Kai Lou, Homer Chen}{articles/110_Paper}
+\includepaper{A Methodology For Quality Assessment In Collaborative Score Libraries}{Vincent Besson, Marco Gurrieri, Philippe Rigaux, Alice Tacaille, Virginie Thion}{articles/076_Paper}
+\includepaper{Aligned Hierarchies: A Multi-Scale Structure-Based Representation For Music-Based Data Streams}{Katherine M. Kinnaird}{articles/020_Paper}
+\includepaper{Analysing Scattering-Based Music Content Analysis Systems: Where'S The Music?}{Francisco Rodríguez-Algarra, Bob L. Sturm, Hugo Maruri-Aguilar}{articles/146_Paper}
+\includepaper{Beat Tracking With A Cepstroid Invariant Neural Network}{Anders Elowsson}{articles/252_Paper}
+\includepaper{Bootstrapping A System For Phoneme Recognition And Keyword Spotting In Unaccompanied Singing}{Anna Kruspe}{articles/070_Paper}
+\includepaper{Can Microblogs Predict Music Charts?
+An Analysis Of The Relationship Between \#Nowplaying Tweets And Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf, Günther Specht}{articles/039_Paper}
+\includepaper{Cross Task Study On Mirex Recent Results: An Index For Evolution Measurement And Some Stagnation Hypotheses}{Ricardo Scholz, Geber Ramalho, Giordano Cabral}{articles/054_Paper}
+\includepaper{Cross-Collection Evaluation For Music Classification Tasks}{Dmitry Bogdanov, Alastair Porter, Perfecto Herrera, Xavier Serra}{articles/220_Paper}
+\includepaper{Downbeat Detection With Conditional Random Fields And Deep Learned Features}{Simon Durand, Slim Essid}{articles/213_Paper}
+\includepaper{Exploiting Frequency, Periodicity And Harmonicity Using Advanced Time-Frequency Concentration Techniques For Multipitch Estimation Of Choir And Symphony}{Li Su, Tsung-Ying Chuang, Yi-Hsuan Yang}{articles/104_Paper}
+\includepaper{Genre Ontology Learning: Comparing Curated With Crowd-Sourced Ontologies}{Hendrik Schreiber}{articles/074_Paper}
+\includepaper{Genre Specific Dictionaries For Harmonic/Percussive Source Separation}{Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski, Gaël Richard}{articles/042_Paper}
+\includepaper{Good-Sounds.Org: A Framework To Explore Goodness In Instrumental Sounds}{Giuseppe Bandiera, Oriol Romani Picas, Xavier Serra}{articles/199_Paper}
+\includepaper{Improving Predictions Of Derived Viewpoints In Multiple Viewpoints Systems}{Thomas Hedges, Geraint Wiggins}{articles/208_Paper}
+\includepaper{Learning Temporal Feature Using Deep Neural Network And Its Application To Music Genre Classification}{Il-Young Jeong, Kyogu Lee}{articles/159_Paper}
+\includepaper{Live Song Id: A Hashprint Approach}{TJ Tsai, Thomas Praetzlich, Meinard Mueller}{articles/098_Paper}
+\includepaper{Minimax Viterbi Algorithm For Hmm-Based Guitar Fingering Decision}{Gen Hori, Shigeki Sagayama}{articles/285_Paper}
+\includepaper{Mixtape: Direction-Based Navigation In Large Music Collections}{Joao Paulo V.
+Cardoso, Luciana Fujii Pontello, Pedro H.
+F.
+Holanda, Bruno Guilherme, Olga Goussevskaia, Ana Paula Couto da SIlva}{articles/155_Paper}
+\includepaper{Musical Note Estimation For F0 Trajectories Of Singing Voices Based On A Bayesian Semi-Beat-Synchronous Hmm}{Ryo Nishikimi, Eita Nakamura, Katsutoshi Itoyama, Kazuyoshi Yoshii}{articles/004_Paper}
+\includepaper{On The Evaluation Of Rhythmic And Melodic Descriptors}{Maria Panteli, Simon Dixon}{articles/161_Paper}
+\includepaper{On The Potential Of Simple Framewise Approaches To Piano Transcription}{Rainer Kelz, Matthias Dorfer, Filip Korzeniowski, Sebastian Böck, Andreas Arzt, Gerhard Widmer}{articles/179_Paper}
+\includepaper{Phrase-Level Audio Segmentation Of Jazz Improvisations Informed By Symbolic Data}{Jeff Gregorio, Youngmoo Kim}{articles/245_Paper}
+\includepaper{Simultaneous Separation And Segmentation In Layered Music}{Prem Seetharaman, Bryan Pardo}{articles/057_Paper}
+\includepaper{Symbolic Meter Detection Using Inner Metric Analysis}{W. Bas de Haas, Anja Volk}{articles/033_Paper}
+\includepaper{Towards Modeling And Decomposing Loop-Based Electronic Music}{Patricio López-Serrano, Christian Dittmar, Jonathan Driedger, Meinard Mueller}{articles/065_Paper}
+\includepaper{Two (Note) Heads Are Better Than One: Pen-Based Multimodal Interaction With Music Notation}{Jorge Calvo-Zaragoza, David Rizo, Jose M. Iñesta}{articles/006_Paper}
+\includepaper{Whither The Design Of Experiments In Mir?}{Bob L. Sturm}{articles/128_Paper}
 
@@
 
-\includepaper{Cross-collection evaluation for music classification tasks}{Dmitry Bogdanov, Alastair Porter, Perfecto Herrera and Xavier Serra}{articles/220_Paper}
-\includepaper{I Said it First: Topological Analysis of Lyrical Influence Networks}{Jack Atherton and Blair Kaneshiro}{articles/221_Paper}
-\includepaper{Exploring Customer Reviews for Music Genre Classification and Evolutionary Studies}{Sergio Oramas, Luis Espinosa-Anke, Aonghus Lawlor, Horacio Saggion and Xavier Serra}{articles/240_Paper}
-\includepaper{DOWNBEAT TRACKING USING BEAT SYNCHRONOUS FEATURES WITH RECURRENT NEURAL NETWORKS}{Florian Krebs, Sebastian Böck, Matthias Dorfer and Gerhard Widmer}{articles/249_Paper}
-\includepaper{Learning and Visualizing Music Specifications Using Pattern Graphs}{Rafael Valle, Alexandre Donzé, Daniel J. Fremont, Ilge Akkaya, Sanjit A. Seshia and Adrian Freed}{articles/280_Paper}
-\includepaper{AVA: An Interactive System for Visual and Quantitative Analyses of Vibrato and Portamento Performance Styles}{Luwei Yang, Elaine Chew and Khalid Z. Rajab}{articles/314_Paper}
-\includepaper{A Hierarchical Bayesian Model of Chords, Pitches, and Spectrograms for Multipitch Analysis}{Yuta Ojima, Eita Nakamura, Katsutoshi Itoyama and Kazuyoshi Yoshii}{articles/003_Paper}
-\includepaper{Symbolic Meter Detection using Inner Metric Analysis}{W. Bas de Haas and Anja Volk}{articles/033_Paper}
-\includepaper{CROSS TASK STUDY ON MIREX RECENT RESULTS: AN INDEX FOR EVOLUTION MEASUREMENT AND SOME STAGNATION HYPOTHESES}{Ricardo Scholz, Geber Ramalho and Giordano Cabral}{articles/054_Paper}
-\includepaper{Towards Modeling and Decomposing Loop-Based Electronic Music}{Patricio López-Serrano, Christian Dittmar, Jonathan Driedger and Meinard Mueller}{articles/065_Paper}
-\includepaper{Human-Interactive Optical Music Recognition}{Liang Chen, Erik Stolterman and Christopher Raphael}{articles/106_Paper}
-\includepaper{A corpus of annotated Irish traditional dance music recordings: design and benchmark evaluations}{Pierre Beauguitte, Bryan Duggan and John Kelleher}{articles/148_Paper}
-\includepaper{Jazz Expressive Performance Modeling}{Helena Bantulà, Sergio Giraldo and Rafael Ramírez}{articles/162_Paper}
-\includepaper{Landmark-based Audio Fingerprinting for DJ Mix Monitoring}{Reinhard Sonnleitner, Andreas Arzt and Gerhard Widmer}{articles/187_Paper}
-\includepaper{Mining Online Music Listening Trajectories}{Flavio Figueiredo, Bruno Ribeiro, Jussara M. Almeida, Nazareno Andrade and Christos Faloutsos}{articles/193_Paper}
-\includepaper{Good-sounds.org: a framework to explore goodness in instrumental sounds}{Giuseppe Bandiera, Oriol Romani Picas and Xavier Serra}{articles/199_Paper}
-\includepaper{Adaptive Frequency Neural Networks for Dynamic Pulse and Metre Perception}{Andrew Lambert, Tillman Weyde and Newton Armstrong}{articles/228_Paper}
-\includepaper{Integration and Quality Assessment of Heterogeneous Chord Sequences using Data Fusion}{Hendrik Vincent Koops, W. Bas de Haas, Dimitrios Bountouridis and Anja Volk}{articles/019_Paper}
-\includepaper{Can Microblogs Predict Music Charts?
-An Analysis of the Relationship between \#Nowplaying Tweets and Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf and Günther Specht}{articles/039_Paper}
-\includepaper{Mixtape: Direction-based navigation in large music collections}{Joao Paulo V.
-Cardoso, Luciana Fujii Pontello, Pedro H.
-F.
-Holanda, Bruno Guilherme, Olga Goussevskaia and Ana Paula Couto da SIlva}{articles/155_Paper}
-\includepaper{An Evaluation Framework and Case Study for Rhythmic Concatenative Synthesis}{Cárthach Ó Nuanáin, Perfecto Herrera and Sergi Jordà}{articles/180_Paper}
-\includepaper{Interactive Scores in Classical Music Production}{Simon Waloschek, Axel Berndt, Benjamin W. Bohl and Aristotelis Hadjakos}{articles/192_Paper}
-\includepaper{An Analysis of Agreement in Classical Music Perception and Its Relationship to Listener Characteristics}{Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez and Marko Tkalcic}{articles/260_Paper}
-\includepaper{STRUCTURAL SEGMENTATION AND VISUALIZATION OF SITAR AND SAROD CONCERT AUDIO}{Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli and Preeti Rao}{articles/151_Paper}
-\includepaper{Minimax Viterbi algorithm for HMM-based Guitar fingering decision}{Gen Hori and Shigeki Sagayama}{articles/285_Paper}
+\includepaper{A Comparison Of Melody Extraction Methods Based On Source-Filter Modelling}{Juan J. Bosch, Rachel M. Bittner, Justin Salamon, Emilia Gómez}{articles/256_Paper}
+\includepaper{A Dataset For Automatic Practice Logging}{R. Michael Winters, Siddharth Gururani, Alexander Lerch}{articles/181_Paper}
+\includepaper{An Analysis Of Agreement In Classical Music Perception And Its Relationship To Listener Characteristics}{Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez, Marko Tkalcic}{articles/260_Paper}
+\includepaper{Automatic Drum Transcription Using Bi-Directional Recurrent Neural Networks}{Carl Southall, Ryan Stables, Jason Hockman}{articles/217_Paper}
+\includepaper{Data-Driven Exploration Of Melodic Structure In Hindustani Music}{Kaustuv Kanti Ganguli, Sankalp Gulati, Xavier Serra, Preeti Rao}{articles/121_Paper}
+\includepaper{Elucidating User Behavior In Music Services Through Persona And Gender}{John Fuller, Lauren Hubener, Yea-Seul Kim, Jin Ha Lee}{articles/205_Paper}
+\includepaper{Exploring The Latent Structure Of Collaborations In Music Production}{Nazareno Andrade, Flavio Figueiredo}{articles/251_Paper}
+\includepaper{Human-Interactive Optical Music Recognition}{Liang Chen, Erik Stolterman, Christopher Raphael}{articles/106_Paper}
+\includepaper{I Said It First: Topological Analysis Of Lyrical Influence Networks}{Jack Atherton, Blair Kaneshiro}{articles/221_Paper}
+\includepaper{Impact Of Music On Decision Making In Quantitative Tasks}{Elad Liebman, Peter Stone, Corey White}{articles/272_Paper}
+\includepaper{Interactive Scores In Classical Music Production}{Simon Waloschek, Axel Berndt, Benjamin W. Bohl, Aristotelis Hadjakos}{articles/192_Paper}
+\includepaper{Jazz Expressive Performance Modeling}{Helena Bantulà, Sergio Giraldo, Rafael Ramírez}{articles/162_Paper}
+\includepaper{Large-Scale Organization Of Hierarchical Music Analyses}{Phillip Kirlin}{articles/259_Paper}
+\includepaper{Learning Invariants For Instrument Recognition}{Vincent Lostanlen, Carmine Emanuele Cella}{articles/093_Paper}
+\includepaper{Mining Musical Traits Of Social Functions In Native American Music}{Daniel Shanahan, Kerstin Neubarth, Darrell Conklin}{articles/167_Paper}
+\includepaper{Mining Online Music Listening Trajectories}{Flavio Figueiredo, Bruno Ribeiro, Jussara M. Almeida, Nazareno Andrade, Christos Faloutsos}{articles/193_Paper}
+\includepaper{Musical Typicality: How Many Similar Songs Exist?}{Tomoyasu Nakano, Daichi Mochihashi, Kazuyoshi Yoshii, Masataka Goto}{articles/191_Paper}
+\includepaper{Musicdb: A Platform For Longitudinal Music Analytics}{Jeremy Hyrkas, Bill Howe}{articles/284_Paper}
+\includepaper{Noise Robust Music Artist Recognition Using I-Vector Features}{Hamid Eghbal-zadeh, Gerhard Widmer}{articles/037_Paper}
+\includepaper{On Practical Strategies Of Melody Indexing For Query By Humming}{Bartlomiej Stasiak}{articles/089_Paper}
+\includepaper{On The Use Of Note Onsets For Improved Lyrics-To-Audio Alignment}{Georgi Dzhambazov, Ajay Srinivasamurthy, Sertan Sentürk, Xavier Serra}{articles/243_Paper}
+\includepaper{Piano Transcription Using An Exponential Decay Model}{Tian Cheng, Matthias Mauch, Emmanouil Benetos, Simon Dixon}{articles/085_Paper}
+\includepaper{Querying Xml Score Databases: Xquery Is Not Enough!}{Raphael Fournier-S'niehotta, Philippe Rigaux, Nicolas Travers}{articles/136_Paper}
+\includepaper{Recurrent Neural Networks For Drum Transcription}{Richard Vogl, Matthias Dorfer, Peter Knees}{articles/269_Paper}
+\includepaper{Singing Voice Melody Transcription Using Deep Neural Networks}{François Rigaud, Mathieu Radenen}{articles/163_Paper}
+\includepaper{Sparse Coding Based Music Genre Classification Using Spectro-Temporal Modulations}{Chih-Shan Lin, Kai-Chun Hsu, Tai-Shih Chi}{articles/046_Paper}
+\includepaper{Time-Delayed Melody Surfaces For Rāga Recognition}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan Şentürk, Xavier Serra}{articles/030_Paper}
+\includepaper{Transcribing Human Piano Performances Into Music Notation}{Andrea Cogliati, David Temperley, Zhiyao Duan}{articles/088_Paper}
+\includepaper{Wimir: An Informetric Study On Women Authors In Ismir}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham, J. Stephen Downie}{articles/283_Paper}

### 2016-07-11 deriveFiles.py

@@ -41,7 +41,7 @@ def generatePapersDotTex(csvFile):
             lastSession = session
             
             papersDotTex.write('\includepaper{%s}{%s}{articles/%03d_Paper}\n'
-                               % (title, authors, int(number)))
+                               % (latexEscape(title), andToComma(authors), int(number)))
 
 
 def papersSectionHeader(name, page):
@@ -54,6 +54,12 @@ def papersSectionHeader(name, page):
 
 """ % (name, page)
     return chunk
+
+def latexEscape(string):
+    return string.replace('#','\#').replace('_','\_').replace('$','\$')
+
+def andToComma(string):
+    return string.replace(' and ', ', ')
 
 def loadSessionInfo():
     return {k: (name, int(num)) for k, name, num

### 2016-07-12 2016_Proceedings_ISMIR/keynotes.tex
updated TOC info for keynotes and tutorials
updated list of paper info
updated keynote information

@@
 % Keynote talk 1
-\includeabstract{Integrating Music Information Sources for Music Production and Consumption}{Mark Sandler}{external/10-1_Keynotes-1.pdf}
+%\includeabstract{Keynote 1}{Speaker 1}{external/10-1_Keynotes-1.pdf}{}
+\includeabstract{The New York Philharmonic Leon Levy Digital Archives:
+An Integrated View of Performance Since 1842}{Barbara Haws, Archivist
+and Historian, New York Philharmonic}{Abstract: For nearly 175 years the New York Philharmonic has been assiduously documenting and keeping all facets of its existence in whatever formats were available; marked conducting scores, orchestra parts, printed programs, business records, contracts, letters, newspaper reviews, audio and video.
+With the digitization of this material, it is possible for the first time to see the relationships between seemingly disparate materials that expand our understanding of the performance experience and the music itself.
+As well, especially through the GitHub repository, unanticipated applications of the data have occurred.
+Working towards the year 2066, the challenge is to incorporate the new formats of the modern era to ensure that the single longest running dataset of a performing institution continues.
+}{Bio: Barbara Haws has been the Archivist and Historian of the New
+York Philharmonic since 1984.  Haws has lectured extensively about the
+Philharmonic’s past and curated major exhibitions here and in
+Europe. She is a Grammy nominated producer of the Philharmonic’s
+Special Editions historic recordings. Haws along with Burton Bernstein
+is the author of Leonard Bernstein: American Original published by
+Harper Collins, 2008 and the essay ``U.C. Hill, An American Musician
+Abroad (1835-37)''. Since 2009, Haws has led an effort funded by the
+Leon Levy Foundation to digitize more than three million pages of
+archival material since 1842, making it freely available over the
+internet. The Digital Archives project was recently featured on
+FiveThirtyEight podcast ``What's The Point''.}
 
@@
 % Keynote talk 2
-\includeabstract{The Promise of Music Information Retrieval: Are we there yet?}{J.\ Stephen Downie}{external/10-2_Keynotes-2.pdf}
+%\includeabstract{Keynote 2}{Speaker 2}{external/10-2_Keynotes-2.pdf}{}
+\includeabstract{Is Machine Learning Enough?}{Beth Logan, PhD, VP, Optimization, DataXu}{Abstract: We live in a world unimaginable even 20 years ago.
+From our phones we can summon a car, book a vacation and of course access the word’s music to find just those songs we like, even songs we didn't know we liked.
+Automated Machine Learning at scale enables these and thousands more applications.
+But in business, it’s good to know when to stop.
+It's not always smart to automate that last, difficult 10\% of performance.
+Indeed in music and other industries, humans often curate the results.
+Will humans always be in the loop or will the machines eventually take over?
+Will Machine Learning ever be enough?}{Bio: Beth is the VP of Optimization at DataXu, a leader in programatic marketing.
+She has made contributions to a wide variety of fields, including speech recognition, music indexing and in-home activity monitoring.
+Beth holds a PhD in speech recognition from the University of Cambridge.}

### 2016-07-12 2016_Proceedings_ISMIR/papers.tex
updated paper list to correspond to camera ready papers

@@
 \includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs, Gerhard Widmer}{articles/186_Paper}
-\includepaper{Bayesian meter tracking on learned signal representations}{Andre Holzapfel, Thomas Grill}{articles/132_Paper}
+\includepaper{Bayesian Meter Tracking on Learned Signal Representations}{Andre Holzapfel, Thomas Grill}{articles/132_Paper}
 \includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font, Xavier Serra}{articles/195_Paper}
@@
 
-\includepaper{A Plan For Sustainable Mir Evaluation}{Brian McFee, Eric Humphrey, Julián Urbano}{articles/257_Paper}
-\includepaper{Go With The Flow: When Listeners Use Music As Technology}{Andrew Demetriou, Martha Larson, Cynthia C. S. Liem}{articles/068_Paper}
-\includepaper{A Look At The Cloud From Both Sides Now: An Analysis Of Cloud Music Service Usage}{Jin Ha Lee, Yea-Seul Kim, Chris Hubbles}{articles/087_Paper}
+\includepaper{A Plan for Sustainable MIR Evaluation}{Brian McFee, Eric Humphrey, Julián Urbano}{articles/257_Paper}
+\includepaper{Go with the Flow: When Listeners Use Music as Technology}{Andrew Demetriou, Martha Larson, Cynthia C. S. Liem}{articles/068_Paper}
+\includepaper{A Look at the Cloud from Both Sides Now: An Analysis of Cloud Music Service Usage}{Jin Ha Lee, Yea-Seul Kim, Chris Hubbles}{articles/087_Paper}
 
@@
 
-\includepaper{Analyzing Measure Annotations For Western Classical Music Recordings}{Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz, Meinard Müller}{articles/079_Paper}
-\includepaper{Instrumental Idiom In The 16Th Century: Patterns In Arrangements Of Vocal Music}{David Lewis, Tim Crawford, Daniel Müllensiefen}{articles/165_Paper}
-\includepaper{The Sousta Corpus: Beat-Informed Automatic Transcription Of Traditional Dance Tunes}{Andre Holzapfel, Emmanouil Benetos}{articles/156_Paper}
-\includepaper{Learning A Feature Space For World Music Style Similarity}{Maria Panteli, Emmanouil Benetos, Simon Dixon}{articles/166_Paper}
+\includepaper{Analyzing Measure Annotations for Western Classical Music Recordings}{Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz, Meinard Mueller}{articles/079_Paper}
+\includepaper{Instrumental Idiom in the 16th Century: Embellishment Patterns in Arrangements of Vocal Music}{David Lewis, Tim Crawford, Daniel Müllensiefen}{articles/165_Paper}
+\includepaper{The Sousta Corpus: Beat-Informed Automatic Transcription of Traditional Dance Tunes}{Andre Holzapfel, Emmanouil Benetos}{articles/156_Paper}
+\includepaper{Learning a Feature Space for Similarity in World Music}{Maria Panteli, Emmanouil Benetos, Simon Dixon}{articles/166_Paper}
 
@@
 
-\includepaper{Systematic Exploration Of Computational Music Structure Research}{Oriol Nieto, Juan Pablo Bello}{articles/043_Paper}
-\includepaper{Using Priors To Improve Estimates Of Music Structure}{Jordan Smith, Masataka Goto}{articles/135_Paper}
+\includepaper{Systematic Exploration of Computational Music Structure Research}{Oriol Nieto, Juan Pablo Bello}{articles/043_Paper}
+\includepaper{Using Priors to Improve Estimates of Music Structure}{Jordan Smith, Masataka Goto}{articles/135_Paper}
+\includepaper{Music Structural Segmentation Across Genres with Gammatone Features}{Mi Tian, Mark Sandler}{articles/032_Paper}
 
@@
 
-\includepaper{Music Structural Segmentation Across Genres With Gammatone Features}{Mi Tian, Mark B. Sandler}{articles/032_Paper}
-\includepaper{Automatic Melodic Reduction Using A Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
-\includepaper{A Neural Greedy Model For Voice Separation In Symbolic Music}{Patrick Gray, Razvan Bunescu}{articles/296_Paper}
+\includepaper{Automatic Melodic Reduction Using a Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
+\includepaper{A Neural Greedy Model for Voice Separation in Symbolic Music}{Patrick Gray, Razvan Bunescu}{articles/296_Paper}
+\includepaper{Towards Score Following In Sheet Music Images}{Matthias Dorfer, Andreas Arzt, Gerhard Widmer}{articles/027_Paper}
+\includepaper{Extracting Ground-Truth Information from MIDI Files: A MIDIfesto}{Colin Raffel, Daniel Ellis}{articles/105_Paper}
 
@@
 
-\includepaper{Towards Reading Sheet Music}{Matthias Dorfer, Andreas Arzt, Gerhard Widmer}{articles/027_Paper}
-\includepaper{Extracting Ground-Truth Information From Midi Files: A Midifesto}{Colin Raffel, Daniel Ellis}{articles/105_Paper}
-\includepaper{Automatic Tagging Using Deep Convolutional Neural Networks}{Keunwoo Choi, George Fazekas, Mark Sandler}{articles/009_Paper}
-\includepaper{A Hybrid Gaussian-Hmm-Deep Learning Approach For Automatic Chord Estimation With Very Large Vocabulary}{Junqi Deng, Yu-Kwong Kwok}{articles/058_Paper}
-\includepaper{Singing Melody Extraction Using Multi-Column Deep Neural Networks}{Sangeun Kum, Changheun Oh, Juhan Nam}{articles/119_Paper}
+\includepaper{Automatic Tagging Using Deep Convolutional Neural Networks}{Keunwoo Choi, György Fazekas, Mark Sandler}{articles/009_Paper}
+\includepaper{A Hybrid Gaussian-HMM-Deep Learning Approach for Automatic Chord Estimation with Very Large Vocabulary}{Junqi Deng, Yu-Kwong Kwok}{articles/058_Paper}
+\includepaper{Melody Extraction on Vocal Segments Using Multi-Column Deep Neural Networks}{Sangeun Kum, Changheun Oh, Juhan Nam}{articles/119_Paper}
 
@@
 
-\includepaper{An Ontology For Audio Features}{Alo Allik, György Fazekas, Mark Sandler}{articles/077_Paper}
-\includepaper{Adaptive Frequency Neural Networks For Dynamic Pulse And Metre Perception}{Andrew Lambert, Tillman Weyde, Newton Armstrong}{articles/228_Paper}
-\includepaper{Listen To Me – Don'T Listen To Me: What Communities Of Critics Tell Us About Music}{Ben Fields, Christophe Rhodes}{articles/173_Paper}
-\includepaper{An Evaluation Framework And Case Study For Rhythmic Concatenative Synthesis}{Cárthach Ó Nuanáin, Perfecto Herrera, Sergi Jordà}{articles/180_Paper}
-\includepaper{On Drum Playing Technique Detection In Polyphonic Mixtures}{Chih-Wei Wu, Alexander Lerch}{articles/268_Paper}
-\includepaper{Analysis And Classification Of Phonation Modes In Singing}{Daniel Stoller, Simon Dixon}{articles/233_Paper}
-\includepaper{Nonnegative Tensor Factorization With Frequency Modulation Cues For Blind Audio Source Separation}{Elliot Creager, Noah Stein, Roland Badeau}{articles/103_Paper}
-\includepaper{Downbeat Tracking Using Beat Synchronous Features With Recurrent Neural Networks}{Florian Krebs, Sebastian Böck, Matthias Dorfer, Gerhard Widmer}{articles/249_Paper}
-\includepaper{Automatic Music Recommendation Systems: Do Demographic, Profiling, And Contextual Features Improve Their Performance?}{Gabriel Vigliensoni, Ichiro Fujinaga}{articles/044_Paper}
-\includepaper{Composer Recognition Based On 2D-Filtered Piano-Rolls}{Gissel Velarde, Carlos Cancino Chacón, David Meredith, Weyde Tillman, Maaten Grachten}{articles/063_Paper}
-\includepaper{Integration And Quality Assessment Of Heterogeneous Chord Sequences Using Data Fusion}{Hendrik Vincent Koops, W. Bas de Haas, Dimitrios Bountouridis, Anja Volk}{articles/019_Paper}
-\includepaper{Predicting Missing Music Components With Bidirectional Long Short-Term Memory Neural Networks}{I-Ting Liu, Richard Randall}{articles/097_Paper}
-\includepaper{Further Steps Towards A Standard Testbed For Optical Music Recognition}{Jan Hajič, jr., Jiří Novotný, Pavel Pecina, Jaroslav Pokorný}{articles/289_Paper}
-\includepaper{Analysis Of Vocal Imitations Of Pitch Trajectories}{Jiajie Dai, Simon Dixon}{articles/127_Paper}
-\includepaper{Towards Template-Based Vibrato Analysis In Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}
-\includepaper{Enhancing Cover Song Identification With Hierarchical Rank Aggregation}{Julien Osmalskyj, Marc Van Droogenbroeck, Jean-Jacques Embrechts}{articles/064_Paper}
-\includepaper{Conversations With Expert Users In Music Retrieval And Research Challenges For Creative Mir}{Kristina Andersen, Peter Knees}{articles/246_Paper}
-\includepaper{Ava: An Interactive System For Visual And Quantitative Analyses Of Vibrato And Portamento Performance Styles}{Luwei Yang, Elaine Chew, Khalid Z. Rajab}{articles/314_Paper}
-\includepaper{Improving Voice Separation By Better Connecting Contigs}{Nicolas Guiomard-Kagan, Mathieu Giraud, Richard Groult, Florence Levé}{articles/129_Paper}
-\includepaper{A Corpus Of Annotated Irish Traditional Dance Music Recordings: Design And Benchmark Evaluations}{Pierre Beauguitte, Bryan Duggan, John Kelleher}{articles/148_Paper}
-\includepaper{Learning And Visualizing Music Specifications Using Pattern Graphs}{Rafael Valle, Alexandre Donzé, Daniel J. Fremont, Ilge Akkaya, Sanjit A. Seshia, Adrian Freed}{articles/280_Paper}
-\includepaper{Landmark-Based Audio Fingerprinting For Dj Mix Monitoring}{Reinhard Sonnleitner, Andreas Arzt, Gerhard Widmer}{articles/187_Paper}
-\includepaper{Long-Term Reverberation Modeling In Under-Determined Audio Source Separation}{Romain Hennequin, François Rigaud}{articles/196_Paper}
-\includepaper{Exploring Customer Reviews For Music Genre Classification And Evolutionary Studies}{Sergio Oramas, Luis Espinosa-Anke, Aonghus Lawlor, Horacio Saggion, Xavier Serra}{articles/240_Paper}
-\includepaper{Towards Evaluating Multiple Predominant Melody Annotations In Jazz Recordings}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar, Meinard Mueller}{articles/049_Paper}
-\includepaper{Ensemble: A Hybrid Human-Machine System For Generating Melody Scores From Audio}{Tim Tse, Justin Salamon, Alex Williams, Helga Jiang, Edith Law}{articles/072_Paper}
-\includepaper{Integer Programming Formulation Of The Problem Of Generating Milton Babbitt'S All-Partition Arrays}{Tsubasa Tanaka, Brian Bemman, David Meredith}{articles/034_Paper}
-\includepaper{Structural Segmentation And Visualization Of Sitar And Sarod Concert Audio}{Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}
-\includepaper{Automatic Outlier Detection In Music Datasets}{Yen-Cheng Lu, Chih-Wei Wu, Alexander Lerch, Chang-Tien Lu}{articles/215_Paper}
+\includepaper{A Corpus of Annotated Irish Traditional Dance Music Recordings: Design and Benchmark Evaluations}{Pierre Beauguitte, Bryan Duggan, John Kelleher}{articles/148_Paper}
+\includepaper{Adaptive Frequency Neural Networks for Dynamic Pulse and Metre Perception}{Andrew Lambert, Tillman Weyde, Newton Armstrong}{articles/228_Paper}
+\includepaper{An Evaluation Framework and Case Study for Rhythmic Concatenative Synthesis}{Cárthach Ó Nuanáin, Perfecto Herrera, Sergi Jordà}{articles/180_Paper}
+\includepaper{An Ontology for Audio Features}{Alo Allik, György Fazekas, Mark Sandler}{articles/077_Paper}
+\includepaper{Analysis and Classification of Phonation Modes In Singing}{Daniel Stoller, Simon Dixon}{articles/233_Paper}
+\includepaper{Analysis of Vocal Imitations of Pitch Trajectories}{Jiajie Dai, Simon Dixon}{articles/127_Paper}
+\includepaper{Automatic Music Recommendation Systems: Do Demographic, Profiling, and Contextual Features Improve Their Performance?}{Gabriel Vigliensoni, Ichiro Fujinaga}{articles/044_Paper}
+\includepaper{Automatic Outlier Detection in Music Genre Datasets}{Yen-Cheng Lu, Chih-Wei Wu, Alexander Lerch, Chang-Tien Lu}{articles/215_Paper}
+\includepaper{AVA: An Interactive System for Visual and Quantitative Analyses of Vibrato and Portamento Performance Styles}{Luwei Yang, Khalid Z. Rajab, Elaine Chew}{articles/314_Paper}
+\includepaper{Composer Recognition Based on 2D-Filtered Piano-Rolls}{Gissel Velarde, Tillman Weyde, Carlos Cancino Chacón, David Meredith, Maarten Grachten}{articles/063_Paper}
+\includepaper{Conversations with Expert Users in Music Retrieval and Research Challenges for Creative MIR}{Kristina Andersen, Peter Knees}{articles/246_Paper}
+\includepaper{Downbeat Tracking Using Beat Synchronous Features with Recurrent Neural Networks}{Florian Krebs, Sebastian Böck, Matthias Dorfer, Gerhard Widmer}{articles/249_Paper}
+\includepaper{Enhancing Cover Song Identification with Hierarchical Rank Aggregation}{Julien Osmalskyj, Marc Van Droogenbroeck, Jean-Jacques Embrechts}{articles/064_Paper}
+\includepaper{Ensemble: A Hybrid Human-Machine System for Generating Melody Scores from Audio}{Tim Tse, Justin Salamon, Alex Williams, Helga Jiang, Edith Law}{articles/072_Paper}
+\includepaper{Exploring Customer Reviews for Music Genre Classification and Evolutionary Studies}{Sergio Oramas, Luis Espinosa-Anke, Aonghus Lawlor, Xavier Serra, Horacio Saggion}{articles/240_Paper}
+\includepaper{Further Steps Towards a Standard Testbed for Optical Music Recognition}{Jan Hajič jr., Jiří Novotný, Pavel Pecina, Jaroslav Pokorný}{articles/289_Paper}
+\includepaper{Improving Voice Separation by Better Connecting Contigs}{Nicolas Guiomard-Kagan, Mathieu Giraud, Richard Groult, Florence Levé}{articles/129_Paper}
+\includepaper{Integer Programming Formulation of the Problem of Generating Milton Babbitt's All-Partition Arrays}{Tsubasa Tanaka, Brian Bemman, David Meredith}{articles/034_Paper}
+\includepaper{Integration and Quality Assessment of Heterogeneous Chord Sequences Using Data Fusion}{Hendrik Vincent Koops, W. Bas de Haas, Dimitrios Bountouridis, Anja Volk}{articles/019_Paper}
+\includepaper{Landmark-Based Audio Fingerprinting for DJ Mix Monitoring}{Reinhard Sonnleitner, Andreas Arzt, Gerhard Widmer}{articles/187_Paper}
+\includepaper{Learning and Visualizing Music Specifications Using Pattern Graphs}{Rafael Valle, Daniel J. Fremont, Ilge Akkaya, Alexandre Donzé, Adrian Freed, Sanjit A. Seshia}{articles/280_Paper}
+\includepaper{Listen To Me – Don't Listen To Me: What Communities of Critics Tell Us About Music}{Ben Fields, Christophe Rhodes}{articles/173_Paper}
+\includepaper{Long-Term Reverberation Modeling for Under-Determined Audio Source Separation with Application to Vocal Melody Extraction}{Romain Hennequin, François Rigaud}{articles/196_Paper}
+\includepaper{Nonnegative Tensor Factorization with Frequency Modulation Cues for Blind Audio Source Separation}{Elliot Creager, Noah Stein, Roland Badeau, Philippe Depalle}{articles/103_Paper}
+\includepaper{On Drum Playing Technique Detection in Polyphonic Mixtures}{Chih-Wei Wu, Alexander Lerch}{articles/268_Paper}
+\includepaper{Predicting Missing Music Components with Bidirectional Long Short-Term Memory Neural Networks}{I-Ting Liu, Richard Randall}{articles/097_Paper}
+\includepaper{Structural Segmentation and Visualization of Sitar and Sarod Concert Audio}{Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}
+\includepaper{Template-Based Vibrato Analysis in Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}
+\includepaper{Towards Evaluating Multiple Predominant Melody Annotations in Jazz Recordings}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar, Meinard Mueller}{articles/049_Paper}
 
@@
 
-\includepaper{A Hierarchical Bayesian Model Of Chords, Pitches, And Spectrograms For Multipitch Analysis}{Yuta Ojima, Eita Nakamura, Katsutoshi Itoyama, Kazuyoshi Yoshii}{articles/003_Paper}
-\includepaper{A Higher-Dimensional Expansion Of Affective Norms For English Terms For Music Tagging}{Michele Buccoli, Massimiliano Zanoni, György Fazekas, Augusto Sarti, Mark Sandler, Stefano Tubaro}{articles/253_Paper}
-\includepaper{A Latent Space Approach To Listening Behavior Analysis}{Chia-Hao Chung, Jing-Kai Lou, Homer Chen}{articles/110_Paper}
-\includepaper{A Methodology For Quality Assessment In Collaborative Score Libraries}{Vincent Besson, Marco Gurrieri, Philippe Rigaux, Alice Tacaille, Virginie Thion}{articles/076_Paper}
-\includepaper{Aligned Hierarchies: A Multi-Scale Structure-Based Representation For Music-Based Data Streams}{Katherine M. Kinnaird}{articles/020_Paper}
-\includepaper{Analysing Scattering-Based Music Content Analysis Systems: Where'S The Music?}{Francisco Rodríguez-Algarra, Bob L. Sturm, Hugo Maruri-Aguilar}{articles/146_Paper}
-\includepaper{Beat Tracking With A Cepstroid Invariant Neural Network}{Anders Elowsson}{articles/252_Paper}
-\includepaper{Bootstrapping A System For Phoneme Recognition And Keyword Spotting In Unaccompanied Singing}{Anna Kruspe}{articles/070_Paper}
+\includepaper{A Hierarchical Bayesian Model of Chords, Pitches, and Spectrograms for Multipitch Analysis}{Yuta Ojima, Eita Nakamura, Katsutoshi Itoyama, Kazuyoshi Yoshii}{articles/003_Paper}
+\includepaper{A Higher-Dimensional Expansion of Affective Norms for English Terms for Music Tagging}{Michele Buccoli, Massimiliano Zanoni, György Fazekas, Augusto Sarti, Mark Sandler}{articles/253_Paper}
+\includepaper{A Latent Representation of Users, Sessions, and Songs for Listening Behavior Analysis}{Chia-Hao Chung, Jing-Kai Lou, Homer Chen}{articles/110_Paper}
+\includepaper{A Methodology for Quality Assessment in Collaborative Score Libraries}{Vincent Besson, Marco Gurrieri, Philippe Rigaux, Alice Tacaille, Virginie Thion}{articles/076_Paper}
+\includepaper{Aligned Hierarchies: A Multi-Scale Structure-Based Representation for Music-Based Data Streams}{Katherine M. Kinnaird}{articles/020_Paper}
+\includepaper{Analysing Scattering-Based Music Content Analysis Systems: Where's the Music?}{Francisco Rodríguez-Algarra, Bob L. Sturm, Hugo Maruri-Aguilar}{articles/146_Paper}
+\includepaper{Beat Tracking with a Cepstroid Invariant Neural Network}{Anders Elowsson}{articles/252_Paper}
+\includepaper{Bootstrapping a System for Phoneme Recognition and Keyword Spotting in Unaccompanied Singing}{Anna Kruspe}{articles/070_Paper}
 \includepaper{Can Microblogs Predict Music Charts?
-An Analysis Of The Relationship Between \#Nowplaying Tweets And Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf, Günther Specht}{articles/039_Paper}
-\includepaper{Cross Task Study On Mirex Recent Results: An Index For Evolution Measurement And Some Stagnation Hypotheses}{Ricardo Scholz, Geber Ramalho, Giordano Cabral}{articles/054_Paper}
-\includepaper{Cross-Collection Evaluation For Music Classification Tasks}{Dmitry Bogdanov, Alastair Porter, Perfecto Herrera, Xavier Serra}{articles/220_Paper}
-\includepaper{Downbeat Detection With Conditional Random Fields And Deep Learned Features}{Simon Durand, Slim Essid}{articles/213_Paper}
-\includepaper{Exploiting Frequency, Periodicity And Harmonicity Using Advanced Time-Frequency Concentration Techniques For Multipitch Estimation Of Choir And Symphony}{Li Su, Tsung-Ying Chuang, Yi-Hsuan Yang}{articles/104_Paper}
-\includepaper{Genre Ontology Learning: Comparing Curated With Crowd-Sourced Ontologies}{Hendrik Schreiber}{articles/074_Paper}
-\includepaper{Genre Specific Dictionaries For Harmonic/Percussive Source Separation}{Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski, Gaël Richard}{articles/042_Paper}
-\includepaper{Good-Sounds.Org: A Framework To Explore Goodness In Instrumental Sounds}{Giuseppe Bandiera, Oriol Romani Picas, Xavier Serra}{articles/199_Paper}
-\includepaper{Improving Predictions Of Derived Viewpoints In Multiple Viewpoints Systems}{Thomas Hedges, Geraint Wiggins}{articles/208_Paper}
-\includepaper{Learning Temporal Feature Using Deep Neural Network And Its Application To Music Genre Classification}{Il-Young Jeong, Kyogu Lee}{articles/159_Paper}
-\includepaper{Live Song Id: A Hashprint Approach}{TJ Tsai, Thomas Praetzlich, Meinard Mueller}{articles/098_Paper}
-\includepaper{Minimax Viterbi Algorithm For Hmm-Based Guitar Fingering Decision}{Gen Hori, Shigeki Sagayama}{articles/285_Paper}
-\includepaper{Mixtape: Direction-Based Navigation In Large Music Collections}{Joao Paulo V.
+An Analysis of the Relationship Between \#Nowplaying Tweets and Music Charts}{Eva Zangerle, Martin Pichl, Benedikt Hupfauf, Günther Specht}{articles/039_Paper}
+\includepaper{Cross Task Study on MIREX Recent Results: An Index for Evolution Measurement and Some Stagnation Hypotheses}{Ricardo Scholz, Geber Ramalho, Giordano Cabral}{articles/054_Paper}
+\includepaper{Cross-Collection Evaluation for Music Classification Tasks}{Dmitry Bogdanov, Alastair Porter, Perfecto Herrera, Xavier Serra}{articles/220_Paper}
+\includepaper{Downbeat Detection with Conditional Random Fields and Deep Learned Features}{Simon Durand, Slim Essid}{articles/213_Paper}
+\includepaper{Exploiting Frequency, Periodicity and Harmonicity Using Advanced Time-Frequency Concentration Techniques for Multipitch Estimation of Choir and Symphony}{Li Su, Tsung-Ying Chuang, Yi-Hsuan Yang}{articles/104_Paper}
+\includepaper{Genre Ontology Learning: Comparing Curated with Crowd-Sourced Ontologies}{Hendrik Schreiber}{articles/074_Paper}
+\includepaper{Genre Specific Dictionaries for Harmonic/Percussive Source Separation}{Clément Laroche, Hélène Papadopoulos, Matthieu Kowalski, Gaël Richard}{articles/042_Paper}
+\includepaper{Good-sounds.org: A Framework to Explore Goodness in Instrumental Sounds}{Giuseppe Bandiera, Oriol Romani Picas, Xavier Serra}{articles/199_Paper}
+\includepaper{Improving Predictions of Derived Viewpoints in Multiple Viewpoints Systems}{Thomas Hedges, Geraint Wiggins}{articles/208_Paper}
+\includepaper{Known Artist Live Song ID: A Hashprint Approach}{TJ Tsai, Thomas Praetzlich, Meinard Mueller}{articles/098_Paper}
+\includepaper{Learning Temporal Features Using a Deep Neural Network and its Application to Music Genre Classification}{Il-Young Jeong, Kyogu Lee}{articles/159_Paper}
+\includepaper{Meter Detection in Symbolic Music Using Inner Metric Analysis}{W. Bas de Haas, Anja Volk}{articles/033_Paper}
+\includepaper{Minimax Viterbi Algorithm for HMM-Based Guitar Fingering Decision}{Gen Hori, Shigeki Sagayama}{articles/285_Paper}
+\includepaper{Mixtape: Direction-Based Navigation in Large Media Collections}{Joao Paulo V.
 Cardoso, Luciana Fujii Pontello, Pedro H.
 F.
-Holanda, Bruno Guilherme, Olga Goussevskaia, Ana Paula Couto da SIlva}{articles/155_Paper}
-\includepaper{Musical Note Estimation For F0 Trajectories Of Singing Voices Based On A Bayesian Semi-Beat-Synchronous Hmm}{Ryo Nishikimi, Eita Nakamura, Katsutoshi Itoyama, Kazuyoshi Yoshii}{articles/004_Paper}
-\includepaper{On The Evaluation Of Rhythmic And Melodic Descriptors}{Maria Panteli, Simon Dixon}{articles/161_Paper}
-\includepaper{On The Potential Of Simple Framewise Approaches To Piano Transcription}{Rainer Kelz, Matthias Dorfer, Filip Korzeniowski, Sebastian Böck, Andreas Arzt, Gerhard Widmer}{articles/179_Paper}
-\includepaper{Phrase-Level Audio Segmentation Of Jazz Improvisations Informed By Symbolic Data}{Jeff Gregorio, Youngmoo Kim}{articles/245_Paper}
-\includepaper{Simultaneous Separation And Segmentation In Layered Music}{Prem Seetharaman, Bryan Pardo}{articles/057_Paper}
-\includepaper{Symbolic Meter Detection Using Inner Metric Analysis}{W. Bas de Haas, Anja Volk}{articles/033_Paper}
-\includepaper{Towards Modeling And Decomposing Loop-Based Electronic Music}{Patricio López-Serrano, Christian Dittmar, Jonathan Driedger, Meinard Mueller}{articles/065_Paper}
-\includepaper{Two (Note) Heads Are Better Than One: Pen-Based Multimodal Interaction With Music Notation}{Jorge Calvo-Zaragoza, David Rizo, Jose M. Iñesta}{articles/006_Paper}
-\includepaper{Whither The Design Of Experiments In Mir?}{Bob L. Sturm}{articles/128_Paper}
+Holanda, Bruno Guilherme, Olga Goussevskaia, Ana Paula Couto da Silva}{articles/155_Paper}
+\includepaper{Musical Note Estimation for F0 Trajectories of Singing Voices Based on a Bayesian Semi-Beat-Synchronous HMM}{Ryo Nishikimi, Eita Nakamura, Katsutoshi Itoyama, Kazuyoshi Yoshii}{articles/004_Paper}
+\includepaper{On the Evaluation of Rhythmic and Melodic Descriptors for Music Similarity}{Maria Panteli, Simon Dixon}{articles/161_Paper}
+\includepaper{On the Potential of Simple Framewise Approaches to Piano Transcription}{Rainer Kelz, Matthias Dorfer, Filip Korzeniowski, Sebastian Böck, Andreas Arzt, Gerhard Widmer}{articles/179_Paper}
+\includepaper{Phrase-Level Audio Segmentation of Jazz Improvisations Informed by Symbolic Data}{Jeff Gregorio, Youngmoo Kim}{articles/245_Paper}
+\includepaper{Revisiting Priorities: Improving MIR Evaluation Practices}{Bob L. Sturm}{articles/128_Paper}
+\includepaper{Simultaneous Separation and Segmentation in Layered Music}{Prem Seetharaman, Bryan Pardo}{articles/057_Paper}
+\includepaper{Towards Modeling and Decomposing Loop-Based Electronic Music}{Patricio López-Serrano, Christian Dittmar, Jonathan Driedger, Meinard Mueller}{articles/065_Paper}
+\includepaper{Two (Note) Heads Are Better Than One: Pen-Based Multimodal Interaction with Music Scores}{Jorge Calvo-Zaragoza, David Rizo, Jose M. Iñesta}{articles/006_Paper}
 
@@
 
-\includepaper{A Comparison Of Melody Extraction Methods Based On Source-Filter Modelling}{Juan J. Bosch, Rachel M. Bittner, Justin Salamon, Emilia Gómez}{articles/256_Paper}
-\includepaper{A Dataset For Automatic Practice Logging}{R. Michael Winters, Siddharth Gururani, Alexander Lerch}{articles/181_Paper}
-\includepaper{An Analysis Of Agreement In Classical Music Perception And Its Relationship To Listener Characteristics}{Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez, Marko Tkalcic}{articles/260_Paper}
+\includepaper{A Comparison of Melody Extraction Methods Based on Source-Filter Modelling}{Juan J. Bosch, Rachel M. Bittner, Justin Salamon, Emilia Gómez}{articles/256_Paper}
+\includepaper{An Analysis of Agreement in Classical Music Perception and its Relationship to Listener Characteristics}{Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez, Marko Tkalcic}{articles/260_Paper}
+\includepaper{An Attack/Decay Model for Piano Transcription}{Tian Cheng, Matthias Mauch, Emmanouil Benetos, Simon Dixon}{articles/085_Paper}
 \includepaper{Automatic Drum Transcription Using Bi-Directional Recurrent Neural Networks}{Carl Southall, Ryan Stables, Jason Hockman}{articles/217_Paper}
-\includepaper{Data-Driven Exploration Of Melodic Structure In Hindustani Music}{Kaustuv Kanti Ganguli, Sankalp Gulati, Xavier Serra, Preeti Rao}{articles/121_Paper}
-\includepaper{Elucidating User Behavior In Music Services Through Persona And Gender}{John Fuller, Lauren Hubener, Yea-Seul Kim, Jin Ha Lee}{articles/205_Paper}
-\includepaper{Exploring The Latent Structure Of Collaborations In Music Production}{Nazareno Andrade, Flavio Figueiredo}{articles/251_Paper}
+\includepaper{Automatic Practice Logging: Introduction, Dataset \& Preliminary Study}{R. Michael Winters, Siddharth Gururani, Alexander Lerch}{articles/181_Paper}
+\includepaper{Data-Driven Exploration of Melodic Structure in Hindustani Music}{Kaustuv Kanti Ganguli, Sankalp Gulati, Xavier Serra, Preeti Rao}{articles/121_Paper}
+\includepaper{Deep Convolutional Networks on the Pitch Spiral For Music Instrument Recognition}{Vincent Lostanlen, Carmine Emanuele Cella}{articles/093_Paper}
+\includepaper{DTV-Based Melody Cutting for DTW-Based Melody Search and Indexing in QbH Systems}{Bartlomiej Stasiak}{articles/089_Paper}
+\includepaper{Elucidating User Behavior in Music Services Through Persona and Gender}{John Fuller, Lauren Hubener, Yea-Seul Kim, Jin Ha Lee}{articles/205_Paper}
+\includepaper{Exploring the Latent Structure of Collaborations in Music Recordings: A Case Study in Jazz}{Nazareno Andrade, Flavio Figueiredo}{articles/251_Paper}
+\includepaper{Global Properties of Expert and Algorithmic Hierarchical Music Analyses}{Phillip Kirlin}{articles/259_Paper}
 \includepaper{Human-Interactive Optical Music Recognition}{Liang Chen, Erik Stolterman, Christopher Raphael}{articles/106_Paper}
-\includepaper{I Said It First: Topological Analysis Of Lyrical Influence Networks}{Jack Atherton, Blair Kaneshiro}{articles/221_Paper}
-\includepaper{Impact Of Music On Decision Making In Quantitative Tasks}{Elad Liebman, Peter Stone, Corey White}{articles/272_Paper}
-\includepaper{Interactive Scores In Classical Music Production}{Simon Waloschek, Axel Berndt, Benjamin W. Bohl, Aristotelis Hadjakos}{articles/192_Paper}
-\includepaper{Jazz Expressive Performance Modeling}{Helena Bantulà, Sergio Giraldo, Rafael Ramírez}{articles/162_Paper}
-\includepaper{Large-Scale Organization Of Hierarchical Music Analyses}{Phillip Kirlin}{articles/259_Paper}
-\includepaper{Learning Invariants For Instrument Recognition}{Vincent Lostanlen, Carmine Emanuele Cella}{articles/093_Paper}
-\includepaper{Mining Musical Traits Of Social Functions In Native American Music}{Daniel Shanahan, Kerstin Neubarth, Darrell Conklin}{articles/167_Paper}
-\includepaper{Mining Online Music Listening Trajectories}{Flavio Figueiredo, Bruno Ribeiro, Jussara M. Almeida, Nazareno Andrade, Christos Faloutsos}{articles/193_Paper}
+\includepaper{I Said it First: Topological Analysis of Lyrical Influence Networks}{Jack Atherton, Blair Kaneshiro}{articles/221_Paper}
+\includepaper{Impact of Music on Decision Making in Quantitative Tasks}{Elad Liebman, Peter Stone, Corey White}{articles/272_Paper}
+\includepaper{Interactive Scores in Classical Music Production}{Simon Waloschek, Axel Berndt, Benjamin W. Bohl, Aristotelis Hadjakos}{articles/192_Paper}
+\includepaper{Jazz Ensemble Expressive Performance Modeling}{Helena Bantulà, Sergio Giraldo, Rafael Ramírez}{articles/162_Paper}
+\includepaper{Mining Musical Traits of Social Functions in Native American Music}{Daniel Shanahan, Kerstin Neubarth, Darrell Conklin}{articles/167_Paper}
+\includepaper{Mining Online Music Listening Trajectories}{Flavio Figueiredo, Bruno Ribeiro, Christos Faloutsos, Nazareno Andrade, Jussara M. Almeida}{articles/193_Paper}
 \includepaper{Musical Typicality: How Many Similar Songs Exist?}{Tomoyasu Nakano, Daichi Mochihashi, Kazuyoshi Yoshii, Masataka Goto}{articles/191_Paper}
-\includepaper{Musicdb: A Platform For Longitudinal Music Analytics}{Jeremy Hyrkas, Bill Howe}{articles/284_Paper}
+\includepaper{MusicDB: A Platform for Longitudinal Music Analytics}{Jeremy Hyrkas, Bill Howe}{articles/284_Paper}
 \includepaper{Noise Robust Music Artist Recognition Using I-Vector Features}{Hamid Eghbal-zadeh, Gerhard Widmer}{articles/037_Paper}
-\includepaper{On Practical Strategies Of Melody Indexing For Query By Humming}{Bartlomiej Stasiak}{articles/089_Paper}
-\includepaper{On The Use Of Note Onsets For Improved Lyrics-To-Audio Alignment}{Georgi Dzhambazov, Ajay Srinivasamurthy, Sertan Sentürk, Xavier Serra}{articles/243_Paper}
-\includepaper{Piano Transcription Using An Exponential Decay Model}{Tian Cheng, Matthias Mauch, Emmanouil Benetos, Simon Dixon}{articles/085_Paper}
-\includepaper{Querying Xml Score Databases: Xquery Is Not Enough!}{Raphael Fournier-S'niehotta, Philippe Rigaux, Nicolas Travers}{articles/136_Paper}
-\includepaper{Recurrent Neural Networks For Drum Transcription}{Richard Vogl, Matthias Dorfer, Peter Knees}{articles/269_Paper}
+\includepaper{On the Use of Note Onsets for Improved Lyrics-To-Audio Alignment in Turkish Makam Music}{Georgi Dzhambazov, Ajay Srinivasamurthy, Sertan Sentürk, Xavier Serra}{articles/243_Paper}
+\includepaper{Querying XML Score Databases: XQuery is not Enough!}{Raphael Fournier-S'niehotta, Philippe Rigaux, Nicolas Travers}{articles/136_Paper}
+\includepaper{Recurrent Neural Networks for Drum Transcription}{Richard Vogl, Matthias Dorfer, Peter Knees}{articles/269_Paper}
 \includepaper{Singing Voice Melody Transcription Using Deep Neural Networks}{François Rigaud, Mathieu Radenen}{articles/163_Paper}
-\includepaper{Sparse Coding Based Music Genre Classification Using Spectro-Temporal Modulations}{Chih-Shan Lin, Kai-Chun Hsu, Tai-Shih Chi}{articles/046_Paper}
-\includepaper{Time-Delayed Melody Surfaces For Rāga Recognition}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan Şentürk, Xavier Serra}{articles/030_Paper}
-\includepaper{Transcribing Human Piano Performances Into Music Notation}{Andrea Cogliati, David Temperley, Zhiyao Duan}{articles/088_Paper}
-\includepaper{Wimir: An Informetric Study On Women Authors In Ismir}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham, J. Stephen Downie}{articles/283_Paper}
+\includepaper{Sparse Coding Based Music Genre Classification Using Spectro-Temporal Modulations}{Kai-Chun Hsu, Chih-Shan Lin, Tai-Shih Chi}{articles/046_Paper}
+\includepaper{Time-Delayed Melody Surfaces for Rāga Recognition}{Sankalp Gulati, Joan Serrà, Kaustuv Kanti Ganguli, Sertan Şentürk, Xavier Serra}{articles/030_Paper}
+\includepaper{Transcribing Human Piano Performances into Music Notation}{Andrea Cogliati, David Temperley, Zhiyao Duan}{articles/088_Paper}
+\includepaper{WIMIR an Informetric Study on Women Authors in ISMIR}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham, J. Stephen Downie}{articles/283_Paper}

### 2016-07-12 deriveFiles.py

@@ -56,7 +56,7 @@ def papersSectionHeader(name, page):
     return chunk
 
 def latexEscape(string):
-    return string.replace('#','\#').replace('_','\_').replace('$','\$')
+    return string.replace('#','\#').replace('_','\_').replace('$','\$').replace('&','\&').replace('%','\%')
 
 def andToComma(string):
     return string.replace(' and ', ', ')

### 2016-07-13 2016_Proceedings_ISMIR/papers.tex
changed papers to be ordered strictly chronologically instead of by type (oral, poster)

@@
 \includepaper{Learning to Pinpoint Singing Voice from Weakly Labeled Examples}{Jan Schlüter}{articles/315_Paper}
-
-\thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 2: Rhythm}
-\includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
-\thispagestyle{empty}\cleardoublepage
-
-\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs, Gerhard Widmer}{articles/186_Paper}
-\includepaper{Bayesian Meter Tracking on Learned Signal Representations}{Andre Holzapfel, Thomas Grill}{articles/132_Paper}
-\includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font, Xavier Serra}{articles/195_Paper}
-\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Praetzlich, Meinard Mueller}{articles/022_Paper}
-
-\thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 3: Users}
-\includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
-\thispagestyle{empty}\cleardoublepage
-
-\includepaper{A Plan for Sustainable MIR Evaluation}{Brian McFee, Eric Humphrey, Julián Urbano}{articles/257_Paper}
-\includepaper{Go with the Flow: When Listeners Use Music as Technology}{Andrew Demetriou, Martha Larson, Cynthia C. S. Liem}{articles/068_Paper}
-\includepaper{A Look at the Cloud from Both Sides Now: An Analysis of Cloud Music Service Usage}{Jin Ha Lee, Yea-Seul Kim, Chris Hubbles}{articles/087_Paper}
-
-\thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 4: Musicologies}
-\includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
-\thispagestyle{empty}\cleardoublepage
-
-\includepaper{Analyzing Measure Annotations for Western Classical Music Recordings}{Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz, Meinard Mueller}{articles/079_Paper}
-\includepaper{Instrumental Idiom in the 16th Century: Embellishment Patterns in Arrangements of Vocal Music}{David Lewis, Tim Crawford, Daniel Müllensiefen}{articles/165_Paper}
-\includepaper{The Sousta Corpus: Beat-Informed Automatic Transcription of Traditional Dance Tunes}{Andre Holzapfel, Emmanouil Benetos}{articles/156_Paper}
-\includepaper{Learning a Feature Space for Similarity in World Music}{Maria Panteli, Emmanouil Benetos, Simon Dixon}{articles/166_Paper}
-
-\thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 5: Structure}
-\includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
-\thispagestyle{empty}\cleardoublepage
-
-\includepaper{Systematic Exploration of Computational Music Structure Research}{Oriol Nieto, Juan Pablo Bello}{articles/043_Paper}
-\includepaper{Using Priors to Improve Estimates of Music Structure}{Jordan Smith, Masataka Goto}{articles/135_Paper}
-\includepaper{Music Structural Segmentation Across Genres with Gammatone Features}{Mi Tian, Mark Sandler}{articles/032_Paper}
-
-\thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 6: Symbolic}
-\includepdf[pages=9,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
-\thispagestyle{empty}\cleardoublepage
-
-\includepaper{Automatic Melodic Reduction Using a Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
-\includepaper{A Neural Greedy Model for Voice Separation in Symbolic Music}{Patrick Gray, Razvan Bunescu}{articles/296_Paper}
-\includepaper{Towards Score Following In Sheet Music Images}{Matthias Dorfer, Andreas Arzt, Gerhard Widmer}{articles/027_Paper}
-\includepaper{Extracting Ground-Truth Information from MIDI Files: A MIDIfesto}{Colin Raffel, Daniel Ellis}{articles/105_Paper}
-
-\thispagestyle{empty}\cleardoublepage
-\addcontentsline{toc}{section}{Oral session 7: Deep-learning}
-\includepdf[pages=10,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
-\thispagestyle{empty}\cleardoublepage
-
-\includepaper{Automatic Tagging Using Deep Convolutional Neural Networks}{Keunwoo Choi, György Fazekas, Mark Sandler}{articles/009_Paper}
-\includepaper{A Hybrid Gaussian-HMM-Deep Learning Approach for Automatic Chord Estimation with Very Large Vocabulary}{Junqi Deng, Yu-Kwong Kwok}{articles/058_Paper}
-\includepaper{Melody Extraction on Vocal Segments Using Multi-Column Deep Neural Networks}{Sangeun Kum, Changheun Oh, Juhan Nam}{articles/119_Paper}
 
@@
 \includepaper{Towards Evaluating Multiple Predominant Melody Annotations in Jazz Recordings}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar, Meinard Mueller}{articles/049_Paper}
+
+\thispagestyle{empty}\cleardoublepage
+\addcontentsline{toc}{section}{Oral session 2: Rhythm}
+\includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\thispagestyle{empty}\cleardoublepage
+
+\includepaper{Joint Beat and Downbeat Tracking with Recurrent Neural Networks}{Sebastian Böck, Florian Krebs, Gerhard Widmer}{articles/186_Paper}
+\includepaper{Bayesian Meter Tracking on Learned Signal Representations}{Andre Holzapfel, Thomas Grill}{articles/132_Paper}
+\includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font, Xavier Serra}{articles/195_Paper}
+\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Praetzlich, Meinard Mueller}{articles/022_Paper}
+
+\thispagestyle{empty}\cleardoublepage
+\addcontentsline{toc}{section}{Oral session 3: Users}
+\includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\thispagestyle{empty}\cleardoublepage
+
+\includepaper{A Plan for Sustainable MIR Evaluation}{Brian McFee, Eric Humphrey, Julián Urbano}{articles/257_Paper}
+\includepaper{Go with the Flow: When Listeners Use Music as Technology}{Andrew Demetriou, Martha Larson, Cynthia C. S. Liem}{articles/068_Paper}
+\includepaper{A Look at the Cloud from Both Sides Now: An Analysis of Cloud Music Service Usage}{Jin Ha Lee, Yea-Seul Kim, Chris Hubbles}{articles/087_Paper}
 
@@
 \thispagestyle{empty}\cleardoublepage
+\addcontentsline{toc}{section}{Oral session 4: Musicologies}
+\includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\thispagestyle{empty}\cleardoublepage
+
+\includepaper{Analyzing Measure Annotations for Western Classical Music Recordings}{Christof Weiß, Vlora Arifi-Müller, Thomas Prätzlich, Rainer Kleinertz, Meinard Mueller}{articles/079_Paper}
+\includepaper{Instrumental Idiom in the 16th Century: Embellishment Patterns in Arrangements of Vocal Music}{David Lewis, Tim Crawford, Daniel Müllensiefen}{articles/165_Paper}
+\includepaper{The Sousta Corpus: Beat-Informed Automatic Transcription of Traditional Dance Tunes}{Andre Holzapfel, Emmanouil Benetos}{articles/156_Paper}
+\includepaper{Learning a Feature Space for Similarity in World Music}{Maria Panteli, Emmanouil Benetos, Simon Dixon}{articles/166_Paper}
+
+\thispagestyle{empty}\cleardoublepage
+\addcontentsline{toc}{section}{Oral session 5: Structure}
+\includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\thispagestyle{empty}\cleardoublepage
+
+\includepaper{Systematic Exploration of Computational Music Structure Research}{Oriol Nieto, Juan Pablo Bello}{articles/043_Paper}
+\includepaper{Using Priors to Improve Estimates of Music Structure}{Jordan Smith, Masataka Goto}{articles/135_Paper}
+\includepaper{Music Structural Segmentation Across Genres with Gammatone Features}{Mi Tian, Mark Sandler}{articles/032_Paper}
+
+\thispagestyle{empty}\cleardoublepage
 \addcontentsline{toc}{section}{Poster session 3}
@@
 \includepaper{Transcribing Human Piano Performances into Music Notation}{Andrea Cogliati, David Temperley, Zhiyao Duan}{articles/088_Paper}
-\includepaper{WIMIR an Informetric Study on Women Authors in ISMIR}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham, J. Stephen Downie}{articles/283_Paper}
+\includepaper{WiMIR: An Informetric Study On Women Authors In ISMIR}{Xiao Hu, Kahyun Choi, Jin Ha Lee, Audrey Laplante, Yun Hao, Sally Jo Cunningham, J. Stephen Downie}{articles/283_Paper}
+
+\thispagestyle{empty}\cleardoublepage
+\addcontentsline{toc}{section}{Oral session 6: Symbolic}
+\includepdf[pages=9,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\thispagestyle{empty}\cleardoublepage
+
+\includepaper{Automatic Melodic Reduction Using a Supervised Probabilistic Context-Free Grammar}{Ryan Groves}{articles/274_Paper}
+\includepaper{A Neural Greedy Model for Voice Separation in Symbolic Music}{Patrick Gray, Razvan Bunescu}{articles/296_Paper}
+\includepaper{Towards Score Following In Sheet Music Images}{Matthias Dorfer, Andreas Arzt, Gerhard Widmer}{articles/027_Paper}
+\includepaper{Extracting Ground-Truth Information from MIDI Files: A MIDIfesto}{Colin Raffel, Daniel Ellis}{articles/105_Paper}
+
+\thispagestyle{empty}\cleardoublepage
+\addcontentsline{toc}{section}{Oral session 7: Deep-learning}
+\includepdf[pages=10,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\thispagestyle{empty}\cleardoublepage
+
+\includepaper{Automatic Tagging Using Deep Convolutional Neural Networks}{Keunwoo Choi, György Fazekas, Mark Sandler}{articles/009_Paper}
+\includepaper{A Hybrid Gaussian-HMM-Deep Learning Approach for Automatic Chord Estimation with Very Large Vocabulary}{Junqi Deng, Yu-Kwong Kwok}{articles/058_Paper}
+\includepaper{Melody Extraction on Vocal Segments Using Multi-Column Deep Neural Networks}{Sangeun Kum, Changheun Oh, Juhan Nam}{articles/119_Paper}

### 2016-07-13 deriveFiles.py
count authors in deriving files

@@ -31,18 +31,27 @@ def unicode_tsv_reader(utf8FileName):
 def generatePapersDotTex(csvFile):
     lastSession = ""
     sessionInfo = loadSessionInfo()
+    authorCount = collections.defaultdict(int)
+    
     # with io.open('2016_Proceedings_ISMIR/papers.tex', 'w', encoding='utf-8') as papersDotTex:
     # with codecs.open('2016_Proceedings_ISMIR/papers.tex', 'w', 'utf-8') as papersDotTex:
     with open('2016_Proceedings_ISMIR/papers.tex', 'w') as papersDotTex:
         for title, authors, number, session in unicode_tsv_reader(csvFile):
+            authors = andToComma(authors)
+            for author in authors.split(', '):
+                authorCount[author] += 1
+                
             if session != lastSession:
                 name, page = sessionInfo[session]
                 papersDotTex.write(papersSectionHeader(name, page))
             lastSession = session
             
             papersDotTex.write('\includepaper{%s}{%s}{articles/%03d_Paper}\n'
-                               % (latexEscape(title), andToComma(authors), int(number)))
+                               % (latexEscape(title), authors, int(number)))
 
+    #print sorted(authorCount.iteritems())
+    print "Total authorings: %s" % sum(authorCount.values())
+    print "Unique authors: %s" % len(authorCount)
 
 def papersSectionHeader(name, page):
     chunk = """

### 2016-07-13 2016_Proceedings_ISMIR/keynotes.tex
big update of pre-defined pdfs from google docs, everything in place now except cover, need to finalize preface

--- 2016-06-29 2016_Proceedings_ISMIR/keynotes.tex
@@
  %-------------------------------------------
+
 % Keynote talk 1
-\addcontentsline{toc}{subsection}{Integrating Music Information Sources for Music Production and Consumption\\\textit{Mark Sandler}}
+\addcontentsline{toc}{subsection}{The New York Philharmonic Leon Levy Digital Archives: An Integrated View of Performance Since 1842\\\textit{Barbara Haws}}
 \includepdf[pagecommand=\thispagestyle{fancy}]{external/10-1_Keynotes-1.pdf}%
@@
 % Keynote talk 2
-\addcontentsline{toc}{subsection}{The Promise of Music Information Retrieval: Are we there yet?\\\textit{J.\ Stephen Downie}}
+\addcontentsline{toc}{subsection}{Is Machine Learning Enough?\\\textit{Beth Logan, PhD}}
 \includepdf[pagecommand=\thispagestyle{fancy}]{external/10-2_Keynotes-2.pdf}%

### 2016-07-13 2016_Proceedings_ISMIR/tutorials.tex
big update of pre-defined pdfs from google docs, everything in place now except cover, need to finalize preface

--- 2016-06-29 2016_Proceedings_ISMIR/tutorials.tex
@@
  %-------------------------------------------
+
+\newcommand{\includetut}[3]{\addcontentsline{toc}{subsection}{#1\\\textit{#2}}
+\includepdf[pages=#3, pagecommand=\thispagestyle{fancy}]{external/11_TutorialsAll.pdf}}
+
 % Tutorial 1
-\includeabstract{Why Singing is Interesting}{Simon Dixon, Masataka Goto, Matthias Mauch}{external/11-1_Tutorial-1.pdf}
+\includetut{Jazz solo analysis between music information
+  retrieval, music psychology, and jazz research}{Jakob Abe{\ss}er,
+  Klaus Frieler, Wolf-Georg Zaddach}{1-2}
 
 % Tutorial 2
-\includeabstract{Addressing the Music Information Needs of Musicologists}{Richard J.\ Lewis, Ben Fields, Tim Crawford}{external/11-2_Tutorial-2.pdf}
+\includetut{Music Information Retrieval: Overview, Recent
+  Developments and Future Challenges}{Emilia G\'omez, Markus Schedl,
+  Xavier Serra, Xiao Hu}{3}
 
 % Tutorial 3
-\includeabstract{Markov Logic Networks for Music Analysis}{Helene Papadopoulos}{external/11-3_Tutorial-3.pdf}
+\includetut{Why is studio production interesting?}{Emmanuel
+Deruty, Fran\c{c}ois Pachet}{4-5}
 
 % Tutorial 4
-\includeabstract{COmputation and FLAmenco: Why Flamenco is Interesting for
-MIR Research}{Emilia G{\'o}mez, Nadine Kroher, Jose Miguel D{\'i}az-B{\'a}{\~n}ez, Sergio Oramas, Joaqu{\'i}n Mora, Francisco G{\'o}mez-Mart{\'i}n}{external/11-4_Tutorial-4.pdf}
+\includetut{Introduction to EEG Decoding for Music Information Retrieval
+Research}{Sebastian Stober, Blair Kaneshiro}{6}
 
 % Tutorial 5
-\includeabstract{Using Correlation Analysis and Big Data to Identify and Predict Musical Behaviors}{Jeff C.\ Smith}{external/11-5_Tutorial-5.pdf}
+\includetut{Natural Language Processing for MIR}{Sergio Oramas,
+  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{7}
 
 % Tutorial 6
-\includeabstract{Automatic Music Transcription}{Zhiyao Duan, Emmanouil Benetos}{external/11-6_Tutorial-6.pdf}
+\includetut{Why Hip-Hop is interesting}{Jan Van Balen, Ethan
+  Hein, Dan Brown}{8-9}

### 2016-07-13 2016_Proceedings_ISMIR/00-run.sh

@@ -1,4 +1,4 @@
-#!/bin/bash
+#!/bin/bash -xue
 
 rm -f 2016_Proceedings_ISMIR.{aux,ain,log,toc}
 pdflatex 2016_Proceedings_ISMIR.tex

### 2016-07-14 2016_Proceedings_ISMIR/00-run.sh
added info necessary for splitting proceedings, getting page count for each paper

@@ -10,3 +10,5 @@ authorindex -d 2016_Proceedings_ISMIR_2.aux
 
 pdflatex 2016_Proceedings_ISMIR.tex
 pdflatex 2016_Proceedings_ISMIR.tex
+
+cp 2016_Proceedings_ISMIR.pdf ../2016_Proceedings_ISMIR_Electronic_Tools/data/

### 2016-07-14 2016_Proceedings_ISMIR/01-get_pages_total.py

@@ -1,0 +1,13 @@
+#!/usr/bin/python
+
+import PyPDF2
+import glob
+
+all_pdf_files = glob.glob('articles/*.pdf')
+with open('../2016_Proceedings_ISMIR_Electronic_Tools/data/pages_total.csv', 'w') as f:
+    f.write('filename,pages_total\n')
+
+    for cur_pdf_filename in all_pdf_files:
+        with open(cur_pdf_filename, 'rb') as cur_pdf_fh:
+            cur_pdf = PyPDF2.PdfFileReader(cur_pdf_fh)
+            f.write(cur_pdf_filename + ',' + str(cur_pdf.getNumPages()) + '\n')

### 2016-07-14 deriveFiles.py

@@ -10,6 +10,7 @@ electronic proceedings.
 import csv
 import collections
 import os
+import shutil
 
 def unicode_csv_reader(utf8_data, dialect="excel", **kwargs):
     """This function will read a csv file and will interpret the
@@ -76,17 +77,19 @@ def loadSessionInfo():
 
     
 def generateElectronicCsvFiles(csvFile):
-    generateSessionIndex(csvFile)
+    copySessionIndex()
     generateSessionFiles(csvFile)
     
-def generateSessionIndex(csvFile):
-    sessionInfo = loadSessionInfo()
-    fileName = '2016_Proceedings_ISMIR_Electronic_Tools/data/session_index.csv'
-    makeDirs(os.path.dirname(fileName))
-    with open(fileName, 'w') as sessionFile:
-        for session, (name, number) in sorted(sessionInfo.iteritems()):
-            sessionFile.write('%s;%s;%s\n' % (session, number, name))
-        
+def copySessionIndex():
+    """Copy session_index file, created manually in excel.  Could
+    maybe be created automatically from table of contents file from
+    latex, but this is easier for now.
+
+    """
+    outFile = '2016_Proceedings_ISMIR_Electronic_Tools/data/session_index.csv'
+    inFile  = 'data/session_index.csv'
+    shutil.copy(inFile, outFile)
+    
 def generateSessionFiles(csvFile):
     sessionInfo = loadSessionInfo()
     sessions = collections.defaultdict(list)
@@ -97,6 +100,7 @@ def generateSessionFiles(csvFile):
                                 '%s.csv' % session)
         makeDirs(os.path.dirname(fileName))
         with open(fileName, 'w') as sessionFile:
+            sessionFile.write('Title;Authors;File\n')
             for title, authors, number in info:
                 sessionFile.write('%s;%s;articles/%03d_Paper.pdf\n'
                                   % (title, authors, number))
@@ -115,7 +119,8 @@ def main():
     csvFile = 'data/completePaperList.csv'
     generatePapersDotTex(csvFile)
     generateElectronicCsvFiles(csvFile)
-
+    shutil.copy('data/reviewers.csv',
+                '2016_Proceedings_ISMIR_Electronic_Tools/data/reviewers.txt')
 
 
 if __name__ == '__main__':

### 2016-07-14 2016_Proceedings_ISMIR_Electronic_Tools/00-split_proceedings.py
got proceedings splitting and overview website generation working

@@ -1,0 +1,68 @@
+#!/usr/bin/python
+
+import csv
+import os
+import PyPDF2
+from ismir_utils import unicode_csv_reader, search_pages_total, makeDirs
+
+
+def main():
+    # open proceedings
+    proceedings_pdf = PyPDF2.PdfFileReader(open('data/2016_Proceedings_ISMIR.pdf', 'rb'))
+
+    # open pages_total as look-up table
+    with open('data/pages_total.csv') as pages_total:
+        pt_reader = unicode_csv_reader(pages_total, delimiter=';')
+        next(pt_reader) # skip the headers
+
+        # store it all in a list
+        pages_total = list(pt_reader)
+
+
+    with open('data/session_index.csv') as session_index:
+        si_reader = unicode_csv_reader(session_index, delimiter=';')
+        next(si_reader) # skip the headers
+
+        # iterate over sessions
+        for session_name, start_page, header_name in si_reader:
+            print "Session name:" +session_name,"Starting Page:" +start_page
+
+            # open session file
+            with open('data/' + session_name + '.csv') as current_session: #define session_name.csv as the current_session
+                s_reader = unicode_csv_reader(current_session, delimiter=';')
+                next(s_reader) # skip the headers
+
+                # iterate over session entries
+                current_paper_start = int(start_page)
+                for paper_title, authors, pdf_filename in s_reader:
+                    # get number of pages for this paper
+                    current_paper = pdf_filename
+                    print current_paper
+                    pdf_filename = pdf_filename.split('/')[1] #split and take the part after "/"
+                    print "Current paper being processed: " + pdf_filename
+                    # search for it in the pages_total
+                    current_paper_length = search_pages_total(current_paper, pages_total)
+
+                    current_paper_end = current_paper_start+current_paper_length-1
+                    #current_paper_end = 0
+                    print "Start page: " +str(current_paper_start)
+                    print  "End page: " +str(current_paper_end)
+
+
+                    output = PyPDF2.PdfFileWriter()
+                    for p in range(current_paper_start-1, current_paper_end):
+                        print p
+                        output.addPage(proceedings_pdf.getPage(p))
+
+                    #output_folder = 'output/articles'
+                    output_folder = 'data/articles_splitted'
+                    makeDirs(output_folder)
+                    with open(output_folder + '/' + pdf_filename, 'wb') as f:
+                        output.write(f)
+
+                    current_paper_start = current_paper_end + 1
+
+
+if __name__ == '__main__':
+    main()
+    

### 2016-07-14 2016_Proceedings_ISMIR_Electronic_Tools/01-generate_overview_website.py

@@ -1,0 +1,73 @@
+#!/usr/bin/python
+
+import codecs
+import csv
+import jinja2
+import os
+from ismir_utils import unicode_csv_reader, search_pages_total, makeDirs
+
+
+# open pages_total as look-up table
+with open('data/pages_total.csv') as pages_total:
+    pt_reader = unicode_csv_reader(pages_total, delimiter=';')
+    next(pt_reader) # skip the headers
+    
+    # store it all in a list
+    pages_total = list(pt_reader)
+
+sessions = []
+pdf_offset = 28
+
+with open('data/session_index.csv') as session_index:
+    si_reader = unicode_csv_reader(session_index, delimiter=';')
+    next(si_reader) # skip the headers
+
+    # iterate over sessions
+    for session_name, start_page, header_name in si_reader:
+        print session_name, start_page
+
+        current_paper_start = int(start_page)
+        # open session file
+        with open('data/' + session_name + '.csv') as current_session:
+            s_reader = unicode_csv_reader(current_session, delimiter=';')
+            next(s_reader) # skip the headers
+
+            # iterate over session entries
+            publications = []
+            for paper_title, authors, pdf_filename in s_reader:
+                current_paper = pdf_filename
+                current_paper_length = search_pages_total(current_paper, pages_total)
+                current_paper_end = current_paper_start+current_paper_length-1
+                publications.append({'title': paper_title,
+                                     'authors': authors,
+                                     'paper_startpage': current_paper_start-pdf_offset,
+                                     'paper_endpage': current_paper_end-pdf_offset,
+                                     'pdf': pdf_filename})
+                current_paper_start = current_paper_end + 1
+
+        sessions.append({'title': header_name,
+                         'publications': publications})
+
+context = {
+        'sessions': sessions
+    }
+
+# get jinja template
+PATH = os.path.dirname(os.path.abspath(__file__))
+template_env = jinja2.Environment(loader=jinja2.FileSystemLoader(os.path.join(PATH, 'templates')))
+template = template_env.get_template('overview_table.html')
+
+makeDirs('output/html_overview_table')
+with open('output/html_overview_table/index.html', 'w') as f:
+    html = template.render(context)
+    f.write(html.encode('utf-8'))
+
+template = template_env.get_template('overview_table.html')
+with open('output/overview_table.html', 'w') as f:
+    html = template.render(context)
+    f.write(html.encode('utf-8'))
+
[…]

### 2016-07-14 2016_Proceedings_ISMIR_Electronic_Tools/ismir_utils.py

@@ -1,0 +1,30 @@
+import codecs
+import csv
+import os
+
+def unicode_csv_reader(utf8_data, dialect=csv.excel, **kwargs):
+# This function will read a csv file and will interpret
+# the contained data as utf-8.
+    csv_reader = csv.reader(utf8_data, dialect=dialect, **kwargs)
+    for row in csv_reader:
+        yield [unicode(cell, 'utf-8') for cell in row]
+
+
+def search_pages_total(paper_name, pages_total):
+    for current_row in pages_total: #go through the rows in pages_total
+        current_row = str(current_row[0]).split(',')  #split row after comma
+        current_paper_name = current_row[0] #paper_name = first "cell"
+        current_pages = int(current_row[1]) # number of pages  = second "cell"
+        if paper_name in current_paper_name: # if paper name matches the name in the list of papers
+            return current_pages
+    raise BaseException("Paper not found: %s" % paper_name)
+        
+def makeDirs(path):
+    sub_path = os.path.dirname(path)
+    if sub_path == path:
+        raise "sub_path == path: %s" % path
+    if len(sub_path) > 0 and not os.path.exists(sub_path):
+        makeDirs(sub_path)
+    if not os.path.exists(path):
+        os.mkdir(path)
+

### 2016-07-14 2016_Proceedings_ISMIR_Electronic_Tools/02-generate_author_index.py
got author index generation working

@@ -1,0 +1,80 @@
+#!/usr/bin/python
+
+import csv
+import codecs
+import jinja2
+import os
+from nameparser import HumanName
+from ismir_utils import search_pages_total, unicode_csv_reader
+import string
+
+
+# open pages_total as look-up table
+with open('data/pages_total.csv') as pages_total:
+    pt_reader = unicode_csv_reader(pages_total, delimiter=';')
+    next(pt_reader) # skip the headers
+    
+    # store it all in a list
+    pages_total = list(pt_reader)
+
+# get jinja template
+PATH = os.path.dirname(os.path.abspath(__file__))
+template_env = jinja2.Environment(loader=jinja2.FileSystemLoader(os.path.join(PATH, 'templates')))
+template = template_env.get_template('author_index.html')
+
+publications = []
+unique_authors =[]
+pdf_offset = 32
+
+with open('data/session_index.csv') as session_index:
+    si_reader = unicode_csv_reader(session_index, delimiter=';')
+    next(si_reader) # skip the headers
+
+    # iterate over sessions
+    for session_name, start_page, header_name in si_reader:
+        # open session file
+        with open('data/' + session_name + '.csv') as current_session:
+            s_reader = unicode_csv_reader(current_session, delimiter=';')
+            next(s_reader) # skip the headers
+
+            # iterate over session entries
+            current_paper_start = int(start_page)
+            for paper_title, authors, pdf_filename in s_reader:
+                current_paper = pdf_filename
+                pdf_filename = pdf_filename.split('/')[1] #split and take the part after "/"
+                # search for it in the pages_total
+                current_paper_length = search_pages_total(current_paper, pages_total)
+                current_paper_end = current_paper_start+current_paper_length-1
+
+                for author in authors.split(','):
+                    author = author.strip()
+                    search_author = filter(lambda cur_author: cur_author['name'] == author, unique_authors)
+                    if not search_author:
+                        # append to list
+                        unique_authors.append({'name': author,
+                                               'human_name': HumanName(author),
+                                               'pdfs': [pdf_filename, ],
+                                               'paper_startpage': [current_paper_start-pdf_offset, ],
+                                               'paper_title': [paper_title, ]})
+                    else:
+                        search_author[0]['pdfs'].append(pdf_filename)
+                        search_author[0]['paper_startpage'].append(current_paper_start-pdf_offset)
[…]

### 2016-07-14 deriveFiles.py

@@ -103,7 +103,7 @@ def generateSessionFiles(csvFile):
             sessionFile.write('Title;Authors;File\n')
             for title, authors, number in info:
                 sessionFile.write('%s;%s;articles/%03d_Paper.pdf\n'
-                                  % (title, authors, number))
+                                  % (title, andToComma(authors), number))
 
 def makeDirs(path):
     sub_path = os.path.dirname(path)

### 2016-07-14 2016_Proceedings_ISMIR_Electronic_Tools/03-generate_reviewer_list.py
reviewer list generation

@@ -1,0 +1,21 @@
+#!/usr/bin/python
+
+import jinja2
+import codecs
+import os
+
+with codecs.open('data/reviewers.txt', 'r', 'utf-8') as f:
+    reviewers = [line.rstrip('\n') for line in f]
+
+context = {'reviewers': reviewers}
+
+print reviewers[85]
+
+# get jinja template
+PATH = os.path.dirname(os.path.abspath(__file__))
+template_env = jinja2.Environment(loader=jinja2.FileSystemLoader(os.path.join(PATH, 'templates')))
+template = template_env.get_template('reviewer_list.html')
+print len(reviewers)
+with open('output/html_overview_table/reviewer_list.html', 'w') as f:
+    html = template.render(context)
+    f.write(html.encode('utf-8'))

### 2016-07-14 2016_Proceedings_ISMIR/tutorials.tex
re-added author index title page, updated preface and tutorials

@@
   Developments and Future Challenges}{Emilia G\'omez, Markus Schedl,
-  Xavier Serra, Xiao Hu}{3}
+  Xavier Serra, Xiao Hu}{3-4}
 
@@
 \includetut{Why is studio production interesting?}{Emmanuel
-Deruty, Fran\c{c}ois Pachet}{4-5}
+Deruty, Fran\c{c}ois Pachet}{5-6}
 
@@
 \includetut{Introduction to EEG Decoding for Music Information Retrieval
-Research}{Sebastian Stober, Blair Kaneshiro}{6}
+Research}{Sebastian Stober, Blair Kaneshiro}{7-8}
 
@@
 \includetut{Natural Language Processing for MIR}{Sergio Oramas,
-  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{7}
+  Luis Espinosa-Anke, Shuo Zhang, Horacio Saggion}{9-10}
 
@@
 \includetut{Why Hip-Hop is interesting}{Jan Van Balen, Ethan
-  Hein, Dan Brown}{8-9}
+  Hein, Dan Brown}{11-12}

### 2016-07-15 2016_Proceedings_ISMIR_Electronic_Tools/02-generate_author_index.py
got author index working and into webpage

@@ -24,7 +24,7 @@ template = template_env.get_template('author_index.html')
 
 publications = []
 unique_authors =[]
-pdf_offset = 32
+pdf_offset = 28
 
 with open('data/session_index.csv') as session_index:
     si_reader = unicode_csv_reader(session_index, delimiter=';')

### 2016-07-15 2016_Proceedings_ISMIR/00-run.sh
updated logos and preface, used second cover instead of first (so twice) for now

@@ -11,4 +11,5 @@ authorindex -d 2016_Proceedings_ISMIR_2.aux
 pdflatex 2016_Proceedings_ISMIR.tex
 pdflatex 2016_Proceedings_ISMIR.tex
 
+cp 2016_Proceedings_ISMIR.pdf ../2016_Proceedings_ISMIR_Electronic/
 cp 2016_Proceedings_ISMIR.pdf ../2016_Proceedings_ISMIR_Electronic_Tools/data/

### 2016-07-15 syncWithS3.sh
script to sync to s3, line break in index

@@ -1,0 +1,8 @@
+#!/bin/bash -xue
+
+# Sync files with amazon s3 bucket using aws command line tool
+
+DEST=m.mr-pc.org/ismir16
+SRC=2016_Proceedings_ISMIR_Electronic/
+
+aws s3 sync $SRC s3://$DEST --grants read=uri=http://acs.amazonaws.com/groups/global/AllUsers

### 2016-07-15 syncWithS3.sh
switched to new cover from Tia

@@ -3,6 +3,8 @@
 # Sync files with amazon s3 bucket using aws command line tool
 
 DEST=m.mr-pc.org/ismir16
-SRC=2016_Proceedings_ISMIR_Electronic/
+SRC=2016_Proceedings_ISMIR_Electronic
 
-aws s3 sync $SRC s3://$DEST --grants read=uri=http://acs.amazonaws.com/groups/global/AllUsers
+mv $SRC.zip $SRC
+aws s3 sync $SRC/ s3://$DEST --grants read=uri=http://acs.amazonaws.com/groups/global/AllUsers
+mv $SRC/$SRC.zip .

### 2016-07-15 2016_Proceedings_ISMIR/papers.tex
big update of pre-defined pdfs from google docs, everything in place now except cover, need to finalize preface
fixed inconsistencies in a few authors' names

@@
 \addcontentsline{toc}{section}{Oral session 1: Mixed}
-\includepdf[pages=2,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\includepdf[pages=4,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
 \thispagestyle{empty}\cleardoublepage
@@
 \includepaper{Predicting Missing Music Components with Bidirectional Long Short-Term Memory Neural Networks}{I-Ting Liu, Richard Randall}{articles/097_Paper}
-\includepaper{Structural Segmentation and Visualization of Sitar and Sarod Concert Audio}{Vinutha T. P., Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}
+\includepaper{Structural Segmentation and Visualization of Sitar and Sarod Concert Audio}{T. P. Vinutha, Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}
 \includepaper{Template-Based Vibrato Analysis in Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}
@@
 \addcontentsline{toc}{section}{Oral session 2: Rhythm}
-\includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
 \thispagestyle{empty}\cleardoublepage
@@
 \includepaper{Tempo Estimation for Music Loops and a Simple Confidence Measure}{Frederic Font, Xavier Serra}{articles/195_Paper}
-\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Praetzlich, Meinard Mueller}{articles/022_Paper}
+\includepaper{Brain Beats: Tempo Extraction from EEG Data}{Sebastian Stober, Thomas Prätzlich, Meinard Mueller}{articles/022_Paper}
 
@@
 \addcontentsline{toc}{section}{Oral session 3: Users}
-\includepdf[pages=5,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
 \thispagestyle{empty}\cleardoublepage
@@
 \addcontentsline{toc}{section}{Poster session 2}
-\includepdf[pages=4,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\includepdf[pages=2,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
 \thispagestyle{empty}\cleardoublepage
@@
 \includepaper{Improving Predictions of Derived Viewpoints in Multiple Viewpoints Systems}{Thomas Hedges, Geraint Wiggins}{articles/208_Paper}
-\includepaper{Known Artist Live Song ID: A Hashprint Approach}{TJ Tsai, Thomas Praetzlich, Meinard Mueller}{articles/098_Paper}
+\includepaper{Known Artist Live Song ID: A Hashprint Approach}{TJ Tsai, Thomas Prätzlich, Meinard Mueller}{articles/098_Paper}
 \includepaper{Learning Temporal Features Using a Deep Neural Network and its Application to Music Genre Classification}{Il-Young Jeong, Kyogu Lee}{articles/159_Paper}
@@
 \addcontentsline{toc}{section}{Oral session 4: Musicologies}
-\includepdf[pages=6,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
 \thispagestyle{empty}\cleardoublepage
@@
 \addcontentsline{toc}{section}{Oral session 5: Structure}
-\includepdf[pages=7,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\includepdf[pages=8,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
 \thispagestyle{empty}\cleardoublepage
@@
 \addcontentsline{toc}{section}{Poster session 3}
-\includepdf[pages=8,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
+\includepdf[pages=3,pagecommand=\thispagestyle{empty}]{external/12_Sessions.pdf}%
 \thispagestyle{empty}\cleardoublepage
@@
 \includepaper{A Comparison of Melody Extraction Methods Based on Source-Filter Modelling}{Juan J. Bosch, Rachel M. Bittner, Justin Salamon, Emilia Gómez}{articles/256_Paper}
-\includepaper{An Analysis of Agreement in Classical Music Perception and its Relationship to Listener Characteristics}{Markus Schedl, Hamid Eghbal-Zadeh, Emilia Gómez, Marko Tkalcic}{articles/260_Paper}
+\includepaper{An Analysis of Agreement in Classical Music Perception and its Relationship to Listener Characteristics}{Markus Schedl, Hamid Eghbal-zadeh, Emilia Gómez, Marko Tkalcic}{articles/260_Paper}
 \includepaper{An Attack/Decay Model for Piano Transcription}{Tian Cheng, Matthias Mauch, Emmanouil Benetos, Simon Dixon}{articles/085_Paper}

### 2016-07-25 2016_Proceedings_ISMIR/00-run.sh
stuff to support fewer duplicate files, saving my disk space

@@ -12,4 +12,4 @@ pdflatex 2016_Proceedings_ISMIR.tex
 pdflatex 2016_Proceedings_ISMIR.tex
 
 cp 2016_Proceedings_ISMIR.pdf ../2016_Proceedings_ISMIR_Electronic/
-cp 2016_Proceedings_ISMIR.pdf ../2016_Proceedings_ISMIR_Electronic_Tools/data/
+# cp 2016_Proceedings_ISMIR.pdf ../2016_Proceedings_ISMIR_Electronic_Tools/data/

### 2016-07-25 syncWithS3.sh

@@ -5,6 +5,6 @@
 DEST=m.mr-pc.org/ismir16
 SRC=2016_Proceedings_ISMIR_Electronic
 
-mv $SRC.zip $SRC
+[ -f $SRC.zip ] && mv $SRC.zip $SRC
 aws s3 sync $SRC/ s3://$DEST --grants read=uri=http://acs.amazonaws.com/groups/global/AllUsers
-mv $SRC/$SRC.zip .
+[ -f $SRC/$SRC.zip ] && mv $SRC/$SRC.zip .

### 2016-09-02 2016_Proceedings_ISMIR/papers.tex
fixed name of paper

@@
 \includepaper{Structural Segmentation and Visualization of Sitar and Sarod Concert Audio}{T. P. Vinutha, Suryanarayana Sankagiri, Kaustuv Kanti Ganguli, Preeti Rao}{articles/151_Paper}
-\includepaper{Template-Based Vibrato Analysis in Complex Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}
+\includepaper{Template-Based Vibrato Analysis of Music Signals}{Jonathan Driedger, Stefan Balke, Sebastian Ewert, Meinard Mueller}{articles/005_Paper}
 \includepaper{Towards Evaluating Multiple Predominant Melody Annotations in Jazz Recordings}{Stefan Balke, Jonathan Driedger, Jakob Abesser, Christian Dittmar, Meinard Mueller}{articles/049_Paper}

### 2016-09-02 2016_Proceedings_ISMIR_Electronic_Tools/02-generate_author_index.py
fixed url in dblp template, required changes elsewhere

@@ -4,6 +4,7 @@ import csv
 import codecs
 import jinja2
 import os
+import re
 from nameparser import HumanName
 from ismir_utils import search_pages_total, unicode_csv_reader
 import string
@@ -41,7 +42,7 @@ with open('data/session_index.csv') as session_index:
             current_paper_start = int(start_page)
             for paper_title, authors, pdf_filename in s_reader:
                 current_paper = pdf_filename
-                pdf_filename = pdf_filename.split('/')[1] #split and take the part after "/"
+                pdf_filename = re.sub('^[^/]*?/', '', pdf_filename) #split and take the part after "/"
                 # search for it in the pages_total
                 current_paper_length = search_pages_total(current_paper, pages_total)
                 current_paper_end = current_paper_start+current_paper_length-1

### 2016-09-02 deriveFiles.py

@@ -102,7 +102,7 @@ def generateSessionFiles(csvFile):
         with open(fileName, 'w') as sessionFile:
             sessionFile.write('Title;Authors;File\n')
             for title, authors, number in info:
-                sessionFile.write('%s;%s;articles/%03d_Paper.pdf\n'
+                sessionFile.write('%s;%s;%03d_Paper.pdf\n'
                                   % (title, andToComma(authors), number))
 
 def makeDirs(path):
